### 2012-06-18 paper.tex
The condensation paper as an independent branch from Tsurusawa's thesis

\input{preamble}

\begin{document}
\title{Gelation as a condensation frustrated by hydrodynamics and mechanical tension}
\author{Hideyo Tsurusawa}
\author{Mathieu Leocmach}
\author{Hajime Tanaka}
\maketitle

\section{Abstract}
Condensations are universal phenomenon in aggregating molecules.
The molecules form droplets and crystals as equilibrium states and gels as non-equilibrium states.
Gels, space-spanning networks with their dynamics arrested, have elasticity and are observed in many systems, including polymers and proteins.
Since open network structures of gels are energetically disfavoured, the mechanism to self-assemble networks has received considerable attentions.
Previously, simulation works have aimed reproducing the process of network formation.
The results of Brownian dynamics simulations, which assume thermal fluctuations and short-range attractions between molecules, have shown formation of droplets in a moderate strength of attractions.
In contrast, the simulations that also consider hydrodynamic interactions can reconstitute gelation in a moderate strength of attractions, suggesting key roles of hydrodynamic interactions in network formation.
However, little is known experimentally about the gelation process because the previous method limits access to the process itself.
Here, we observe the entire process of gelation in a single particle level by a new experimental method and demonstrate that gelation is not a simple condensation but frustrated by hydrodynamic interactions and mechanical tension.

\section{Introduction} % Introduction, from wide attentions to specific subjects
% General attentions
Gels are space-spanning networks with their dynamics arrested, which cause elasticity and are widely used in our daily life such as food and filter.
In a scientific viewpoint, gels have received wide attentions because gels are non-equilibrium non-ergodic states.
% Focusing on 'colloidal gels'
Among various model systems, colloidal gels have been intensively studied since colloids have a great advantage of a single particle resolution.
% AO attraction
Addition of polymer can induce inter-particle attractions, which gelation requires.
As the polymer concentration increases, the attraction strength increases.
% Summary
Therefore, colloid – polymer mixtures have both a single particle resolution and tunabilities of inter-particle attractions.

% Explaining previous works on colloidal gelation
% Phase diagram
Previous works have focused on the phase diagram of colloidal gels and revealed that the gelation boundary is close to the boundary of spinodal decomposition.
% Importance of formation process
But open network structures of gels are energetically disfavored and the mechanism to self-assemble network structures, competing with condensation, is still controversial.
% Formation process / simulation works
Numerical simulation works have studied the formation process of gels.
Tanaka and Araki have compared simulations with and without hydrodynamic interactions and suggested that hydrodynamic interactions may play key roles in network formation.
% Define our problem
However, there are little experimental evidences of the gelation ‘ process ’ in colloidal suspensions because the previous method severely limits access to the formation process.
% Our solution
Here, we observe the ‘ entire process ’ of gelation in a single particle level by a new experimental method and reveal that gelation is not a simple condensation but frustrated by hydrodynamic interactions and mechanical tensions.

\section{New method} % Method of salt reservoir cell
% Principle
Colloidal gels require three components in a solvent: colloid, polymer, and salt.
Polymers are added to induce inter-particle attractions, whereas the salt is needed to screen surface charges of colloids.
If the system contains no salt, colloids can hardly aggregate because of the strong electrostatic repulsions.
% Implementation
Figure~\ref{fig:methods}a shows the schematic diagram of our cell system.
Initially, colloid – polymer mixture without salt are incubated into the observation cell.
Next, salt is added into the reservoir cell and observation is started.
After the salt passes through the filter, the surface charges of colloids are screened and colloids start gelation.
% Validity
Figure~\ref{fig:methods}c-h shows an example of gelation.
At t = 0 min, almost all colloids are dispersed by electrostatic repulsions.
At t = 5 min, the salt diffuses into the observation cell and initiates gelation.
At t = 30 min, the system percolates.
By the new method, we can access the entire process of gelation in a single particle level.

\section{Cluster aggregation} % Subject I: Cluster formation
% Topic sentence
Figure~\ref{fig:methods}a shows the phase diagram of all samples.
First of all, we focus on cluster formation since clusters constitute " building blocks " of gels.
% Results of birth
Figure~\ref{fig:fluid_dilute} a shows the compaction dynamics of the clusters with three colloids in the early stage.
The results show that the clusters can hardly accomplish compaction within one Brownian motion time and clusters with four and five colloids show very similar tendency (Supplement).
% Explanation 1) Local energy minimization.
If one assumes that each colloid can move independently by Brownian motion and static short-range attractions are induced between colloids, the clusters with three colloids should reach the compact states within one Brownian motion time.
This explanation contradicts to our results.
% Addressing our question
In other words, some interactions stabilize linear structures, competing with the principle of energy minimization.
% Explanation 2) Electrostatic repulsion.
Although the effect of electrostatic repulsions has been studied, our results are observed after salt screens surface charges and electrostatic repulsions can be negligible in our system.
% Explanation 3) Hydrodynamic interactions.
Thus, the only possible explanation is the effect of hydrodynamic interactions.
Hydrodynamic interactions originate from the incompressivility of the solvent, whose effect between colloids have been demonstrated by both numerical simulations and the experiments of optical tweezers.
For compaction, clusters must squeeze the solvent inside the cluster to the outside.
% Conclusion.
Our results suggest that squeezing process can be the bottleneck of compaction and hydrodynamic interactions enhance linear structures in clusters.

% Results of growth
% topic sentence
To investigate whether clusters can reach compact states in their growing stage, fractal dimension of each time is analysed in Figure~\ref{fig:fluid_dilute}b.
% General explanation about fractal dimension.
In general, compact clusters have df around three, whereas chain-like clusters have df around one.
%Our results of fractal dimensions
Our results show that df increases from 1 in the early stage to 2 in the late stage but df is much lower than three.
% Explanation 1) DLCA
Previously diffusion limited cluster aggregation model has been proposed to explain uncompact structures of clusters, assuming sticky attractions.
But DLCA model predicts that df is always fixed around 1.85, which contradicts to our results.
% Addressing our question
Therefore, other mechanism should decrease df close to 1 from condensation equilibrium.
% Explanation 2) Hydrodynamic interactions
As discussed in the early stage of cluster formation, hydrodynamic interactions can frustrate condensation of clusters.
If clusters form chain-like structures, clusters can both avoid squeezing process and decrease resistance from external flow.
Therefore, structures of df = 1 are hydrodynamically favored though energetically disfavored.
% Conclusion
Our results suggest that hydrodynamic interactions dominate the system in the early stage.
As the cluster aggregation proceeds, each colloid can access to a more compact state, squeezing out the solvent in the cluster, and df gradually increases.

\section{Dilute gels} % Subject II: Dilute gels
% Topic sentence
Next, we focus on the mechanism of gelation in a dilute system.
% Our results
Figure~\ref{fig:general}c-h shows the process of gelation of phi = 7\%.
Clusters grow by connecting with each other and the radius of gyration of the biggest cluster finally becomes comparable to the system size as shown in Figure~\ref{fig:fluid_dilute}c. 
Figure~\ref{fig:fluid_dilute}b shows that fractal dimension of clusters increase from 1 in the early stage to 2 in the late stage as similar with the case of cluster aggregation.
% Addressing our question
One can address a natural question about dilute gels: Why can the system percolate with phi of only 7\%?
% Introduction to effective phi
Number density of colloids has little importance since fractal dimension of the system is much lower than three and it changes during the gelation process.
% Procedure to calculate the effective volume
To calculate the ‘ effective ’ volume fraction of colloid, we replace each cluster with the effective sphere whose radius is equal to the radius gyration of the cluster.
% Results of effective phi
As shown in Figure~\ref{fig:fluid_dilute}, the effective volume fraction increases from 7\% in the early stage to 60\% in the late stage.
% Discuss the mechanism of percolation in a dilute gel
Our results clearly reveal that the system cannot avoid percolation because the effective volume fraction is too high.
The reason for the 10 times increase of the effective phi is that df is much lower than three.
The low df originates from hydrodynamic interactions.
% Conclusion
Therefore, percolation in a dilute system is a consequence of condensation frustrated by hydrodynamic interactions.

\section{Dense gels} % Subject III: Dense gels
% Topic sentence
Gelation in a dense system, on the other hand, behaves different patterns than in a dilute system.
% Results of the entire process of dense gelation
As shown in Figure~\ref{fig:dense}a, the system accomplishes percolation in a few minutes, whereas coarsening process proceeds for several hours.
% Focusing on percolation mechanism
% Results of percolation
When the system percolates at t = 5 min, the averaged number of nearest neighbours is only three and the averaged bond-bond angle is 105 deg.
Thus, the network right after percolated has chain-like structures instead of condensed domains.
% Discussions of percolation
As shown in Figure~\ref{fig:fluid_dilute}a, the aggregated clusters in the early stage have linear structures by the effect of hydrodynamic interactions.
In a dense system, linear clusters are generated simultaneously in a high density.
The clusters connect with each other before they can reach compact states and form chain-like networks within a few Tb.
% Conclusion
Therefore, percolation in a dense system is a consequence of condensation frustrated by hydrodynamic interactions.

% Focusing on coarsening mechanism
The coarsening proceeds for a long term.
% General discussion
So, each colloid can access an energetically favoured structure by thermal fluctuations.
As condensation proceeds, each colloid is captured in a ‘ cage ’ of nearest neighbours and finally arrested in a deep energy potential.
This model is consistent with the previous suggestions based on the glass transition.
% Introduction for elementary process of coarsening
But the elementary process of coarsening has been unknown.
In the early stage at t = 5 min, more than 99\% of all colloids connect with a single network.
When one colloid moves to form a compact domain, the network interconnected with the colloid should cooperatively move.
Therefore, coarsening process is frustrated by mechanical tensions and the mechanism to overcome the frustration for further condensation has great importance in basic research.
% Results of NW cutting
Figure~\ref{fig:dense}b-d shows an elementary process of coarsening, in which networks coarsens by seizing a part of the network.
The single strand is strained between two strong chains.
After stretched straight, the strand is seized and the fragments are integrated into strong chains.
% Conclusion of elementary process of NW coarsening
Therefore, the system can selectively seize weak chains of the network by inducing mechanical tensions and condensation proceeds until the local structures of the network are strong enough.

\section{Conclusion} % Conclusion of this study
% Topic sentence
In this study, we analyse the entire process of colloidal gelation in a single particle level.
% Universality of colloidal gelation
To show the universality of colloidal gelation, Figure~\ref{fig:general} summarizes the processes of all our data of gel samples.
In a dilute system, local condensation proceeds simultaneously as percolation.
In contrast, dense systems accomplish percolation in the early stage, whereas local condensation proceeds until the late stage.
% Conclusion of colloidal gelation
In both cases of gelation, percolation is a consequence of condensation frustrated by hydrodynamic interactions, whereas the coarsening process is frustrated by mechanical tensions.
%General impacts
Generally, colloidal suspensions are model cases of the binary mixtures that consist of small and big components.
Our study shed a new light on not only colloidal gelation but also dynamically asymmetric mixtures, which include polymer solutions and protein solutions.

\section{Materials} % Materials and others
% Materials
We use poly-methyl-methacrylate colloids with its radius of \unit{1.4}{\micro\metre} with steric stabilizer of methacryloxypropyl terminated polydimethylsiloxane ( Glest ) dispersed in a mixture of cis-decalin (Tokyo Kasei) and bromocyclohexane ( Sigma-Aldrich ) that matches both optical index and density of the colloids.
The non-adsorbing polymer is \unit{8.4}{\mega\dalton} polystyrene ( TOSOH ) whose radius of gyration in theta solvent is estimated to \unit{110}{\nano\metre}. 
Here the solvent may be regarded as ``good'' and $25\%–40\%$ swelling of the polymer coils is expected~\cite{Royall2007}. We estimate the range of the interaction potential to \unit{148}{\nano\metre} by direct measurements~\cite{Royall2007}, which corresponds to $35\%$ swelling leading to a polymer-colloid size ratio $q=0.05$.

In the absence of salt, the Debye length is expected to reach \unit{???}{\nano\metre}.
Screening by tetrabutylammonium bromide (Fluka) at saturated concentration  brings down the Debye length to about \unit{13}{\nano\metre}.

% Salt-reservoir system
%% Design of the cell
The observation cell has a thickness of approximately \unit{200}{\micro\metre}, whose volume is approximately 1/400 of the volume of the reservoir.
The filter is ??? with pore size of \unit{100}{\nano\metre}.
%% Experimental procedure
Initially, mixture of colloid and polymer without salt is incubated into the observation cell and solvent without salt is incubated into the reservoir.
The reservoir is half-opened and we exchange the solvent into the solvent with salt.
Then, scan starts within \unit{30}{\second}.
%% Results
We estimate that the diffusion time of salt is the order of \unit{10}{\second} as ???.
In our experiments, the colloids in the top area of scan volume start aggregation \unit{1}{\min} after the colloids in the bottom area started aggregation.
Therefore, salt diffuses into the observation cell within only several $\tau_B$.

% Microscope system
Colloids are fluorescently labeled with rhodamines  and observed three-dimensionally by a laser-scanning confocal microscope (Leica SP-5) equipped with excitation laser with its wavelength of \unit{532}{\nano\metre}.
The scan volume is \unit{82 \times 82 \times 85}{\micro\metre} or larger.
We carefully set the scanning time in order to track more than \unit{98}\% of colloids between two continuous time steps.

% Analysis
%% Calculate center positions of colloids
For single-particle analysis, the center position of each colloid is calculated from the three-dimensional images by the algorithm shown in ???.
Trajectory of each colloid is calculated by the algorithm of ???.
%% Identify 'bond'
Colloid A and B are defined as bonded if the distance between the two colloids is smaller than a threshold.
We define the threshold as the first minimum of $g(r)$ of a typical gel samples and apply it for all samples.
%% Identify 'cluster'
By linking all bonds, all clusters are identified and radius gyration and size of each cluster are calculated.
Fractal dimension is calculated by fitting size $r_g\propto N^{d_f}$.
%% Track clusters
To analyse compaction dynamics of clusters with three colloids, we search trajectory of each colloid such that the size of the cluster that contains the colloid is equal to three for continuous time steps.
%% Colouring the picture of cutting NW
???.

\clearpage
\begin{figure}
	\begin{center}
	\includegraphics{generate-figure0.pdf}
	\end{center}
	\caption{\textbf{Observing gelation.} \textbf{a} Sketch of our experimental setup. The observation cell contains initially colloids, polymer and no salt. \textbf{b} Phase diagram of our system (the line is a guide for the eye). \textbf{c-h} Early stage of gelation observed experimentally (state point is circled in \textbf{b}). Pictures are computer reconstruction of the experimental coordinates coloured by the number of particles in clusters.}
	\label{fig:methods}
\end{figure}

\clearpage
\begin{figure}
	\begin{center}
	\includegraphics{generate-figure1.pdf}
	\end{center}
	\caption{\textbf{Fluid and dilute gel.} \textbf{a} Compaction mechanism of 3-particle-clusters in a fluid. The characteristic time to reach the stable compact cluster is much longer than $\tau_B$. \textbf{b} Effective volume fraction for various percolating and non-percolating samples. Dilute gels reach effective volume fractions comparable to dense phases due to their lack of compactness. \textbf{c-d} Time-evolution of the fractal dimension of the non-percolation clusters below (\textbf{c}) and above (\textbf{d}) the gelation boundary. Insets: typical $d_f$ plots for various times.}
	\label{fig:fluid_dilute}
\end{figure}

\clearpage
\begin{figure}
	\begin{center}
	\includegraphics{generate-figure2.pdf}
	\end{center}
	\caption{\textbf{Gelation in dense samples.} \textbf{a} Typical time evolution of the largest cluster size and of the mean coordination number. Insets: Confocal images (2D) at percolation and at final stage. \textbf{b-d} Typical arm-breaking event, from relaxed, to stretched, to rupture. Particles are drawn to scale and colors indicate potential energies from blue (low) to red (high). The smooth surface is a Gaussian coarse-graining of the network pattern. %\textbf{e-f} Typical loop compaction event.  \textbf{b-f} are top views, thus there is no direct role of sedimentation.
	}
	\label{fig:dense}
\end{figure}

\clearpage
\begin{figure}
	\begin{center}
	%\includegraphics{generate-figure3.pdf}
	\end{center}
	\caption{\textbf{Percolation vs compaction} for the three systems studied here: fluid (not percolating), dilute gel and dense gel.}
	\label{fig:general}
\end{figure}
\end{document}

### 2012-06-18 gel_cond/trunk/generate.tex
The condensation paper as an independent branch from Tsurusawa's thesis

\input{preamble}

\usepackage{pgfplots}
\usepgfplotslibrary{external}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{units}
\usepgflibrary{decorations.shapes, decorations.fractals}
\usetikzlibrary{positioning, plotmarks, matrix}
\tikzexternalize
%\tikzset{external/force remake}
\tikzset{every mark/.append style={scale=0.8}}
\pgfplotsset{every axis/.append style={small}}
\pgfplotsset{compat=1.3}

\begin{document}
\tikzset{external/force remake}
\begin{figure}
	\centering
	\begin{tikzpicture}[
		pic3d/.style={inner sep=0}, %
		lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
		]%
		\begin{scope}[xshift=0.1\textwidth, yshift=-0.025\textwidth]
			%\fill[blue!10] (0.01\textwidth,0) rectangle (0.2\textwidth, 0.19\textwidth);
			\draw (0, 0.12\textwidth) rectangle (0.01\textwidth,0) %
				(0.2\textwidth, 0.12\textwidth) rectangle (0.21\textwidth,0)%
				(0, 0.13\textwidth) rectangle (0.01\textwidth,0.19\textwidth)%
				(0.2\textwidth, 0.13\textwidth) rectangle (0.21\textwidth,0.19\textwidth)%
				(0, 0.19\textwidth) rectangle (0.21\textwidth, 0.195\textwidth);		
			\filldraw[gray] (0, 0.12\textwidth) rectangle (0.038\textwidth, 0.13\textwidth) 
				(0.042\textwidth, 0.13\textwidth) rectangle (0.098\textwidth, 0.12\textwidth)
				(0.102\textwidth, 0.13\textwidth) rectangle (0.158\textwidth, 0.12\textwidth)
				(0.162\textwidth, 0.13\textwidth) rectangle (0.21\textwidth, 0.12\textwidth);
			\fill[green, semitransparent] (0.1\textwidth, 0.17\textwidth) -- (0.06\textwidth, 0.22\textwidth) -- (0.14\textwidth, 0.22\textwidth) -- cycle;
			\filldraw[lightgray] (0.05\textwidth, 0.22\textwidth) arc[start angle=180,delta angle=180,x radius=0.05\textwidth, y radius=0.01\textwidth] --cycle;
			\begin{scope}[radius=0.008\textwidth, ball color=red!80]
				\shade(0.08\textwidth, 0.175\textwidth) circle;
				\shade(0.11\textwidth, 0.16\textwidth) circle;
				\shade(0.05\textwidth, 0.15\textwidth) circle;
				\shade(0.03\textwidth, 0.18\textwidth) circle;
				\shade(0.14\textwidth, 0.14\textwidth) circle;
				\shade(0.16\textwidth, 0.165\textwidth) circle;
			\end{scope}
			\draw[%
				gray, decoration={coil, segment length=0.0025\textwidth, amplitude=0.0025\textwidth},
				]
				(0.06\textwidth, 0.1745\textwidth)
				decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) }
				(0.17\textwidth, 0.1345\textwidth)
				decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) }
				(0.172\textwidth, 0.14\textwidth)
				decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) }
				(0.145\textwidth, 0.16\textwidth)
				decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) }
				(0.19\textwidth, 0.18\textwidth)
				decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) }
				(0.09\textwidth, 0.14\textwidth)
				decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) }
				(0.03\textwidth, 0.15\textwidth)
				decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) }
				;
			\begin{scope}[blue, every node/.style={circle, inner sep=0.002\textwidth, fill}]
				\draw[decorate,decoration={shape backgrounds,shape=circle,shape size=0.002\textwidth}, fill=blue, step=0.01\textwidth] %
				(0.012\textwidth,0) grid (0.19\textwidth, 0.08\textwidth);
				\draw[decorate,decoration={shape backgrounds,shape=circle,shape size=0.002\textwidth}, fill=blue, step=0.017\textwidth] %
				(0.012\textwidth, 0.08\textwidth) grid (0.195\textwidth, 0.115\textwidth);
				%(0.17\textwidth,  0.0745\textwidth) -- (0.145\textwidth, 0.05\textwidth) -- (0.0514\textwidth, 0.09\textwidth)%
				%(0.03\textwidth, 0.045\textwidth) -- (0.07\textwidth, 0.07\textwidth);
			\end{scope}
			\begin{scope}[blue!20,->, line width=0.005\textwidth]
					\draw (0.16\textwidth, 0.08\textwidth) -- (0.16\textwidth, 0.11\textwidth);
					\draw (0.1\textwidth, 0.08\textwidth) -- (0.1\textwidth, 0.11\textwidth);
					\draw (0.04\textwidth, 0.08\textwidth) -- (0.04\textwidth, 0.11\textwidth);
			\end{scope}
			\node[lab, above right=0, inner sep=0] at (0, 0.195\textwidth) {a};
			\begin{scope}[right, font=\footnotesize]
				\node at (0.21\textwidth,0.21\textwidth) {Objective lens};
				\node at (0.21\textwidth,0.17\textwidth) {Observation cell};
				\node at (0.21\textwidth,0.125\textwidth){Filter};
				\node[above right,blue] at (0.21\textwidth,0.08\textwidth) {Salt diffusion};
				\node[above right] at (0.21\textwidth, 0) {Reservoir};
			\end{scope}
		\end{scope}
		\begin{semilogyaxis}[%
			at={(0.5\textwidth,0)}, anchor=left of south west,%
			name={phasediag},%
			width=0.425\textwidth, height=0.3\textwidth,%
			xmin=0, xmax=40, xlabel={$\phi$}, x unit={\%},
			ymin=0.08, ymax=3.5, ylabel={$c_p$}, y unit={\gram\per\liter},%
			ytick={0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,2}, yticklabels={0.1,0.2,,,0.5,,,,,1,2},%
			legend pos=outer north east,%
			legend style={font=\footnotesize},%
			only marks,%
			]%
			\addplot[sharp plot, no marks] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_sg.phd};
			%\addplot[sharp plot, no marks] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_bg.phd};
			\addplot[sharp plot, no marks, dashed] table [x expr=100*\thisrowno{0}, y index=1] {fluidsolid_f.phd};
			\addplot table [x index=1,y index=2] {phase_diag_gel.csv};
			\addplot table [x index=1,y index=2] {phase_diag_fluid.csv};
			\addplot table [x index=1,y index=2] {phase_diag_transient.csv};
			\addplot table [x index=1,y index=2] {phase_diag_binodal.csv};
			\legend{spinodal, binodal, gel, fluid, transient, binodal};
			\node[circle, draw, gray] at (axis cs:7.4, 0.98) (155C) {};
		\end{semilogyaxis}
		\node[lab] at (phasediag.outer north west) {b};

		\begin{scope}[pic3d]
			\node[below left=0 of phasediag.outer south east] (threeD_20min) {\includegraphics[width=0.3\textwidth]{155C_percolation_1645_p2size_t084.png}};
			\node[left=0.01\textwidth of threeD_20min] (threeD_10min){\includegraphics[width=0.3\textwidth]{155C_percolation_1645_p2size_t044.png}};
			\node[left=0.01\textwidth of threeD_10min] (threeD_5min) {\includegraphics[width=0.3\textwidth]{155C_percolation_1645_p2size_t024.png}};
			\node[below=0.01\textwidth of threeD_5min] (threeD_30min) {\includegraphics[width=0.3\textwidth]{155C_1715_ageing_p2size_t00.png}};
			\node[right=0.01\textwidth of threeD_30min] (threeD_40min) {\includegraphics[width=0.3\textwidth]{155C_1715_ageing_p2size_t20.png}};
			\node[right=0.01\textwidth of threeD_40min] (threeD_50min) {\includegraphics[width=0.3\textwidth]{155C_1715_ageing_p2size_t40.png}};
		\end{scope}
		%\node[right=0.01\textwidth of threeD_10min] (threeD_20min){\includegraphics[width=0.3\textwidth]{3d_draft_20min.jpg}};
		\begin{scope}[lab]
			\node at (threeD_5min.north west) {c};
			\node at (threeD_10min.north west) {d};
			\node at (threeD_20min.north west) {e};
			\node at (threeD_30min.north west) {f};
			\node at (threeD_40min.north west) {g};
			\node at (threeD_50min.north west) {h};
		\end{scope}
		\begin{scope}[above right]
			\node at (threeD_5min.south west) {\unit{5}{\minute}};
			\node at (threeD_10min.south west) {\unit{10}{\minute}};
			\node at (threeD_20min.south west) {\unit{20}{\minute}};
			\node at (threeD_30min.south west) {\unit{30}{\minute}};
			\node at (threeD_40min.south west) {\unit{40}{\minute}};
			\node at (threeD_50min.south west) {\unit{50}{\minute}};
		\end{scope}
	\end{tikzpicture}
	\caption{\textbf{Observing gelation.} \textbf{a} Sketch of our experimental setup. The observation cell contains initially colloids, polymer and no salt. \textbf{b} Phase diagram of our system (the line is a guide for the eye). \textbf{c-h} Early stage of gelation observed experimentally (state point is circled in \textbf{b}). Pictures are computer reconstruction of the experimental coordinates coloured by the number of particles in clusters.}
	\label{fig:methods}
\end{figure}
\tikzset{external/force remake=false}

\begin{figure}
	\centering
	\begin{tikzpicture}[
		pic3d/.style={inner sep=0}, %
		lab/.style={below left, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
		every axis/.style={xlabel near ticks, ylabel near ticks, legend cell align=left, legend style={font=\tiny}},%
		]%
		\begin{axis}[%
			width=0.45\textwidth,%
			xlabel={$t/\tau_B$}, xmin=0, xmax=20,%
			ylabel={$R_g/\sigma$}, %ymin=1, %ymax=0.8,%
			]%
			%\node[pic3d, above right] at(axis cs:2.5,1.55) {\includegraphics[width=0.075\textwidth]{N3_0.png}};
			%\node[pic3d, below right] at(axis cs:3,1.45) {\includegraphics[width=0.075\textwidth]{N3_1.png}};
			%\node[pic3d, above left] at(axis cs:20,1.35) {\includegraphics[width=0.075\textwidth]{N3_2.png}};
			\begin{scope}[every node/.style={inner sep=0}]
				\node[circle, ball color=gray] at (axis cs:2.5,1.6) (n3_01){};
				\node[circle, ball color=gray, right=0 of n3_01] (n3_02){};
				\node[circle, ball color=gray, above right= -0.3em and +0.3em of n3_02] (n3_03){};
				\node[circle, ball color=gray] at (axis cs:4,1.4) (n3_11){};
				\node[circle, ball color=gray, below right=-0.3em and 0.3em of n3_11] (n3_12){};
				\node[circle, ball color=gray, above right= +0 and -0 of n3_12] (n3_13){};
				\node[circle, ball color=gray] at (axis cs:18,1.35) (n3_21){};
				\node[circle, ball color=gray, above right=0.2em and -0.3em of n3_21] (n3_22){};
				\node[circle, ball color=gray, right=0 of n3_21] (n3_23){};
			\end{scope}
			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{1}]{cluster_Rg_dynamics_N3.csv};
			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{2}]{cluster_Rg_dynamics_N3.csv};
			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{3}]{cluster_Rg_dynamics_N3.csv};
			\legend{All triplets, Most elongated 20\%, Most compact 20\%};
		\end{axis}
		\begin{semilogxaxis}[%
			at={(0.5\textwidth, 0)},%
			width=0.45\textwidth,%
			xlabel={$t/\tau_B$}, xmin=1, %xmax=200,%
			ylabel={$\phi_\text{eff}$}, ymin=0, ymax=0.8,%
			legend style={legend pos=north west},%
			]%
			\addplot table [x expr=\thisrowno{0}*6-49, y expr=\thisrowno{5}]{201A.csv};
			\addplot table [x expr=(\thisrowno{0}+0.75)*6-45, y expr=\thisrowno{5}]{188B.csv};
			\addplot table [x expr=(\thisrowno{0}+0.75)*6-60, y expr=\thisrowno{5}]{154B.csv};
			\legend{Fluid, Shallow gel, Deep gel};
		\end{semilogxaxis}
		%\node[anchor=south west] at(0.4\textwidth, 0) {\includegraphics[width=0.45\textwidth]{4_EffectiveVolumeFraction_Results.pdf}};
		\begin{semilogxaxis}[%
			at={(0, -0.4\textwidth)},%
			width=0.45\textwidth,%
			xlabel={$t/\tau_B$}, xmin=1, %xmax=160,%
			ylabel={$d_f$}, ymin=1, %ymax=2,%
			legend style={legend pos=south east},%
			no markers,%
			]%
			\addplot table [x expr=\thisrowno{0}/10-49, y expr=\thisrowno{1}]{201A.df};
			%\addplot table [x expr=(\thisrowno{0}+45)/10, y expr=\thisrowno{1}]{155C.df};
			\addplot table [x expr=(\thisrowno{0}+45)/10-45, y expr=\thisrowno{1}]{188B.df};
			\addplot table [x expr=(\thisrowno{0}+45)/10-60, y expr=\thisrowno{1}]{154B.df};
			\legend{Fluid, Shallow gel, Deep gel};
		\end{semilogxaxis}
	\end{tikzpicture}
	\caption{\textbf{Fluid and dilute gel.} \textbf{a} Compaction mechanism of 3-particle-clusters in a fluid. The characteristic time to reach the stable compact cluster is much longer than $\tau_B$. \textbf{b} Effective volume fraction for various percolating and non-percolating samples. Dilute gels reach effective volume fractions comparable to dense phases due to their lack of compactness. \textbf{c-d} Time-evolution of the fractal dimension of the non-percolation clusters below (\textbf{c}) and above (\textbf{d}) the gelation boundary. Insets: typical $d_f$ plots for various times.}
	\label{fig:fluid_dilute}
\end{figure}

%\tikzset{external/force remake}
\begin{figure}
	\centering
	\begin{tikzpicture}[
		pic3d/.style={inner sep=0}, %
		lab/.style={below left, text height=0.8em, text depth=0.2em, font=\Large\bfseries}%
		]%
		\node (im) {\includegraphics[width=0.4\textwidth]{draft_compaction_dense}};
		\node[left=0 of im] {\includegraphics[width=0.25\textwidth]{draft_nwk_dense_perco}};
		\node[right=0 of im] {\includegraphics[width=0.25\textwidth]{draft_nwk_dense_compact}};
		\matrix [below=0of im, inner sep=0.005\textwidth]{%
			\node (arm1) {\includegraphics[width=0.3\textwidth]{gaussian_forces_10.png}};&%
			\node (arm2) {\includegraphics[width=0.3\textwidth]{gaussian_forces_60.png}};&%
			\node (arm3) {\includegraphics[width=0.3\textwidth]{gaussian_forces_65.png}};\\%
			};
		\node[above right=0 of arm1.south west] {$t=0$};
		\node[above right=0 of arm2.south west] {$t=30\tau_B$};
		\node[above right=0 of arm3.south west] {$t=33\tau_B$};
	\end{tikzpicture}
	\caption{\textbf{Gelation in dense samples.} \textbf{a} Typical time evolution of the largest cluster size and of the mean coordination number. Insets: Confocal images (2D) at percolation and at final stage. \textbf{b-d} Typical arm-breaking event, from relaxed, to stretched, to rupture. Particles are drawn to scale and colors indicate potential energies from blue (low) to red (high). The smooth surface is a Gaussian coarse-graining of the network pattern. %\textbf{e-f} Typical loop compaction event.  \textbf{b-f} are top views, thus there is no direct role of sedimentation.
	}
	\label{fig:dense}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{7_GelUniversality}
	\caption{\textbf{Percolation vs compaction} for the three systems studied here: fluid (not percolating), dilute gel and dense gel.}
	\label{fig:general}
\end{figure}
\end{document}

### 2012-06-19 paper.tex
Rephrase Methods and observation of the initial stage

@@
 \author{Hajime Tanaka}
+
+\begin{abstract}
+
+\end{abstract}
+
 \maketitle
 
-\section{Abstract}
-Condensations are universal phenomenon in aggregating molecules.
-The molecules form droplets and crystals as equilibrium states and gels as non-equilibrium states.
-Gels, space-spanning networks with their dynamics arrested, have elasticity and are observed in many systems, including polymers and proteins.
-Since open network structures of gels are energetically disfavoured, the mechanism to self-assemble networks has received considerable attentions.
-Previously, simulation works have aimed reproducing the process of network formation.
-The results of Brownian dynamics simulations, which assume thermal fluctuations and short-range attractions between molecules, have shown formation of droplets in a moderate strength of attractions.
-In contrast, the simulations that also consider hydrodynamic interactions can reconstitute gelation in a moderate strength of attractions, suggesting key roles of hydrodynamic interactions in network formation.
-However, little is known experimentally about the gelation process because the previous method limits access to the process itself.
-Here, we observe the entire process of gelation in a single particle level by a new experimental method and demonstrate that gelation is not a simple condensation but frustrated by hydrodynamic interactions and mechanical tension.
+\section*{Introduction}
 
-\section{Introduction} % Introduction, from wide attentions to specific subjects
-% General attentions
-Gels are space-spanning networks with their dynamics arrested, which cause elasticity and are widely used in our daily life such as food and filter.
-In a scientific viewpoint, gels have received wide attentions because gels are non-equilibrium non-ergodic states.
-% Focusing on 'colloidal gels'
-Among various model systems, colloidal gels have been intensively studied since colloids have a great advantage of a single particle resolution.
-% AO attraction
-Addition of polymer can induce inter-particle attractions, which gelation requires.
-As the polymer concentration increases, the attraction strength increases.
-% Summary
-Therefore, colloid – polymer mixtures have both a single particle resolution and tunabilities of inter-particle attractions.
+\section*{Results}
 
-% Explaining previous works on colloidal gelation
-% Phase diagram
-Previous works have focused on the phase diagram of colloidal gels and revealed that the gelation boundary is close to the boundary of spinodal decomposition.
-% Importance of formation process
-But open network structures of gels are energetically disfavored and the mechanism to self-assemble network structures, competing with condensation, is still controversial.
-% Formation process / simulation works
-Numerical simulation works have studied the formation process of gels.
-Tanaka and Araki have compared simulations with and without hydrodynamic interactions and suggested that hydrodynamic interactions may play key roles in network formation.
-% Define our problem
-However, there are little experimental evidences of the gelation ‘ process ’ in colloidal suspensions because the previous method severely limits access to the formation process.
-% Our solution
-Here, we observe the ‘ entire process ’ of gelation in a single particle level by a new experimental method and reveal that gelation is not a simple condensation but frustrated by hydrodynamic interactions and mechanical tensions.
+\subsection*{Observation of the initial stage}
 
-\section{New method} % Method of salt reservoir cell
-% Principle
-Colloidal gels require three components in a solvent: colloid, polymer, and salt.
-Polymers are added to induce inter-particle attractions, whereas the salt is needed to screen surface charges of colloids.
-If the system contains no salt, colloids can hardly aggregate because of the strong electrostatic repulsions.
-% Implementation
-Figure~\ref{fig:methods}a shows the schematic diagram of our cell system.
-Initially, colloid – polymer mixture without salt are incubated into the observation cell.
-Next, salt is added into the reservoir cell and observation is started.
-After the salt passes through the filter, the surface charges of colloids are screened and colloids start gelation.
-% Validity
-Figure~\ref{fig:methods}c-h shows an example of gelation.
-At t = 0 min, almost all colloids are dispersed by electrostatic repulsions.
-At t = 5 min, the salt diffuses into the observation cell and initiates gelation.
-At t = 30 min, the system percolates.
-By the new method, we can access the entire process of gelation in a single particle level.
+We use a novel experimental setup that allows the observation of the entire process of gelation at a single particle level (see Methods).
+The principle is to introduce salts through a membrane in a charged colloids and non adsorbing polymers suspension (see Fig.~\ref{fig:methods}a).
+The polymers induce a very short range depletion attraction between colloids, however long range electrostatic repulsion between the colloids prevent any aggregation.
+When we introduce salt the charges get screened and attraction suddenly kicks in, eventually leading to the formation of a gel.
+The whole process can take place on the microscope stage and can thus be observed in three dimensions from the very beginning.
+
+Figure~\ref{fig:methods}c-h shows a computer reconstruction from experimental coordinates of a typical gelation experiment.
+We are able to follow the state of the system from a Wigner crystal (Fig.~\ref{fig:methods}c) where the particles are far apart due to repulsion to a fully percolated network (Fig.~\ref{fig:methods}h).
 
@@
 
-\section{Materials} % Materials and others
-% Materials
-We use poly-methyl-methacrylate colloids with its radius of \unit{1.4}{\micro\metre} with steric stabilizer of methacryloxypropyl terminated polydimethylsiloxane ( Glest ) dispersed in a mixture of cis-decalin (Tokyo Kasei) and bromocyclohexane ( Sigma-Aldrich ) that matches both optical index and density of the colloids.
-The non-adsorbing polymer is \unit{8.4}{\mega\dalton} polystyrene ( TOSOH ) whose radius of gyration in theta solvent is estimated to \unit{110}{\nano\metre}. 
-Here the solvent may be regarded as ``good'' and $25\%–40\%$ swelling of the polymer coils is expected~\cite{Royall2007}.
-We estimate the range of the interaction potential to \unit{148}{\nano\metre} by direct measurements~\cite{Royall2007}, which corresponds to $35\%$ swelling leading to a polymer-colloid size ratio $q=0.05$.
+\section*{Methods}
 
-In the absence of salt, the Debye length is expected to reach \unit{???}{\nano\metre}.
-Screening by tetrabutylammonium bromide (Fluka) at saturated concentration  brings down the Debye length to about \unit{13}{\nano\metre}.
+\subsection*{Experimental}
+
+We used \textsc{pmma} (poly(methyl methacrylate)) colloids sterically stabilized with methacryloxypropyl terminated \textsc{pdms}(poly(dimethyl siloxane)) and fluorescently labelled with rhodamine isothiocyanate chemically bonded to the \textsc{pmma}.
+Colloids are dispersed in a mixture of cis-decalin (Tokyo Kasei) and bromocyclohexane (Sigma-Aldrich) that matches both optical index and density of the colloids.
+
+To induce short-ranged depletion attraction, we use polystyrene (TOSOH) of molecular weight \unit{8.4}{\mega\dalton} as non-adsorbing polymer.
+The radius of gyration in theta solvent is estimated to \unit{110}{\nano\metre}.
+Here the solvent may be regarded as ``good'' and a Flory scaling of the measurements of~\cite{lu2008gelation} yields $R_g=\unit{148}{\nano\metre}$.
+
+The data were collected on a Leica SP5 confocal microscope, using \unit{532}{\nano\meter} laser excitation.
+The temperature was controlled on both stage and objective lens, allowing a more precise density matching.
+The scanned volume is at least \unit{82 \times 82 \times 85}{\micro\metre}.
+Standard particle tracking techniques allow us to localise our particles with errors below $1\%$ of a diameter.
+We carefully set the scanning time in order to track more than \unit{98}\% of colloids between two successive time steps.
+
+From direct confocal measurement~\cite{Royall2007, Poon2012}, we estimate the hard-core diameter of our colloids ($\sigma=\unit{2.75}{\micro\metre}$) and the range of the interaction potential (that confirmed our scaling of $R_g$ within $1\%$), leading to a polymer-colloid size ratio $q = 2R_g/\sigma = 0.10(6)$.
+Two particles are considered bonded when their centres are within $\sigma+2R_g$, which corresponds to the first minimum of $g(r)$.
+
+In the absence of salt, the Debye length is expected to reach \unit{100}{\nano\metre} and the (weakly) charged colloids experience a long range electrostatic repulsion.
+We confirm that colloids never come close enough to feel the short-ranged attraction.
+Screening by tetrabutylammonium bromide (Fluka) at saturated concentration brings down the Debye length to about \unit{13}{\nano\metre}, practically discarding the repulsion.
 
@@
 %% Design of the cell
-The observation cell has a thickness of approximately \unit{200}{\micro\metre}, whose volume is approximately 1/400 of the volume of the reservoir.
-The filter is ??? with pore size of \unit{100}{\nano\metre}.
-%% Experimental procedure
-Initially, mixture of colloid and polymer without salt is incubated into the observation cell and solvent without salt is incubated into the reservoir.
-The reservoir is half-opened and we exchange the solvent into the solvent with salt.
-Then, scan starts within \unit{30}{\second}.
-%% Results
-We estimate that the diffusion time of salt is the order of \unit{10}{\second} as ???.
-In our experiments, the colloids in the top area of scan volume start aggregation \unit{1}{\min} after the colloids in the bottom area started aggregation.
-Therefore, salt diffuses into the observation cell within only several $\tau_B$.
+The colloids and polymers are contained in an observation cell ($\unit{1}{\milli\metre^2} \times \unit{200}{\micro\metre}$) in contact with an half-open reservoir approximately 400 larger in volume, via a millipore filter with pore size of \unit{100}{\nano\metre} that allows the salt through but neither polymer nor colloid (see Fig.~\ref{fig:methods}).
 
-% Microscope system
-Colloids are fluorescently labeled with rhodamines  and observed three-dimensionally by a laser-scanning confocal microscope (Leica SP-5) equipped with excitation laser with its wavelength of \unit{532}{\nano\metre}.
-The scan volume is \unit{82 \times 82 \times 85}{\micro\metre} or larger.
-We carefully set the scanning time in order to track more than \unit{98}\% of colloids between two continuous time steps.
+Initially the system is salt-free and colloids repel each-other to form a Wigner crystal~\cite{Royall2003}.
+A super-saturated salt solution at density matching composition is then added to the reservoir, which is immediately sealed to prevent evaporation.
+Our procedure induces practically no solvent flow in the observation cell.
+We confirmed the presence of undissolved salt several days after mixing, indicating that the observation cell was brought to saturation concentration.
+Data acquisition starts within \unit{30}{\second} after salt introduction.
 
-% Analysis
-%% Calculate center positions of colloids
-For single-particle analysis, the center position of each colloid is calculated from the three-dimensional images by the algorithm shown in ???.
-Trajectory of each colloid is calculated by the algorithm of ???.
-%% Identify 'bond'
-Colloid A and B are defined as bonded if the distance between the two colloids is smaller than a threshold.
-We define the threshold as the first minimum of $g(r)$ of a typical gel samples and apply it for all samples.
-%% Identify 'cluster'
-By linking all bonds, all clusters are identified and radius gyration and size of each cluster are calculated.
-Fractal dimension is calculated by fitting size $r_g\propto N^{d_f}$.
+Given the diffusion constants of Bromide and alkyl cation ($6$ and $\unit{2 \times 10^{-10}}{\metre^2\second^{-1}}$~\cite{Campbell2005}), we estimate the characteristic diffusion time of salt from top to bottom of the order of \unit{10}{\second}.
+Therefore, we reach uniform final salt concentration into the observation cell within only a few Brownian times of the colloids.
+Indeed we measured a delay of about \unit{1}{\min} between the aggregation at the bottom and at the top of the cell.
+We define the initial time of the aggregation process when the maximum of the $g(r)$ jumps from the lattice constant of the Wigner crystal to the hard-core diameter $\sigma$.
+
+\subsection*{Analysis}
+
 %% Track clusters

### 2012-06-20 gel_cond/trunk/paper.tex
Equal contribution Simpler description of the protocol in Results. Different from redispersion. bibliography

--- 2012-06-19 paper.tex
@@
 \author{Hideyo Tsurusawa}
+\thanks{These authors contributed equally to this work}
 \author{Mathieu Leocmach}
+\thanks{These authors contributed equally to this work}
 \author{Hajime Tanaka}
+\email{tanaka@iis.u-tokyo.ac.jp}
+\affiliation{ {Institute of Industrial Science, University of Tokyo, 4-6-1 Komaba, Meguro-ku, Tokyo 153-8505, Japan} }
 
@@
 
-We use a novel experimental setup that allows the observation of the entire process of gelation at a single particle level (see Methods).
-The principle is to introduce salts through a membrane in a charged colloids and non adsorbing polymers suspension (see Fig.~\ref{fig:methods}a).
+We use a novel experimental set-up that allows the observation of the entire process of gelation at a single particle level (see Methods).
+The principle is to introduce salt through a membrane in a charged colloids and non adsorbing polymers suspension (see Fig.~\ref{fig:methods}a).
 The polymers induce a very short range depletion attraction between colloids, however long range electrostatic repulsion between the colloids prevent any aggregation.
-When we introduce salt the charges get screened and attraction suddenly kicks in, eventually leading to the formation of a gel.
-The whole process can take place on the microscope stage and can thus be observed in three dimensions from the very beginning.
+When we introduce salt the charges get screened - repulsion is `turned off' - and attraction suddenly become dominant, eventually leading to the formation of a gel.
+The whole process takes place on the microscope stage and can thus be observed in three dimensions from the very beginning.
 
@@
 
+Our protocol is not equivalent to a redispersion of an existing gel at the same state point either by shaking or shear melting~\cite{lu2008gelation,Teece2011,Bartlett2012}.
+It is closer to a quench and to application relevant processes where the sudden addition of a component (e.g.
+salt, acid, depletion agent) induces gelation in an otherwise stable suspension (e.g.
+milk).
+
 \section{Cluster aggregation} % Subject I: Cluster formation
@@
 Figure~\ref{fig:methods}a shows the phase diagram of all samples.
-First of all, we focus on cluster formation since clusters constitute " building blocks " of gels.
+First of all, we focus on cluster formation since clusters constitute ``building blocks'' of gels.
 % Results of birth
@@
 
+\bibliographystyle{naturemag3}
+\bibliography{ico_dyn}
+
 \clearpage

### 2012-06-20 paper.tex
Start discussing spinodal Fleer2008

@@
 
-We use a novel experimental setup that allows the observation of the entire process of gelation at a single particle level (see Methods).
-The principle is to introduce salts through a membrane in a charged colloids and non adsorbing polymers suspension (see Fig.~\ref{fig:methods}a).
-The polymers induce a very short range depletion attraction between colloids, however long range electrostatic repulsion between the colloids prevent any aggregation.
-When we introduce salt the charges get screened and attraction suddenly kicks in, eventually leading to the formation of a gel.
-The whole process can take place on the microscope stage and can thus be observed in three dimensions from the very beginning.
+We use a novel experimental set-up that allows the observation of the entire process of gelation at a single particle level (see Methods).
+In a suspension of sticky colloids with long range repulsion, we suddenly turn off the repulsion.
+The short range attraction become dominant, eventually leading to the formation of a gel.
+The whole process takes place on the microscope stage and can thus be observed in three dimensions from the very beginning.
 
 Figure~\ref{fig:methods}c-h shows a computer reconstruction from experimental coordinates of a typical gelation experiment.
-We are able to follow the state of the system from a Wigner crystal (Fig.~\ref{fig:methods}c) where the particles are far apart due to repulsion to a fully percolated network (Fig.~\ref{fig:methods}h).
+We are able to follow the state of the system from (Fig.~\ref{fig:methods}c) a Wigner crystal where the particles are far apart due to repulsion to (Fig.~\ref{fig:methods}h) a fully percolated network.
+Using this protocol, we explored the phase diagram (Fig.~\ref{fig:methods}b) and found three possible behaviours: permanent gelation as above, transient gelation and cluster formation.
+Transient gelation is characterised by the formation of a percolating network that melts into separate clusters over a few tens of Brownian times (the time needed for an isolated particle to diffuse over its own radius, here about $\unit{10}{second}$).
+
+We observe in Fig.~\ref{fig:methods}b that the spinodal line predicted by the generalized free volume theory~\cite{Fleer2008} corresponds roughly to the boundary between permanent and transient gelation.
+Furthermore, it means that in our system gelation can happen transiently without an underlying spinodal decomposition dynamics, somewhat in contradiction to~\cite{lu2008gelation}.
+
+Our protocol is not equivalent to a redispersion of an existing gel at the same state point either by shaking or shear melting like in  e.g.~\cite{lu2008gelation,Teece2011,Bartlett2012}.
+It is closer to a quench and to application relevant processes where the sudden addition of a component (e.g.
+salt, acid, depletion agent) induces aggregation in an otherwise stable suspension (e.g.
+milk).
 
@@
 From direct confocal measurement~\cite{Royall2007, Poon2012}, we estimate the hard-core diameter of our colloids ($\sigma=\unit{2.75}{\micro\metre}$) and the range of the interaction potential (that confirmed our scaling of $R_g$ within $1\%$), leading to a polymer-colloid size ratio $q = 2R_g/\sigma = 0.10(6)$.
+Spinodal and binodal lines on Fig.~\ref{fig:methods}b are calculated from this size ratio using the generalized free volume theory~\cite{Fleer2008}.
 Two particles are considered bonded when their centres are within $\sigma+2R_g$, which corresponds to the first minimum of $g(r)$.
@@
 ???.
+
+\bibliographystyle{naturemag3}
+\bibliography{ico_dyn}
 

### 2012-07-05 gel_cond/trunk/paper.tex
maximum bond length

@@
 We use a novel experimental set-up that allows the observation of the entire process of gelation at a single particle level (see Methods).
-The principle is to introduce salt through a membrane in a charged colloids and non adsorbing polymers suspension (see Fig.~\ref{fig:methods}a).
-The polymers induce a very short range depletion attraction between colloids, however long range electrostatic repulsion between the colloids prevent any aggregation.
-When we introduce salt the charges get screened - repulsion is `turned off' - and attraction suddenly become dominant, eventually leading to the formation of a gel.
-The whole process takes place on the microscope stage and can thus be observed in three dimensions from the very beginning.
+In a suspension of sticky colloids with long range repulsion, we suddenly turn off the repulsion.
+The short range attraction become dominant, eventually leading to the formation of a gel.
+The whole process takes place on the microscope stage and can thus be observed dynamically in three dimensions from the very beginning.
+
+Our protocol is not equivalent to a redispersion of an existing gel at the same state point either by shaking or shear melting like in  e.g.~\cite{lu2008gelation,Teece2011,Bartlett2012}.
+It is closer to a quench, however we expect differences compared to a quench simulated via molecular or Brownian dynamics, because of the presence of a solvent mediating hydrodynamic interactions~\cite{Furukawa2010}.
+Thus our protocol might be very close to application relevant processes where the sudden addition of a component (e.g.
+salt, acid, depletion agent) induces aggregation in an otherwise stable suspension (e.g.
+milk).
 
 Figure~\ref{fig:methods}c-h shows a computer reconstruction from experimental coordinates of a typical gelation experiment.
-We are able to follow the state of the system from a Wigner crystal (Fig.~\ref{fig:methods}c) where the particles are far apart due to repulsion to a fully percolated network (Fig.~\ref{fig:methods}h).
+We are able to follow the state of the system from (Fig.~\ref{fig:methods}c) a Wigner crystal where the particles are far apart due to repulsion to (Fig.~\ref{fig:methods}h) a fully percolated network.
+Using this protocol, we explored the phase diagram (Fig.~\ref{fig:methods}b) and found three possible behaviours: permanent gelation as above, transient gelation and cluster formation.
+Transient gelation is characterised by the formation of a percolating network that melts into separate clusters over a few tens of Brownian times (the time needed for an isolated particle to diffuse over its own radius, here about $\unit{10}{second}$).
 
-Our protocol is not equivalent to a redispersion of an existing gel at the same state point either by shaking or shear melting~\cite{lu2008gelation,Teece2011,Bartlett2012}.
-It is closer to a quench and to application relevant processes where the sudden addition of a component (e.g.
-salt, acid, depletion agent) induces gelation in an otherwise stable suspension (e.g.
-milk).
+We observe in Fig.~\ref{fig:methods}b that the spinodal line predicted by the generalized free volume theory~\cite{Fleer2008} corresponds roughly to the boundary between permanent and transient gelation.
+Furthermore, it means that in our system gelation can happen transiently without an underlying spinodal decomposition dynamics, somewhat in contradiction to~\cite{lu2008gelation}.
 
@@
 Standard particle tracking techniques allow us to localise our particles with errors below $1\%$ of a diameter.
-We carefully set the scanning time in order to track more than \unit{98}\% of colloids between two successive time steps.
+We carefully set the scanning time in order to be able to follow between two successive time steps all the colloids that stay in the field of view.
 
 From direct confocal measurement~\cite{Royall2007, Poon2012}, we estimate the hard-core diameter of our colloids ($\sigma=\unit{2.75}{\micro\metre}$) and the range of the interaction potential (that confirmed our scaling of $R_g$ within $1\%$), leading to a polymer-colloid size ratio $q = 2R_g/\sigma = 0.10(6)$.
-Two particles are considered bonded when their centres are within $\sigma+2R_g$, which corresponds to the first minimum of $g(r)$.
+Spinodal and binodal lines on Fig.~\ref{fig:methods}b are calculated from this size ratio using the generalized free volume theory~\cite{Fleer2008}.
+In principle two particles are considered bonded when their centres are within $\sigma+2R_g$, however resolution-dependent tracking imprecisions and systematic errors do not give a precise enough estimate of such short distance.
+Therefore we use the first minimum of $g(r)$ as a threshold, which is $\unit{3.40 \text{ or } 3.55}{\micro\metre}$ depending on the resolution.
 

### 2012-08-07 gel_cond/trunk/generate.tex
Add binodal line

@@
 		\end{scope}
+
 		\begin{semilogyaxis}[%
@@
 			\addplot[sharp plot, no marks] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_sg.phd};
-			%\addplot[sharp plot, no marks] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_bg.phd};
-			\addplot[sharp plot, no marks, dashed] table [x expr=100*\thisrowno{0}, y index=1] {fluidsolid_f.phd};
+			\addplot[sharp plot, no marks, dashed] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_bg.phd};
+			\addplot[sharp plot, no marks, dotted] table [x expr=100*\thisrowno{0}, y index=1] {fluidsolid_f.phd};
 			\addplot table [x index=1,y index=2] {phase_diag_gel.csv};
@@
 			\addplot table [x index=1,y index=2] {phase_diag_binodal.csv};
-			\legend{spinodal, binodal, gel, fluid, transient, binodal};
+			\legend{spinodal, binodal, gas-solid, gel, fluid, transient, binodal};
 			\node[circle, draw, gray] at (axis cs:7.4, 0.98) (155C) {};

### 2012-08-07 paper.tex
Add binodal line

@@
 The short range attraction become dominant, eventually leading to the formation of a gel.
-The whole process takes place on the microscope stage and can thus be observed in three dimensions from the very beginning.
+The whole process takes place on the microscope stage and can thus be observed dynamically in three dimensions from the very beginning.
+
+Our protocol is not equivalent to a redispersion of an existing gel at the same state point either by shaking or shear melting like in  e.g.~\cite{lu2008gelation,Teece2011,Bartlett2012}.
+It is closer to a quench, however we expect differences compared to a quench simulated via molecular or Brownian dynamics, because of the presence of a solvent mediating hydrodynamic interactions~\cite{Furukawa2010}.
+Thus our protocol might be very close to application relevant processes where the sudden addition of a component (e.g.
+salt, acid, depletion agent) induces aggregation in an otherwise stable suspension (e.g.
+milk).
 
@@
 Furthermore, it means that in our system gelation can happen transiently without an underlying spinodal decomposition dynamics, somewhat in contradiction to~\cite{lu2008gelation}.
-
-Our protocol is not equivalent to a redispersion of an existing gel at the same state point either by shaking or shear melting like in  e.g.~\cite{lu2008gelation,Teece2011,Bartlett2012}.
-It is closer to a quench and to application relevant processes where the sudden addition of a component (e.g.
-salt, acid, depletion agent) induces aggregation in an otherwise stable suspension (e.g.
-milk).
 
@@
 Standard particle tracking techniques allow us to localise our particles with errors below $1\%$ of a diameter.
-We carefully set the scanning time in order to track more than \unit{98}\% of colloids between two successive time steps.
+We carefully set the scanning time in order to be able to follow between two successive time steps all the colloids that stay in the field of view.
 
@@
 Spinodal and binodal lines on Fig.~\ref{fig:methods}b are calculated from this size ratio using the generalized free volume theory~\cite{Fleer2008}.
-Two particles are considered bonded when their centres are within $\sigma+2R_g$, which corresponds to the first minimum of $g(r)$.
+In principle two particles are considered bonded when their centres are within $\sigma+2R_g$, however resolution-dependent tracking imprecisions and systematic errors do not give a precise enough estimate of such short distance.
+Therefore we use the first minimum of $g(r)$ as a threshold, which is $\unit{3.40 \text{ or } 3.55}{\micro\metre}$ depending on the resolution.
 
@@
 	\caption{\textbf{Observing gelation.} \textbf{a} Sketch of our experimental setup.
-The observation cell contains initially colloids, polymer and no salt.
-\textbf{b} Phase diagram of our system (the line is a guide for the eye).
+The blue arrows stands for the diffusion of the salt through the membrane into the observation cell.
+\textbf{b} Phase diagram of our system.
+Theoretical lines represent the gas-liquid spinodal (full) and binodal (dashed) as well as the gas-solid coexistence.
 \textbf{c-h} Early stage of gelation observed experimentally (state point is circled in \textbf{b}).

### 2014-07-10 gel_cond/trunk/generate.tex
I pruned the phase diagram of the samples who's initial state point was unreliable. I kept the samples which had sedimentation problems in the long time scale.  I marqued with a square the sample made in the "traditional" way (pumped into a capillary after mixing everything in a bottle).
switch to siunitx and prl formatting state point of bond breaking event

@@
 \tikzset{external/force remake}
-\begin{figure}
+\begin{figure*}
 	\centering
@@
 			xmin=0, xmax=40, xlabel={$\phi$}, x unit={\%},
-			ymin=0.08, ymax=3.5, ylabel={$c_p$}, y unit={\gram\per\liter},%
+			ymin=0.08, ymax=3.5, ylabel={$c_p$}, y unit={\si{\gram\per\litre}},%
 			ytick={0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,2}, yticklabels={0.1,0.2,,,0.5,,,,,1,2},%
@@
 			\addplot[sharp plot, no marks, dotted] table [x expr=100*\thisrowno{0}, y index=1] {fluidsolid_f.phd};
+			%\addplot+[forget plot] table [x index=1,y index=2] {phase_diag_capillary.csv};
 			\addplot table [x index=1,y index=2] {phase_diag_gel.csv};
@@
 			\addplot table [x index=1,y index=2] {phase_diag_transient.csv};
-			\addplot table [x index=1,y index=2] {phase_diag_binodal.csv};
-			\legend{spinodal, binodal, gas-solid, gel, fluid, transient, binodal};
+			\legend{spinodal, binodal, gas-solid, gel, fluid, transient};
 			\node[circle, draw, gray] at (axis cs:7.4, 0.98) (155C) {};
+			\node[draw, gray] at (axis cs:30, 1) (Cap1) {};
 		\end{semilogyaxis}
@@
 		\begin{scope}[above right]
-			\node at (threeD_5min.south west) {\unit{5}{\minute}};
-			\node at (threeD_10min.south west) {\unit{10}{\minute}};
-			\node at (threeD_20min.south west) {\unit{20}{\minute}};
-			\node at (threeD_30min.south west) {\unit{30}{\minute}};
-			\node at (threeD_40min.south west) {\unit{40}{\minute}};
-			\node at (threeD_50min.south west) {\unit{50}{\minute}};
+			\node at (threeD_5min.south west) {\SI{5}{\minute}};
+			\node at (threeD_10min.south west) {\SI{10}{\minute}};
+			\node at (threeD_20min.south west) {\SI{20}{\minute}};
+			\node at (threeD_30min.south west) {\SI{30}{\minute}};
+			\node at (threeD_40min.south west) {\SI{40}{\minute}};
+			\node at (threeD_50min.south west) {\SI{50}{\minute}};
 		\end{scope}
@@
 	\label{fig:methods}
-\end{figure}
+\end{figure*}
 \tikzset{external/force remake=false}
@@
 Insets: Confocal images (2D) at percolation and at final stage.
-\textbf{b-d} Typical arm-breaking event, from relaxed, to stretched, to rupture.
+\textbf{b-d} Typical arm-breaking event, from relaxed, to stretched, to rupture ($\phi=29~\%$ and $c_p=\SI{0.71}{\gram\per\litre}$).
 Particles are drawn to scale and colors indicate potential energies from blue (low) to red (high).

### 2014-07-10 gel_cond/trunk/paper.tex
switch to siunitx and prl formatting state point of bond breaking event

@@
 Using this protocol, we explored the phase diagram (Fig.~\ref{fig:methods}b) and found three possible behaviours: permanent gelation as above, transient gelation and cluster formation.
-Transient gelation is characterised by the formation of a percolating network that melts into separate clusters over a few tens of Brownian times (the time needed for an isolated particle to diffuse over its own radius, here about $\unit{10}{second}$).
+Transient gelation is characterised by the formation of a percolating network that melts into separate clusters over a few tens of Brownian times (the time needed for an isolated particle to diffuse over its own radius, here about $\SI{10}{second}$).
 
@@
 
-To induce short-ranged depletion attraction, we use polystyrene (TOSOH) of molecular weight \unit{8.4}{\mega\dalton} as non-adsorbing polymer.
-The radius of gyration in theta solvent is estimated to \unit{110}{\nano\metre}.
-Here the solvent may be regarded as ``good'' and a Flory scaling of the measurements of~\cite{lu2008gelation} yields $R_g=\unit{148}{\nano\metre}$.
+To induce short-ranged depletion attraction, we use polystyrene (TOSOH) of molecular weight \SI{8.4}{\mega\dalton} as non-adsorbing polymer.
+The radius of gyration in theta solvent is estimated to \SI{110}{\nano\metre}.
+Here the solvent may be regarded as ``good'' and a Flory scaling of the measurements of~\cite{lu2008gelation} yields $R_g=\SI{148}{\nano\metre}$.
 
-The data were collected on a Leica SP5 confocal microscope, using \unit{532}{\nano\meter} laser excitation.
+The data were collected on a Leica SP5 confocal microscope, using \SI{532}{\nano\metre} laser excitation.
 The temperature was controlled on both stage and objective lens, allowing a more precise density matching.
-The scanned volume is at least \unit{82 \times 82 \times 85}{\micro\metre}.
+The scanned volume is at least $82 \times 82 \times \SI{85}{\micro\metre}$.
 Standard particle tracking techniques allow us to localise our particles with errors below $1\%$ of a diameter.
@@
 
-From direct confocal measurement~\cite{Royall2007, Poon2012}, we estimate the hard-core diameter of our colloids ($\sigma=\unit{2.75}{\micro\metre}$) and the range of the interaction potential (that confirmed our scaling of $R_g$ within $1\%$), leading to a polymer-colloid size ratio $q = 2R_g/\sigma = 0.10(6)$.
+From direct confocal measurement~\cite{Royall2007, Poon2012}, we estimate the hard-core diameter of our colloids ($\sigma=\SI{2.75}{\micro\metre}$) and the range of the interaction potential (that confirmed our scaling of $R_g$ within $1\%$), leading to a polymer-colloid size ratio $q = 2R_g/\sigma = 0.10(6)$.
 Spinodal and binodal lines on Fig.~\ref{fig:methods}b are calculated from this size ratio using the generalized free volume theory~\cite{Fleer2008}.
 In principle two particles are considered bonded when their centres are within $\sigma+2R_g$, however resolution-dependent tracking imprecisions and systematic errors do not give a precise enough estimate of such short distance.
-Therefore we use the first minimum of $g(r)$ as a threshold, which is $\unit{3.40 \text{ or } 3.55}{\micro\metre}$ depending on the resolution.
+Therefore we use the first minimum of $g(r)$ as a threshold, which is $3.40 \text{ or } \SI{3.55}{\micro\metre}$ depending on the resolution.
 
-In the absence of salt, the Debye length is expected to reach \unit{100}{\nano\metre} and the (weakly) charged colloids experience a long range electrostatic repulsion.
+In the absence of salt, the Debye length is expected to reach \SI{100}{\nano\metre} and the (weakly) charged colloids experience a long range electrostatic repulsion.
 We confirm that colloids never come close enough to feel the short-ranged attraction.
-Screening by tetrabutylammonium bromide (Fluka) at saturated concentration brings down the Debye length to about \unit{13}{\nano\metre}, practically discarding the repulsion.
+Screening by tetrabutylammonium bromide (Fluka) at saturated concentration brings down the Debye length to about \SI{13}{\nano\metre}, practically discarding the repulsion.
 
@@
 %% Design of the cell
-The colloids and polymers are contained in an observation cell ($\unit{1}{\milli\metre^2} \times \unit{200}{\micro\metre}$) in contact with an half-open reservoir approximately 400 larger in volume, via a millipore filter with pore size of \unit{100}{\nano\metre} that allows the salt through but neither polymer nor colloid (see Fig.~\ref{fig:methods}).
+The colloids and polymers are contained in an observation cell ($\SI{1}{\milli\metre^2} \times \SI{200}{\micro\metre}$) in contact with an half-open reservoir approximately 400 larger in volume, via a millipore filter with pore size of \SI{100}{\nano\metre} that allows the salt through but neither polymer nor colloid (see Fig.~\ref{fig:methods}).
 
@@
 We confirmed the presence of undissolved salt several days after mixing, indicating that the observation cell was brought to saturation concentration.
-Data acquisition starts within \unit{30}{\second} after salt introduction.
+Data acquisition starts within \SI{30}{\second} after salt introduction.
 
-Given the diffusion constants of Bromide and alkyl cation ($6$ and $\unit{2 \times 10^{-10}}{\metre^2\second^{-1}}$~\cite{Campbell2005}), we estimate the characteristic diffusion time of salt from top to bottom of the order of \unit{10}{\second}.
+Given the diffusion constants of Bromide and alkyl cation ($6$ and \SI{2e-10}{\metre^2\second^{-1}}~\cite{Campbell2005}), we estimate the characteristic diffusion time of salt from top to bottom of the order of \SI{10}{\second}.
 Therefore, we reach uniform final salt concentration into the observation cell within only a few Brownian times of the colloids.
-Indeed we measured a delay of about \unit{1}{\min} between the aggregation at the bottom and at the top of the cell.
+Indeed we measured a delay of about \SI{1}{\minute} between the aggregation at the bottom and at the top of the cell.
 We define the initial time of the aggregation process when the maximum of the $g(r)$ jumps from the lattice constant of the Wigner crystal to the hard-core diameter $\sigma$.

### 2014-08-19 gel_cond/trunk/generate.tex
figure hydro export figures in figs directory

@@
 \pgfplotsset{every axis/.append style={small}}
-\pgfplotsset{compat=1.3}
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.9}
+\usepgfplotslibrary{groupplots}
+\usepgfplotslibrary{external}
+\tikzexternalize
+\tikzsetexternalprefix{figs/}
 
 \begin{document}
-\tikzset{external/force remake}
+\tikzset{external/force remake=false}
 \begin{figure*}
@@
 \begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{7_GelUniversality}
-	\caption{\textbf{Percolation vs compaction} for the three systems studied here: fluid (not percolating), dilute gel and dense gel.}
+	\tikzset{external/force remake}
+	\tikzsetnextfilename{hydro}
+	\begin{tikzpicture}
+		\begin{groupplot}[%
+			group style={
+				group name=g, group size=1 by 2,
+				},
+			width=\columnwidth,%
+			]
+			\nextgroupplot[
+			xlabel={$t/\tau_B$}, xmin=0, xmax=20,%
+			ylabel={$R_g/\sigma$},
+			]%
+			\begin{scope}[every node/.style={inner sep=0.4em}]
+				\node[circle, ball color=gray] at (axis cs:2.5,1.6) (n3_01){};
+				\node[circle, ball color=gray, right=0 of n3_01] (n3_02){};
+				\node[circle, ball color=gray, above right= -0.4em and +0.4em of n3_02] (n3_03){};
+				\node[circle, ball color=gray] at (axis cs:4,1.4) (n3_11){};
+				\node[circle, ball color=gray, below right=-0.4em and 0.4em of n3_11] (n3_12){};
+				\node[circle, ball color=gray, above right= +0 and -0 of n3_12] (n3_13){};
+				\node[circle, ball color=gray] at (axis cs:18,1.35) (n3_21){};
+				\node[circle, ball color=gray, above right=0.3em and -0.4em of n3_21] (n3_22){};
+				\node[circle, ball color=gray, right=0 of n3_21] (n3_23){};
+			\end{scope}
+			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{1}]{cluster_Rg_dynamics_N3.csv};
+			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{2}]{cluster_Rg_dynamics_N3.csv};
+			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{3}]{cluster_Rg_dynamics_N3.csv};
+			\legend{All triplets, Most elongated 20\%, Most compact 20\%};
+
+		\nextgroupplot[
+			xlabel={angle (degree)}, xmin=0,xmax=180,%
+			ylabel={probability (degree${}^{-2}$)}, ymin=0,
+			no markers,%
+			height=0.6\columnwidth%,
+			]
+			\addplot+[gray!50, fill=gray!50, area legend] file {all.angles} \closedcycle;
+			\addplot file {new.angles};
+			\addplot+[blue] file {alone.angles};
+			\legend{existing, future, isolated};
+
+			%sketch future
+			\fill[radius=0.6em, red!50] (axis cs:20,0.02) circle[] +(0,1.2em) circle[] ++(1.2em,0) circle[] +(-120:1.2em) circle[];
+			\draw[ultra thick] (axis cs:20,0.02) -- ++(1.2em,0) -- +(-120:1.2em);
+			\draw[thick, dotted] (axis cs:20,0.02) +(1.2em,0) -- +(0,1.2em);
+
+			%sketch alone
+			\fill[radius=0.6em, blue!50] (axis cs:90,0.04) circle[] +(-1.2em,0) circle[] +(-120:1.2em) circle[] +(30:1.5em) circle[];
+			\draw[ultra thick] (axis cs:90,0.04) -- +(-1.2em,0) (axis cs:90,0.04)-- +(-120:1.2em);
+			\draw[thick, dotted] (axis cs:90,0.04) -- +(30:1.5em);
+
+		\end{groupplot}
+	\end{tikzpicture}
+	\caption{\textbf{Hydrodynamics} \textbf{a} Evolution of triplet radii of gyration in a non percolating sample ($\phi=4~\%$, $c_p=\SI{1}{\gram\per\litre}$).
+The characteristic time to reach the stable compact cluster is much longer than the Brownian time.
+\textbf{b} Bond angle distribution in a percolating sample ($\phi=8~\%$, $c_p=\SI{1.5}{\gram\per\litre}$) relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue).
+Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles.}
 	\label{fig:general}

### 2014-08-19 generate.tex
Hydro : Label subfigures and tweak spacing

--- 2014-08-19 gel_cond/trunk/generate.tex
@@
 	\tikzsetnextfilename{hydro}
-	\begin{tikzpicture}
+	\begin{tikzpicture}[lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries}]
 		\begin{groupplot}[%
@@
 				group name=g, group size=1 by 2,
+				vertical sep=4em,
 				},
 			width=\columnwidth,%
+			ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
 			]
 			\nextgroupplot[
+			height=0.8\columnwidth-1em,
 			xlabel={$t/\tau_B$}, xmin=0, xmax=20,%
@@
 		\end{groupplot}
+		\node[lab] at (g c1r1.outer north west) {a};
+		\node[lab] at (g c1r2.outer north west) {b};
 	\end{tikzpicture}
@@
 \textbf{b} Bond angle distribution in a percolating sample ($\phi=8~\%$, $c_p=\SI{1.5}{\gram\per\litre}$) relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue).
-Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles.}
+Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles.
+Insets sketch both cases, with present bonds drawn thick and future bonds drawn dotted.}
 	\label{fig:general}

### 2014-08-20 generate.tex
fig:cell_vs_cap - Redesign cell sketch with relative coordinates, use foreach and random points for salt - Phase diagram in linear scale (duh!) with only spinodal, gel, fluid and clusters

@@
 \usepgflibrary{decorations.shapes, decorations.fractals}
-\usetikzlibrary{positioning, plotmarks, matrix}
+\usetikzlibrary{positioning, plotmarks, matrix, fit, shapes.geometric}
 \tikzexternalize
@@
 \begin{figure}
-	\tikzset{external/force remake}
+	%\tikzset{external/force remake}
 	\tikzsetnextfilename{hydro}
@@
 Insets sketch both cases, with present bonds drawn thick and future bonds drawn dotted.}
-	\label{fig:general}
+	\label{fig:hydro}
 \end{figure}
+
+\begin{figure*}
+	\tikzset{external/force remake}
+	\tikzsetnextfilename{cell_vs_cap}
+	\begin{tikzpicture}[
+		pic3d/.style={inner sep=0}, %
+		lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
+		]%
+		%box
+		\draw[every node/.style={draw, inner sep=0, minimum width=0.01\textwidth, minimum height=0.12\textwidth, anchor=south west}] 
+			node (Rrightwall) at (0, 0) {}
+			node (Rleftwall) at (0.2\textwidth, 0) {}
+			[every node/.append style={minimum height=0.06\textwidth}]
+			node (Crightwall) at (0, 0.13\textwidth) {}
+			node (Cleftwall) at (Crightwall.south -| Rleftwall.west) {}
+			(Crightwall.north west) +(0,0.005\textwidth) rectangle (Cleftwall.north east);
+
+		%filtre
+		\foreach \x / \y in {0/0.23, 0.27/0.48, 0.52/0.73, 0.77/1}
+			\fill[gray] ($(Rrightwall.north west)!\x!(Rleftwall.north east)$) rectangle ($(Crightwall.south west)!\y!(Cleftwall.south east)$);
+
+		%laser
+		\node[fill, green, semitransparent, isosceles triangle, anchor=apex, shape border rotate=-90, minimum width=0.08\textwidth, inner sep=0,  isosceles triangle apex angle=75] at ($(Crightwall.north east)!0.4!(Cleftwall.south west)$) (laser) {};
+
+		%lens
+		\filldraw[lightgray] (laser.right corner) arc[start angle=180,delta angle=180,x radius=0.04\textwidth, y radius=0.01\textwidth] --cycle;
+		%colloids
+		\begin{scope}[radius=0.008\textwidth, ball color=red!80]
+			\shade(0.08\textwidth, 0.175\textwidth) circle;
+			\shade(0.11\textwidth, 0.16\textwidth) circle;
+			\shade(0.05\textwidth, 0.15\textwidth) circle;
+			\shade(0.03\textwidth, 0.18\textwidth) circle;
+			\shade(0.14\textwidth, 0.14\textwidth) circle;
+			\shade(0.16\textwidth, 0.165\textwidth) circle;
+		\end{scope}
+
+		%polymers
+		\foreach \x / \y in {0.06/0.1745, 0.17/0.1345, 0.172/0.14, 0.145/0.16, 0.19/0.18, 0.09/0.14, 0.03/0.15} 
+			\draw[%
+			gray, decoration={coil, segment length=0.0025\textwidth, amplitude=0.0025\textwidth},
+			] (\x\textwidth, \y\textwidth)
+			decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) };
+
+		%salt
+		\begin{axis}[
+			at={($(Rrightwall.south east)+(0.75,0.75)$)},
+			width=0.19\textwidth-2*0.75,
+			height=0.115\textwidth,
+			axis lines=none,
+			scale only axis,
+			xmin=-1, xmax=1,ymin=0,ymax=1,
+			]
+			\addplot [blue, only marks, mark=*, samples=1000, mark size=0.75]
+    {rand^2};
+		\end{axis}
+
+		%arrows
+		\foreach \x in {0.25,0.5,0.75}
+			\draw[blue!20,->, line width=0.005\textwidth] ++($(Rrightwall.south west)!\x!(Rleftwall.south east)$) +(0, 0.08\textwidth) -- +(0, 0.11\textwidth);
+
+		%labels
+		\begin{scope}[right, font=\footnotesize]
+			\node[above right=0 of Rleftwall.south east] (Reservoir) {Reservoir};
+			\node[anchor=north west] at (laser.lower side-|Reservoir.west) {Objective lens};
+			\node at (Cleftwall-|Reservoir.west) (oc) {Observation cell};
+			\node[anchor=base west] at (Rleftwall.north-|Reservoir.west){Filter};
+			\node[above right,blue] at (Rleftwall.east-|Reservoir.west) {Salt diffusion};
+			%\node[above right] at (0.21\textwidth, 0) {Reservoir};
+		\end{scope}
+
+		\node[inner sep=0pt,thick,fit=(Rrightwall) (oc) (laser)
+		] (cellsketch) {};
+		\node[lab, below right=0, inner sep=0] at (cellsketch.north west) {a};
+
+		%%%%Phase diagram%%%%
+
+		\begin{axis}[%
+			at={($(cellsketch.north west)+(\textwidth,0)$)}, anchor=outer north east,%
+			name={phasediag},%
+			width=0.425\textwidth, height=0.3\textwidth,%
+			xmin=0, xmax=40, xlabel={$\phi$}, x unit={\%},
+			ymin=0.08, ymax=3.5, ylabel={$c_p$}, y unit={\si{\gram\per\litre}},%
+			%ytick={0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,2}, yticklabels={0.1,0.2,,,0.5,,,,,1,2},%
+			legend pos=north east,%
+			legend style={font=\footnotesize},%
+			only marks,%
+			]%
+			\addplot[sharp plot, no marks] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_sg.phd};
+			%\addplot[sharp plot, no marks, dashed] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_bg.phd};
+			%\addplot[sharp plot, no marks, dotted] table [x expr=100*\thisrowno{0}, y index=1] {fluidsolid_f.phd};
+			%\addplot+[forget plot] table [x index=1,y index=2] {phase_diag_capillary.csv};
+			\addplot table [x index=1,y index=2] {phase_diag_gel.csv};
+			\addplot table [x index=1,y index=2] {phase_diag_fluid.csv};
+			\addplot table [x index=1,y index=2] {phase_diag_clusters.csv};
+			\legend{spinodal, gel, fluid, clusters};
+			\node[circle, draw, gray] at (axis cs:7.4, 0.98) (155C) {};
+			\node[draw, gray] at (axis cs:30, 1) (Cap1) {};
+		\end{axis}
+		\node[lab] at (phasediag.outer north west) {b};
+	\end{tikzpicture}
+	\caption{\textbf{Reservoir cell} \textbf{a} Sketch of our experimental setup.
+The observation cell contains initially colloids, polymer and no salt.
+\textbf{b} Phase diagram.
+\textbf{c-e} Comparison between gels made at the same state point ($\phi=27~\%$, $c_p=\SI{0.75}{\gram\per\litre}$) either in situ (\textbf{c}, blue) or ex situ (\textbf{d}, red).}
+	\label{fig:cell_vs_cap}
+\end{figure*}
 \end{document}

### 2014-08-22 generate.tex
fig:wholeprocess reduced 3D snapshots, porod and qmax

@@
 \begin{figure*}
-	\tikzset{external/force remake}
+	%\tikzset{external/force remake}
 	\tikzsetnextfilename{cell_vs_cap}
@@
 \end{figure*}
+
+\begin{figure*}
+	\tikzset{external/force remake}
+	\tikzsetnextfilename{wholeprocess}
+	\begin{tikzpicture}
+	\begin{groupplot}[
+	group style={
+			group name=g, group size=1 by 2,
+			vertical sep=3em,
+			},
+		width=0.4\textwidth,%
+		height=0.2\textwidth+1em,%
+		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
+		]
+		\nextgroupplot[
+			xlabel={time (min)},
+			ymin=0, ymax=3, ylabel={Porod exponent},]
+		\addplot[no marks, error bars/.cd, y dir=both,y explicit] table[y error index=2] {155C.porod};
+
+		\nextgroupplot[
+			xmode=log, ymode=log,
+			xlabel={$(t-t_0)/\tau_B$},
+			ylabel=$\langle q\rangle\sigma$,
+			ytick={0.6,0.8,1,1.6,2}, yticklabels={0.6, 0.8,1,1.6, 2},
+			]
+		\addplot[only marks] table[x expr=6*(\thisrowno{0}-5)]{155C.qmax};
+		\addplot+[red, no marks, domain=50:300] {6*x^(-1/3)} node[midway, above]{$-1/3$};
+	\end{groupplot}
+
+	\matrix[
+		matrix of nodes, inner sep=0, column sep=0.0125\textwidth, row sep=0.5em,
+		matrix anchor=north west,
+		at={($(g c1r1.outer north east)+(-\textwidth,0)$)},
+		] (m){
+		\SI{5}{\minute} & \SI{10}{\minute} & \SI{20}{\minute} \\
+		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t024s.png}&
+		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t044s.png}&
+		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t084s.png}\\
+		 \SI{30}{\minute} & \SI{40}{\minute} & \SI{50}{\minute}\\
+		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t00s.png}&
+		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t20s.png}&
+		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t40s.png}\\
+		};
+
+	\end{tikzpicture}
+\caption{\textbf{Gelation observed in-situ} in a typical sample ($\phi=7.5~\%$, $c_p=\SI{1}{\gram\per\litre}$).
+Origin of time is salt introduction.
+\textbf{a} Reconstruction of experimental coordinates coloured by the number of particles in clusters.
+\textbf{b} Evolution of Porod exponent.
+\textbf{c} Growth of the characteristic wave number.
+Time origin is shifted to correspond to the melting of the Wigner crystal.}
+\label{fig:wholeprocess}
+\end{figure*}
+
 \end{document}

### 2014-08-27 gel_cond/trunk/generate.tex
Insert snapshots in fig:cell_vs_cap. Add and circle the statepoint of comparision.

@@
 		]%
-		\node (im) {\includegraphics[width=0.4\textwidth]{draft_compaction_dense}};
-		\node[left=0 of im] {\includegraphics[width=0.25\textwidth]{draft_nwk_dense_perco}};
-		\node[right=0 of im] {\includegraphics[width=0.25\textwidth]{draft_nwk_dense_compact}};
+		\node (im) {%\includegraphics[width=0.4\textwidth]{draft_compaction_dense}
+		};
+		\node[left=0 of im] {%\includegraphics[width=0.25\textwidth]{draft_nwk_dense_perco}
+		};
+		\node[right=0 of im] {%\includegraphics[width=0.25\textwidth]{draft_nwk_dense_compact}
+		};
 		\matrix [below=0of im, inner sep=0.005\textwidth]{%
@@
 \begin{figure}
-	\tikzset{external/force remake}
+	%\tikzset{external/force remake}
 	\tikzsetnextfilename{hydro}
-	\begin{tikzpicture}
+	\begin{tikzpicture}[lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries}]
 		\begin{groupplot}[%
@@
 \textbf{b} Bond angle distribution in a percolating sample ($\phi=8~\%$, $c_p=\SI{1.5}{\gram\per\litre}$) relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue).
-Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles.}
-	\label{fig:general}
+Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles.
+Insets sketch both cases, with present bonds drawn thick and future bonds drawn dotted.}
+	\label{fig:hydro}
 \end{figure}
+
+\begin{figure*}
+	\tikzset{external/force remake}
+	\tikzsetnextfilename{cell_vs_cap}
+	\begin{tikzpicture}[
+		pic3d/.style={inner sep=0}, %
+		lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
+		]%
+		%box
+		\draw[every node/.style={draw, inner sep=0, minimum width=0.01\textwidth, minimum height=0.12\textwidth, anchor=south west}] 
+			node (Rrightwall) at (0, 0) {}
+			node (Rleftwall) at (0.2\textwidth, 0) {}
+			[every node/.append style={minimum height=0.06\textwidth}]
+			node (Crightwall) at (0, 0.13\textwidth) {}
+			node (Cleftwall) at (Crightwall.south -| Rleftwall.west) {}
+			(Crightwall.north west) +(0,0.005\textwidth) rectangle (Cleftwall.north east);
+
+		%filtre
+		\foreach \x / \y in {0/0.23, 0.27/0.48, 0.52/0.73, 0.77/1}
+			\fill[gray] ($(Rrightwall.north west)!\x!(Rleftwall.north east)$) rectangle ($(Crightwall.south west)!\y!(Cleftwall.south east)$);
+
+		%laser
+		\node[fill, green, semitransparent, isosceles triangle, anchor=apex, shape border rotate=-90, minimum width=0.08\textwidth, inner sep=0,  isosceles triangle apex angle=75] at ($(Crightwall.north east)!0.4!(Cleftwall.south west)$) (laser) {};
+
+		%lens
+		\filldraw[lightgray] (laser.right corner) arc[start angle=180,delta angle=180,x radius=0.04\textwidth, y radius=0.01\textwidth] --cycle;
+		%colloids
+		\begin{scope}[radius=0.008\textwidth, ball color=red!80]
+			\shade(0.08\textwidth, 0.175\textwidth) circle;
+			\shade(0.11\textwidth, 0.16\textwidth) circle;
+			\shade(0.05\textwidth, 0.15\textwidth) circle;
+			\shade(0.03\textwidth, 0.18\textwidth) circle;
+			\shade(0.14\textwidth, 0.14\textwidth) circle;
+			\shade(0.16\textwidth, 0.165\textwidth) circle;
+		\end{scope}
+
+		%polymers
+		\foreach \x / \y in {0.06/0.1745, 0.17/0.1345, 0.172/0.14, 0.145/0.16, 0.19/0.18, 0.09/0.14, 0.03/0.15} 
+			\draw[%
+			gray, decoration={coil, segment length=0.0025\textwidth, amplitude=0.0025\textwidth},
+			] (\x\textwidth, \y\textwidth)
+			decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) };
+
+		%salt
+		\begin{axis}[
+			at={($(Rrightwall.south east)+(0.75,0.75)$)},
+			width=0.19\textwidth-2*0.75,
+			height=0.115\textwidth,
+			axis lines=none,
+			scale only axis,
+			xmin=-1, xmax=1,ymin=0,ymax=1,
+			]
+			\addplot [blue, only marks, mark=*, samples=1000, mark size=0.75]
+    {rand^2};
+		\end{axis}
+
+		%arrows
+		\foreach \x in {0.25,0.5,0.75}
+			\draw[blue!20,->, line width=0.005\textwidth] ++($(Rrightwall.south west)!\x!(Rleftwall.south east)$) +(0, 0.08\textwidth) -- +(0, 0.11\textwidth);
+
+		%labels
+		\begin{scope}[right, font=\footnotesize]
+			\node[above right=0 of Rleftwall.south east] (Reservoir) {Reservoir};
+			\node[anchor=north west] at (laser.lower side-|Reservoir.west) {Objective lens};
+			\node at (Cleftwall-|Reservoir.west) (oc) {Observation cell};
+			\node[anchor=base west] at (Rleftwall.north-|Reservoir.west){Filter};
+			\node[above right,blue] at (Rleftwall.east-|Reservoir.west) {Salt diffusion};
+			%\node[above right] at (0.21\textwidth, 0) {Reservoir};
+		\end{scope}
+
+		\node[inner sep=0pt,thick,fit=(Rrightwall) (oc) (laser)
+		] (cellsketch) {};
+		\node[lab, below right=0, inner sep=0] at (cellsketch.north west) {a};
+
+		%%%%Capillary vs Reservoir Cell%%%
+		\node[inner sep=0, below right=0 and 1em of cellsketch.north east] (ResSnapshot) {\includegraphics[width=0.2\textwidth]{Res362A_scan2Snapshot1.jpg}};
+		\node[inner sep=0, above right=0 and 1em of cellsketch.south east] (CapSnapshot) {\includegraphics[width=0.2\textwidth]{Cap362_Snapshot1.jpg}};
+		\node[lab,white] at (ResSnapshot.north west) {b};
+		\node[lab,white] at (CapSnapshot.north west) {c};
+
+		%%%%Phase diagram%%%%
+
+		\begin{axis}[%
+			at={($(cellsketch.north west)+(\textwidth,0)$)}, anchor=outer north east,%
+			name={phasediag},%
+			width=0.425\textwidth, height=0.3\textwidth,%
+			xmin=0, xmax=40, xlabel={$\phi$}, x unit={\%},
+			ymin=0.08, ymax=3.5, ylabel={$c_p$}, y unit={\si{\gram\per\litre}},%
+			%ytick={0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,2}, yticklabels={0.1,0.2,,,0.5,,,,,1,2},%
+			legend pos=north east,%
+			legend style={font=\footnotesize},%
+			only marks,%
+			]%
+			\addplot[sharp plot, no marks] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_sg.phd};
+			%\addplot[sharp plot, no marks, dashed] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_bg.phd};
+			%\addplot[sharp plot, no marks, dotted] table [x expr=100*\thisrowno{0}, y index=1] {fluidsolid_f.phd};
+			%\addplot+[forget plot] table [x index=1,y index=2] {phase_diag_capillary.csv};
+			\addplot table [x index=1,y index=2] {phase_diag_gel.csv};
+			\addplot table [x index=1,y index=2] {phase_diag_fluid.csv};
+			\addplot table [x index=1,y index=2] {phase_diag_clusters.csv};
+			\legend{spinodal, gel, fluid, clusters};
+			\node[circle, draw, gray] at (axis cs:7.4, 0.98) (155C) {};
+			\node[draw, gray] at (axis cs:25.7, 1.43) (Cap1) {};
+		\end{axis}
+		\node[lab] at (phasediag.outer north west) {d};
+	\end{tikzpicture}
+	\caption{\textbf{Reservoir cell} \textbf{a} Sketch of our experimental setup.
+The observation cell contains initially colloids, polymer and no salt.
+\textbf{b} Confocal picture of a gel formed in situ ($\phi=25.5~\%$, $c_p=\SI{1.4}{\gram\per\litre}$), \SI{1}{\hour} after gelation.
+\textbf{c} Confocal picture of a gel at the same state point formed ex situ, \SI{1}{\hour} after shear melting.
+\textbf{d} Phase diagram obtained in reservoir cell.
+Spinodal line is obtained from free volume theory.}
+	\label{fig:cell_vs_cap}
+\end{figure*}
+
+\begin{figure*}
+	\tikzset{external/force remake}
+	\tikzsetnextfilename{wholeprocess}
+	\begin{tikzpicture}
+	\begin{groupplot}[
+	group style={
+			group name=g, group size=1 by 2,
+			vertical sep=3em,
+			},
+		width=0.4\textwidth,%
+		height=0.2\textwidth+1em,%
+		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
+		]
+		\nextgroupplot[
+			xlabel={time (min)},
+			ymin=0, ymax=3, ylabel={Porod exponent},]
+		\addplot[no marks, error bars/.cd, y dir=both,y explicit] table[y error index=2] {155C.porod};
+
+		\nextgroupplot[
+			xmode=log, ymode=log,
+			xlabel={$(t-t_0)/\tau_B$},
+			ylabel=$\langle q\rangle\sigma$,
+			ytick={0.6,0.8,1,1.6,2}, yticklabels={0.6, 0.8,1,1.6, 2},
+			]
+		\addplot[only marks] table[x expr=6*(\thisrowno{0}-5)]{155C.qmax};
+		\addplot+[red, no marks, domain=50:300] {6*x^(-1/3)} node[midway, above]{$-1/3$};
+	\end{groupplot}
+
+	\matrix[
+		matrix of nodes, inner sep=0, column sep=0.0125\textwidth, row sep=0.5em,
+		matrix anchor=north west,
+		at={($(g c1r1.outer north east)+(-\textwidth,0)$)},
+		] (m){
+		\SI{5}{\minute} & \SI{10}{\minute} & \SI{20}{\minute} \\
+		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t024s.png}&
+		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t044s.png}&
+		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t084s.png}\\
+		 \SI{30}{\minute} & \SI{40}{\minute} & \SI{50}{\minute}\\
+		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t00s.png}&
+		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t20s.png}&
+		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t40s.png}\\
+		};
+
+	\end{tikzpicture}
+\caption{\textbf{Gelation observed in-situ} in a typical sample ($\phi=7.5~\%$, $c_p=\SI{1}{\gram\per\litre}$).
+Origin of time is salt introduction.
+\textbf{a} Reconstruction of experimental coordinates coloured by the number of particles in clusters.
+\textbf{b} Evolution of Porod exponent.
+\textbf{c} Growth of the characteristic wave number.
+Time origin is shifted to correspond to the melting of the Wigner crystal.}
+\label{fig:wholeprocess}
+\end{figure*}
+
 \end{document}

### 2014-08-27 gel_cond/trunk/generate.tex
Use aspect ratios rather than Porod exponent in fig:wholeprocess. Add labels for subfigures.

@@
 	\tikzsetnextfilename{wholeprocess}
-	\begin{tikzpicture}
+	\begin{tikzpicture}[
+		lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
+		]
 	\begin{groupplot}[
@@
 		\nextgroupplot[
-			xlabel={time (min)},
-			ymin=0, ymax=3, ylabel={Porod exponent},]
-		\addplot[no marks, error bars/.cd, y dir=both,y explicit] table[y error index=2] {155C.porod};
+			xlabel={time (min)}, xmin=0,
+			ymin=0, ymax=1, ylabel={aspect ratio},
+			only marks,]
+		\addplot table {155C_percolation_1645.aspect} node[below left] {$\lambda_3/\lambda_1$};
+		\addplot table[y index=3] {155C_percolation_1645.aspect} node[above left] {$\lambda_2/\lambda_1$};
 
@@
 		};
-
+	\node[lab] at (m.north west) {a};
+	\node[lab] at (g c1r1.outer north west) {b};
+	\node[lab] at (g c1r2.outer north west) {c};
 	\end{tikzpicture}
@@
 \textbf{a} Reconstruction of experimental coordinates coloured by the number of particles in clusters.
-\textbf{b} Evolution of Porod exponent.
+\textbf{b} Evolution of average aspect ratios of cluster containing more than 4 particles.
 \textbf{c} Growth of the characteristic wave number.

### 2014-08-27 gel_cond/trunk/generate.tex
fig:wholeprocess in column. A pannel with S(q) every 150s.

@@
 
-\begin{figure*}
+\begin{figure}
 	\tikzset{external/force remake}
@@
 		]
+	\pgfplotscreateplotcyclelist{earthy}{%
+	black,
+	red!40!black,
+	red!60!black,
+	red!80!black,
+	red,
+	red!80!yellow,
+	red!60!yellow,
+	red!40!yellow,
+	}
 	\begin{groupplot}[
 	group style={
-			group name=g, group size=1 by 2,
-			vertical sep=3em,
+			group name=g, group size=2 by 1,
+			horizontal sep=4em,
 			},
-		width=0.4\textwidth,%
-		height=0.2\textwidth+1em,%
+		width=0.5\columnwidth+1em,%
+		height=10\baselineskip,%
 		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
@@
 		\addplot[only marks] table[x expr=6*(\thisrowno{0}-5)]{155C.qmax};
-		\addplot+[red, no marks, domain=50:300] {6*x^(-1/3)} node[midway, above]{$-1/3$};
+		\addplot+[red, no marks, domain=20:200] {4*x^(-1/3)} node[midway, below left]{$-1/3$};
 	\end{groupplot}
 
+	\begin{axis}[name=Sq,
+		anchor=below south west,
+		at={(g c1r1.above north west)},
+		xmin=0, xmax=13, ymin=0,
+		xlabel=$q\sigma$, ylabel=$S(q)$,
+		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em},
+		scale only axis,
+		width=\columnwidth-3.5em,
+		height=6\baselineskip,
+		no marks, cycle list name=earthy]
+		\foreach \ii in {1,2,...,7}
+			\addplot table[y index=\ii] {155C_every150s.Sqs};
+		\draw[<-] (axis cs:3.1,3.3) -- +(45:1em) node[right]{Wigner};
+		\draw[<-,red!80!black] (axis cs:6.5,1.9) -- +(45:1em) node[right]{Hard sphere};
+		\draw[<-,red!60!yellow] (axis cs:0.8,7.5) -- +(0:1em) node[right]{Gelation};
+	\end{axis}
+
 	\matrix[
-		matrix of nodes, inner sep=0, column sep=0.0125\textwidth, row sep=0.5em,
-		matrix anchor=north west,
-		at={($(g c1r1.outer north east)+(-\textwidth,0)$)},
+		matrix of nodes, inner sep=0, column sep=0.01\textwidth, row sep=0.5em,
+		matrix anchor=south west,
+		%at={($(g c1r1.outer north west)$)},
+		at={($(Sq.outer north west)$)},
 		] (m){
-		\SI{5}{\minute} & \SI{10}{\minute} & \SI{20}{\minute} \\
-		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t024s.png}&
-		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t044s.png}&
-		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t084s.png}\\
-		 \SI{30}{\minute} & \SI{40}{\minute} & \SI{50}{\minute}\\
-		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t00s.png}&
-		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t20s.png}&
-		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t40s.png}\\
+		\SI{5}{\minute} & \SI{10}{\minute} \\
+		\includegraphics[width=0.48\columnwidth]{155C_percolation_1645_p2size_t024s.png}&
+		\includegraphics[width=0.48\columnwidth]{155C_percolation_1645_p2size_t044s.png}\\
+		\SI{20}{\minute} & \SI{30}{\minute}\\
+		\includegraphics[width=0.48\columnwidth]{155C_percolation_1645_p2size_t084s.png} &
+		\includegraphics[width=0.48\columnwidth]{155C_1715_ageing_p2size_t00s.png}\\
+		 \SI{40}{\minute} & \SI{50}{\minute}\\
+		\includegraphics[width=0.48\columnwidth]{155C_1715_ageing_p2size_t20s.png}&
+		\includegraphics[width=0.48\columnwidth]{155C_1715_ageing_p2size_t40s.png}\\
 		};
 	\node[lab] at (m.north west) {a};
-	\node[lab] at (g c1r1.outer north west) {b};
-	\node[lab] at (g c1r2.outer north west) {c};
+	%\node[lab] at (g c1r1.outer north west) {b};
+	%\node[lab] at (g c1r2.outer north west) {c};
 	\end{tikzpicture}
@@
 \label{fig:wholeprocess}
-\end{figure*}
+\end{figure}
 

### 2014-08-28 gel_cond/trunk/generate.tex
aspect ratio of 172A in fig:hydro, remove little balls and legend of (a) Cahn plot instead of aspect ratio in fig:wholeprocess

@@
 \begin{figure}
-	%\tikzset{external/force remake}
+	\tikzset{external/force remake}
 	\tikzsetnextfilename{hydro}
@@
 			group style={
-				group name=g, group size=1 by 2,
-				vertical sep=4em,
+				group name=g, group size=2 by 1,
+				horizontal sep=3em,
 				},
-			width=\columnwidth,%
+			width=0.5\columnwidth+1em,%
+			height=0.5\columnwidth,
 			ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
@@
 			\nextgroupplot[
-			height=0.8\columnwidth-1em,
+			%height=0.8\columnwidth-1em,
 			xlabel={$t/\tau_B$}, xmin=0, xmax=20,%
@@
 			]%
-			\begin{scope}[every node/.style={inner sep=0.4em}]
-				\node[circle, ball color=gray] at (axis cs:2.5,1.6) (n3_01){};
-				\node[circle, ball color=gray, right=0 of n3_01] (n3_02){};
-				\node[circle, ball color=gray, above right= -0.4em and +0.4em of n3_02] (n3_03){};
-				\node[circle, ball color=gray] at (axis cs:4,1.4) (n3_11){};
-				\node[circle, ball color=gray, below right=-0.4em and 0.4em of n3_11] (n3_12){};
-				\node[circle, ball color=gray, above right= +0 and -0 of n3_12] (n3_13){};
-				\node[circle, ball color=gray] at (axis cs:18,1.35) (n3_21){};
-				\node[circle, ball color=gray, above right=0.3em and -0.4em of n3_21] (n3_22){};
-				\node[circle, ball color=gray, right=0 of n3_21] (n3_23){};
-			\end{scope}
-			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{1}]{cluster_Rg_dynamics_N3.csv};
-			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{2}]{cluster_Rg_dynamics_N3.csv};
-			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{3}]{cluster_Rg_dynamics_N3.csv};
-			\legend{All triplets, Most elongated 20\%, Most compact 20\%};
+			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{1}]{cluster_Rg_dynamics_N3.csv} node[pos=0, above right] {all};
+			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{2}]{cluster_Rg_dynamics_N3.csv} node[pos=0, right] {most elongated};
+			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{3}]{cluster_Rg_dynamics_N3.csv} node[pos=0, above right] {least elongated};
+			%\legend{All triplets, Most elongated 20\%, Most compact 20\%};
 
 		\nextgroupplot[
+			%height=0.6\columnwidth,
+			xlabel={$t/\tau_B$}, xmin=0, xmax=400,
+			ymin=0, ymax=1, ylabel={aspect ratio},
+			only marks,]
+		\addplot table[x expr=\thisrowno{0}*6-19] {172A_1206_percolation.aspect} node[below left] {$\lambda_3/\lambda_1$};
+		\addplot table[x expr=\thisrowno{0}*6-19, y index=3] {172A_1206_percolation.aspect} node[above left] {$\lambda_2/\lambda_1$};
+	\end{groupplot}
+
+	\begin{axis}[
+		name=hist,
+		anchor=above north west,
+		at={(g c1r1.below south west)},
 		xlabel={angle (degree)}, xmin=0,xmax=180,%
@@
 		no markers,%
-			height=0.6\columnwidth%,
+		width=\columnwidth,
+		height=0.6\columnwidth,
+		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
 		]
@@
 			\draw[thick, dotted] (axis cs:90,0.04) -- +(30:1.5em);
+		\end{axis}
 
-		\end{groupplot}
 		\node[lab] at (g c1r1.outer north west) {a};
-		\node[lab] at (g c1r2.outer north west) {b};
+		\node[lab] at (g c2r1.outer north west) {b};
 	\end{tikzpicture}
@@
 \end{figure}
+\tikzset{external/force remake=false}
 
@@
 \begin{figure}
-	\tikzset{external/force remake}
+	%\tikzset{external/force remake}
 	\tikzsetnextfilename{wholeprocess}
@@
 		]
+%		\nextgroupplot[
+%			xlabel={time (min)}, xmin=0,
+%			ymin=0, ymax=1, ylabel={aspect ratio},
+%			only marks,]
+%		\addplot table {155C_percolation_1645.aspect} node[below left] {$\lambda_3/\lambda_1$};
+%		\addplot table[y index=3] {155C_percolation_1645.aspect} node[above left] {$\lambda_2/\lambda_1$};
 		\nextgroupplot[
-			xlabel={time (min)}, xmin=0,
-			ymin=0, ymax=1, ylabel={aspect ratio},
-			only marks,]
-		\addplot table {155C_percolation_1645.aspect} node[below left] {$\lambda_3/\lambda_1$};
-		\addplot table[y index=3] {155C_percolation_1645.aspect} node[above left] {$\lambda_2/\lambda_1$};
+			xlabel=$q^2\sigma^2$, xmin=0,
+			ylabel=$A\tau_B/q^2\sigma^2$, ymin=0, ymax=0.2, ytick={0,0.1,0.2},
+			]
+		\addplot[only marks] table[x expr=\thisrowno{0}^2, y expr=\thisrowno{1}/\thisrowno{0}^2] {155C.growth};
+		\addplot[no marks, red, domain=1.6:7] {1.5*(1-0.115*x)/(1+3.62*x)};
 
@@
 			xlabel={$(t-t_0)/\tau_B$},
-			ylabel=$\langle q\rangle\sigma$,
-			ytick={0.6,0.8,1,1.6,2}, yticklabels={0.6, 0.8,1,1.6, 2},
+			ylabel=$\langle q\rangle\sigma$, ymin=0.6,
+			ytick={0.6,0.8,1,1.2,1.6,2}, yticklabels={0.6, 0.8,1,1.2,1.6, 2},
 			]
@@
 		%at={($(g c1r1.outer north west)$)},
-		at={($(Sq.outer north west)$)},
+		at={($(Sq.outer north west)+(0,1em)$)},
 		] (m){
-		\SI{5}{\minute} & \SI{10}{\minute} \\
+		\SI{0}{\minute} & \SI{5}{\minute} \\
 		\includegraphics[width=0.48\columnwidth]{155C_percolation_1645_p2size_t024s.png}&
 		\includegraphics[width=0.48\columnwidth]{155C_percolation_1645_p2size_t044s.png}\\
-		\SI{20}{\minute} & \SI{30}{\minute}\\
+		\SI{15}{\minute} & \SI{25}{\minute}\\
 		\includegraphics[width=0.48\columnwidth]{155C_percolation_1645_p2size_t084s.png} &
 		\includegraphics[width=0.48\columnwidth]{155C_1715_ageing_p2size_t00s.png}\\
-		 \SI{40}{\minute} & \SI{50}{\minute}\\
+		 \SI{35}{\minute} & \SI{45}{\minute}\\
 		\includegraphics[width=0.48\columnwidth]{155C_1715_ageing_p2size_t20s.png}&
@@
 	\node[lab] at (m.north west) {a};
-	%\node[lab] at (g c1r1.outer north west) {b};
-	%\node[lab] at (g c1r2.outer north west) {c};
+	\node[lab] at (Sq.outer north west) {b};
+	\node[lab] at (g c1r1.outer north west) {c};
+	\node[lab] at (g c2r1.outer north west) {d};
 	\end{tikzpicture}
 \caption{\textbf{Gelation observed in-situ} in a typical sample ($\phi=7.5~\%$, $c_p=\SI{1}{\gram\per\litre}$).
-Origin of time is salt introduction.
+Origin of time is the last frame before melting of Wigner crystal.
 \textbf{a} Reconstruction of experimental coordinates coloured by the number of particles in clusters.
-\textbf{b} Evolution of average aspect ratios of cluster containing more than 4 particles.
-\textbf{c} Growth of the characteristic wave number.
-Time origin is shifted to correspond to the melting of the Wigner crystal.}
+\textbf{b} Structure factor evolution (a curve every \SI{150}{\second}).
+\textbf{c} Cahn plot of the initial growth rate $A(q)$.
+The line is a fit by Eq.
+XXX with $\xi=0.11\sigma$ and $\xi_{ve}=3.6\sigma$.
+\textbf{d} Growth of the characteristic wave number.}
 \label{fig:wholeprocess}

### 2014-08-28 gel_cond/trunk/generate.tex
Label, alignement and caption of fig:hydro

@@
 				group name=g, group size=2 by 1,
-				horizontal sep=3em,
+				horizontal sep=4em,
 				},
@@
 			\nextgroupplot[
-			%height=0.8\columnwidth-1em,
 			xlabel={$t/\tau_B$}, xmin=0, xmax=20,%
@@
 		\nextgroupplot[
-			%height=0.6\columnwidth,
+			width=0.5\columnwidth,
 			xlabel={$t/\tau_B$}, xmin=0, xmax=400,
@@
 		\node[lab] at (g c2r1.outer north west) {b};
+		\node[lab] at (hist.outer north west) {c};
 	\end{tikzpicture}
@@
 The characteristic time to reach the stable compact cluster is much longer than the Brownian time.
-\textbf{b} Bond angle distribution in a percolating sample ($\phi=8~\%$, $c_p=\SI{1.5}{\gram\per\litre}$) relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue).
+\textbf{b} Evolution of the aspect ratios of clusters of 4 particles and more in a percolating sample ($\phi=8~\%$, $c_p=\SI{1.5}{\gram\per\litre}$) \textbf{c} Bond angle distribution relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue).
 Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles.

### 2014-08-28 generate.tex
Scale bar in fig:cel_vs_cap xmin=0.1 in qmax

--- 2014-08-20 generate.tex
@@
 			group style={
-				group name=g, group size=1 by 2,
-				vertical sep=4em,
+				group name=g, group size=2 by 1,
+				horizontal sep=4em,
 				},
-			width=\columnwidth,%
+			width=0.5\columnwidth+1em,%
+			height=0.5\columnwidth,
 			ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
@@
 			\nextgroupplot[
-			height=0.8\columnwidth-1em,
 			xlabel={$t/\tau_B$}, xmin=0, xmax=20,%
@@
 			]%
-			\begin{scope}[every node/.style={inner sep=0.4em}]
-				\node[circle, ball color=gray] at (axis cs:2.5,1.6) (n3_01){};
-				\node[circle, ball color=gray, right=0 of n3_01] (n3_02){};
-				\node[circle, ball color=gray, above right= -0.4em and +0.4em of n3_02] (n3_03){};
-				\node[circle, ball color=gray] at (axis cs:4,1.4) (n3_11){};
-				\node[circle, ball color=gray, below right=-0.4em and 0.4em of n3_11] (n3_12){};
-				\node[circle, ball color=gray, above right= +0 and -0 of n3_12] (n3_13){};
-				\node[circle, ball color=gray] at (axis cs:18,1.35) (n3_21){};
-				\node[circle, ball color=gray, above right=0.3em and -0.4em of n3_21] (n3_22){};
-				\node[circle, ball color=gray, right=0 of n3_21] (n3_23){};
-			\end{scope}
-			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{1}]{cluster_Rg_dynamics_N3.csv};
-			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{2}]{cluster_Rg_dynamics_N3.csv};
-			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{3}]{cluster_Rg_dynamics_N3.csv};
-			\legend{All triplets, Most elongated 20\%, Most compact 20\%};
+			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{1}]{cluster_Rg_dynamics_N3.csv} node[pos=0, above right] {all};
+			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{2}]{cluster_Rg_dynamics_N3.csv} node[pos=0, right] {most elongated};
+			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{3}]{cluster_Rg_dynamics_N3.csv} node[pos=0, above right] {least elongated};
+			%\legend{All triplets, Most elongated 20\%, Most compact 20\%};
 
 		\nextgroupplot[
+			width=0.5\columnwidth,
+			xlabel={$t/\tau_B$}, xmin=0, xmax=400,
+			ymin=0, ymax=1, ylabel={aspect ratio},
+			only marks,]
+		\addplot table[x expr=\thisrowno{0}*6-19] {172A_1206_percolation.aspect} node[below left] {$\lambda_3/\lambda_1$};
+		\addplot table[x expr=\thisrowno{0}*6-19, y index=3] {172A_1206_percolation.aspect} node[above left] {$\lambda_2/\lambda_1$};
+	\end{groupplot}
+
+	\begin{axis}[
+		name=hist,
+		anchor=above north west,
+		at={(g c1r1.below south west)},
 		xlabel={angle (degree)}, xmin=0,xmax=180,%
@@
 			\draw[thick, dotted] (axis cs:90,0.04) -- +(30:1.5em);
+		\end{axis}
 
-		\end{groupplot}
 		\node[lab] at (g c1r1.outer north west) {a};
-		\node[lab] at (g c1r2.outer north west) {b};
+		\node[lab] at (g c2r1.outer north west) {b};
+		\node[lab] at (hist.outer north west) {c};
 	\end{tikzpicture}
@@
 \end{figure}
+%\tikzset{external/force remake=false}
 
@@
 
+		%%%%Capillary vs Reservoir Cell%%%
+		\node[inner sep=0, below right=0 and 1em of cellsketch.north east] (ResSnapshot) {\includegraphics[width=0.2\textwidth]{Res362A_scan2Snapshot1.jpg}};
+		\node[inner sep=0, above right=0 and 1em of cellsketch.south east] (CapSnapshot) {\includegraphics[width=0.2\textwidth]{Cap362_Snapshot1.jpg}};
+		\node[lab,white] at (ResSnapshot.north west) {b};
+		\node[lab,white] at (CapSnapshot.north west) {c};
+
 		%%%%Phase diagram%%%%
@@
 			\node[circle, draw, gray] at (axis cs:7.4, 0.98) (155C) {};
-			\node[draw, gray] at (axis cs:30, 1) (Cap1) {};
+			\node[draw, gray] at (axis cs:25.7, 1.43) (Cap1) {};
 		\end{axis}
-		\node[lab] at (phasediag.outer north west) {b};
+		\node[lab] at (phasediag.outer north west) {d};
+
+		%scale bar
+		\draw[ultra thick] node[anchor=south east, inner xsep=0] (sb) at (CapSnapshot.south east |- phasediag.outer south)  {\SI{50}{\micro\metre}} (sb.north east) -- +(-0.069\textwidth,0);
 	\end{tikzpicture}
@@
 The observation cell contains initially colloids, polymer and no salt.
-\textbf{b} Phase diagram.
-\textbf{c-e} Comparison between gels made at the same state point ($\phi=27~\%$, $c_p=\SI{0.75}{\gram\per\litre}$) either in situ (\textbf{c}, blue) or ex situ (\textbf{d}, red).}
+\textbf{b} Confocal picture of a gel formed in situ ($\phi=25.5~\%$, $c_p=\SI{1.4}{\gram\per\litre}$), \SI{1}{\hour} after gelation.
+\textbf{c} Confocal picture of a gel at the same state point formed ex situ, \SI{1}{\hour} after shear melting.
+\textbf{d} Phase diagram obtained in reservoir cell.
+Spinodal line is obtained from free volume theory.}
 	\label{fig:cell_vs_cap}
 \end{figure*}
+
+\begin{figure}
+	\tikzset{external/force remake}
+	\tikzsetnextfilename{wholeprocess}
+	\begin{tikzpicture}[
+		lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
+		]
+	\pgfplotscreateplotcyclelist{earthy}{%
+	black,
+	red!40!black,
+	red!60!black,
+	red!80!black,
+	red,
+	red!80!yellow,
+	red!60!yellow,
+	red!40!yellow,
+	}
+	\begin{groupplot}[
+	group style={
+			group name=g, group size=2 by 1,
+			horizontal sep=4em,
+			},
+		width=0.5\columnwidth+1em,%
+		height=10\baselineskip,%
+		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
+		]
+%		\nextgroupplot[
+%			xlabel={time (min)}, xmin=0,
+%			ymin=0, ymax=1, ylabel={aspect ratio},
+%			only marks,]
+%		\addplot table {155C_percolation_1645.aspect} node[below left] {$\lambda_3/\lambda_1$};
+%		\addplot table[y index=3] {155C_percolation_1645.aspect} node[above left] {$\lambda_2/\lambda_1$};
+		\nextgroupplot[
+			xlabel=$q^2\sigma^2$, xmin=0,
+			ylabel=$A\tau_B/q^2\sigma^2$, ymin=0, ymax=0.2, ytick={0,0.1,0.2},
+			]
+		\addplot[only marks] table[x expr=\thisrowno{0}^2, y expr=\thisrowno{1}/\thisrowno{0}^2] {155C.growth};
+		\addplot[no marks, red, domain=1.6:7] {1.5*(1-0.115*x)/(1+3.62*x)};
+
+		\nextgroupplot[
+			xmode=log, ymode=log,
+			xlabel={$(t-t_0)/\tau_B$}, xmin=1,
+			ylabel=$\langle q\rangle\sigma$, ymin=0.6,
+			ytick={0.6,0.8,1,1.2,1.6,2}, yticklabels={0.6, 0.8,1,1.2,1.6, 2},
+			]
+		\addplot[only marks] table[x expr=6*(\thisrowno{0}-5)]{155C.qmax};
+		\addplot+[red, no marks, domain=20:200] {4*x^(-1/3)} node[midway, below left]{$-1/3$};
+	\end{groupplot}
+
+	\begin{axis}[name=Sq,
+		anchor=below south west,
+		at={(g c1r1.above north west)},
+		xmin=0, xmax=13, ymin=0,
+		xlabel=$q\sigma$, ylabel=$S(q)$,
+		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em},
+		scale only axis,
+		width=\columnwidth-3.5em,
+		height=6\baselineskip,
+		no marks, cycle list name=earthy]
+		\foreach \ii in {1,2,...,7}
+			\addplot table[y index=\ii] {155C_every150s.Sqs};
+		\draw[<-] (axis cs:3.1,3.3) -- +(45:1em) node[right]{Wigner};
+		\draw[<-,red!80!black] (axis cs:6.5,1.9) -- +(45:1em) node[right]{Hard sphere};
+		\draw[<-,red!60!yellow] (axis cs:0.8,7.5) -- +(0:1em) node[right]{Gelation};
+	\end{axis}
+
+	\matrix[
+		matrix of nodes, inner sep=0, column sep=0.01\textwidth, row sep=0.5em,
+		matrix anchor=south west,
+		%at={($(g c1r1.outer north west)$)},
+		at={($(Sq.outer north west)+(0,1em)$)},
+		] (m){
+		\SI{0}{\minute} & \SI{5}{\minute} \\
+		\includegraphics[width=0.48\columnwidth]{155C_percolation_1645_p2size_t024s.png}&
+		\includegraphics[width=0.48\columnwidth]{155C_percolation_1645_p2size_t044s.png}\\
+		\SI{15}{\minute} & \SI{25}{\minute}\\
+		\includegraphics[width=0.48\columnwidth]{155C_percolation_1645_p2size_t084s.png} &
+		\includegraphics[width=0.48\columnwidth]{155C_1715_ageing_p2size_t00s.png}\\
+		 \SI{35}{\minute} & \SI{45}{\minute}\\
+		\includegraphics[width=0.48\columnwidth]{155C_1715_ageing_p2size_t20s.png}&
+		\includegraphics[width=0.48\columnwidth]{155C_1715_ageing_p2size_t40s.png}\\
+		};
+	\node[lab] at (m.north west) {a};
+	\node[lab] at (Sq.outer north west) {b};
+	\node[lab] at (g c1r1.outer north west) {c};
+	\node[lab] at (g c2r1.outer north west) {d};
+	\end{tikzpicture}
+\caption{\textbf{Gelation observed in-situ} in a typical sample ($\phi=7.5~\%$, $c_p=\SI{1}{\gram\per\litre}$).
+Origin of time is the last frame before melting of Wigner crystal.
+\textbf{a} Reconstruction of experimental coordinates coloured by the number of particles in clusters.
+\textbf{b} Structure factor evolution (a curve every \SI{150}{\second}).
+\textbf{c} Cahn plot of the initial growth rate $A(q)$.
+The line is a fit by Eq.
+XXX with $\xi=0.11\sigma$ and $\xi_{ve}=3.6\sigma$.
+\textbf{d} Growth of the characteristic wave number.}
+\label{fig:wholeprocess}
+\end{figure}
+
 \end{document}

### 2014-09-02 generate.tex
fig:breaking

@@
 
+\begin{figure*}
+\tikzset{external/force remake}
+\tikzsetnextfilename{breaking}
+\begin{tikzpicture}[
+	lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
+	]
+	\begin{groupplot}[
+	group style={
+			group name=g, group size=1 by 2,
+			%horizontal sep=4em,
+			},
+		width=0.25\textwidth,%
+		height=8\baselineskip,%
+		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
+		]
+		\nextgroupplot[
+			height=9\baselineskip,%
+			xlabel=$L$, ylabel={count},
+			xmode=log, ymode=log,
+			ymin=1, xmin=1,
+			clip marker paths=true,
+			]
+			\addplot+[only marks] file {172A_broken_length.hist};
+			\addplot+[only marks] file {170A_broken_length.hist};
+			\addplot+[only marks,mark=asterisk, black] file {150A_broken_length.hist};
+			\addplot[domain=1:32, no marks] {1e6/x^3} node[midway, above right] {-3};
+			\addplot[domain=1:10, no marks] {1e4/x^4} node[midway, below left] {-4};
+
+		\nextgroupplot[
+			xlabel=$q_2$, ylabel={$P(q_2)$ [\%]},
+			xmin=0,xmax=1,
+			ymin=0,
+			no marks
+			]
+			\addplot table[y expr=\thisrowno{1}*100] {150A_broken_q2.proba};
+			\addplot table[y expr=\thisrowno{1}*100] {150A_broken_q2_L2.proba};
+	\end{groupplot}
+
+	\matrix[
+		matrix of nodes, inner sep=0, %column sep=0.01\textwidth, 
+		row sep=0.5em,
+		matrix anchor=north west,
+		at={($(g c1r1.outer north east)+(-\textwidth,0)$)},
+		] (m){
+		\SI{0}{\minute} & \SI{16}{\minute} & \SI{22}{\minute} & \SI{30.5}{\minute} & \SI{31}{\minute} & \SI{90}{\minute} \\
+		\includegraphics[width=0.13\textwidth]{breaking_particles_wireframe_t0000s.png}&
+		\includegraphics[width=0.13\textwidth]{breaking_particles_wireframe_t0032s.png}&
+		\includegraphics[width=0.13\textwidth]{breaking_particles_wireframe_t0043s.png}&
+		\includegraphics[width=0.13\textwidth]{breaking_particles_wireframe_t0061s.png}&
+		\includegraphics[width=0.13\textwidth]{breaking_particles_wireframe_t0062s.png}&
+		\includegraphics[width=0.13\textwidth]{breaking_particles_wireframe_t0180s.png}\\
+		\includegraphics[width=0.13\textwidth]{breaking_wireframe_t0000s.png}&
+		\includegraphics[width=0.13\textwidth]{breaking_wireframe_t0032s.png}&
+		\includegraphics[width=0.13\textwidth]{breaking_wireframe_t0043s.png}&
+		\includegraphics[width=0.13\textwidth]{breaking_wireframe_t0061s.png}&
+		\includegraphics[width=0.13\textwidth]{breaking_wireframe_t0062s.png}&
+		\includegraphics[width=0.13\textwidth]{breaking_wireframe_t0180s.png}\\
+		};
+	\node[lab] at (m.north west) {a};
+	\node[lab] at (g c1r1.outer north west) {b};
+	\node[lab] at (g c1r2.left of south west) {c};
+\end{tikzpicture}
+\caption{\textbf{Mechanical tension drives coarsening} 
+\textbf{a} Reconstruction from experimental coordinates ($\phi=29~\%$, $c_p=\SI{0.7}{\gram\per\litre}$) of coarsening process geometry (top) and topology (bottom).
+Particles are drawn to scale and coloured by $q_2$ from blue (low) to red (high).
+The meshed surface is a Gaussian coarse-graining of the network pattern.
+The red line indicates the shortest on-graph path between the two particles of interest.
+\textbf{b} Number of bond breaking function of the future on-graph distance for three state points (after percolation): $\phi=8,\,18,\,29~\%$, $c_p=1.5,\,0.6,\,\SI{0.7}{\gram\per\litre}$ for \textcolor{blue}{$\bullet$}, \textcolor{red}{\tiny$\blacksquare$} and $*$ respectively.
+\textbf{c} Probability for a bond to break during $3\tau_B$ function of bond-centred $q_2$ for all events (blue) and for events with $L>1$ (red) in the same sample as \textbf{a}.
+}
+\label{fig:breaking}
+\end{figure*}
+
 \end{document}

### 2014-09-02 generate.tex
cleanup old figures

@@
 \tikzset{external/force remake=false}
-\begin{figure*}
-	\centering
-	\begin{tikzpicture}[
-		pic3d/.style={inner sep=0}, %
-		lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
-		]%
-		\begin{scope}[xshift=0.1\textwidth, yshift=-0.025\textwidth]
-			%\fill[blue!10] (0.01\textwidth,0) rectangle (0.2\textwidth, 0.19\textwidth);
-			\draw (0, 0.12\textwidth) rectangle (0.01\textwidth,0) %
-				(0.2\textwidth, 0.12\textwidth) rectangle (0.21\textwidth,0)%
-				(0, 0.13\textwidth) rectangle (0.01\textwidth,0.19\textwidth)%
-				(0.2\textwidth, 0.13\textwidth) rectangle (0.21\textwidth,0.19\textwidth)%
-				(0, 0.19\textwidth) rectangle (0.21\textwidth, 0.195\textwidth);		
-			\filldraw[gray] (0, 0.12\textwidth) rectangle (0.038\textwidth, 0.13\textwidth) 
-				(0.042\textwidth, 0.13\textwidth) rectangle (0.098\textwidth, 0.12\textwidth)
-				(0.102\textwidth, 0.13\textwidth) rectangle (0.158\textwidth, 0.12\textwidth)
-				(0.162\textwidth, 0.13\textwidth) rectangle (0.21\textwidth, 0.12\textwidth);
-			\fill[green, semitransparent] (0.1\textwidth, 0.17\textwidth) -- (0.06\textwidth, 0.22\textwidth) -- (0.14\textwidth, 0.22\textwidth) -- cycle;
-			\filldraw[lightgray] (0.05\textwidth, 0.22\textwidth) arc[start angle=180,delta angle=180,x radius=0.05\textwidth, y radius=0.01\textwidth] --cycle;
-			\begin{scope}[radius=0.008\textwidth, ball color=red!80]
-				\shade(0.08\textwidth, 0.175\textwidth) circle;
-				\shade(0.11\textwidth, 0.16\textwidth) circle;
-				\shade(0.05\textwidth, 0.15\textwidth) circle;
-				\shade(0.03\textwidth, 0.18\textwidth) circle;
-				\shade(0.14\textwidth, 0.14\textwidth) circle;
-				\shade(0.16\textwidth, 0.165\textwidth) circle;
-			\end{scope}
-			\draw[%
-				gray, decoration={coil, segment length=0.0025\textwidth, amplitude=0.0025\textwidth},
-				]
-				(0.06\textwidth, 0.1745\textwidth)
-				decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) }
-				(0.17\textwidth, 0.1345\textwidth)
-				decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) }
-				(0.172\textwidth, 0.14\textwidth)
-				decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) }
-				(0.145\textwidth, 0.16\textwidth)
-				decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) }
-				(0.19\textwidth, 0.18\textwidth)
-				decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) }
-				(0.09\textwidth, 0.14\textwidth)
-				decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) }
-				(0.03\textwidth, 0.15\textwidth)
-				decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) }
-				;
-			\begin{scope}[blue, every node/.style={circle, inner sep=0.002\textwidth, fill}]
-				\draw[decorate,decoration={shape backgrounds,shape=circle,shape size=0.002\textwidth}, fill=blue, step=0.01\textwidth] %
-				(0.012\textwidth,0) grid (0.19\textwidth, 0.08\textwidth);
-				\draw[decorate,decoration={shape backgrounds,shape=circle,shape size=0.002\textwidth}, fill=blue, step=0.017\textwidth] %
-				(0.012\textwidth, 0.08\textwidth) grid (0.195\textwidth, 0.115\textwidth);
-				%(0.17\textwidth,  0.0745\textwidth) -- (0.145\textwidth, 0.05\textwidth) -- (0.0514\textwidth, 0.09\textwidth)%
-				%(0.03\textwidth, 0.045\textwidth) -- (0.07\textwidth, 0.07\textwidth);
-			\end{scope}
-			\begin{scope}[blue!20,->, line width=0.005\textwidth]
-					\draw (0.16\textwidth, 0.08\textwidth) -- (0.16\textwidth, 0.11\textwidth);
-					\draw (0.1\textwidth, 0.08\textwidth) -- (0.1\textwidth, 0.11\textwidth);
-					\draw (0.04\textwidth, 0.08\textwidth) -- (0.04\textwidth, 0.11\textwidth);
-			\end{scope}
-			\node[lab, above right=0, inner sep=0] at (0, 0.195\textwidth) {a};
-			\begin{scope}[right, font=\footnotesize]
-				\node at (0.21\textwidth,0.21\textwidth) {Objective lens};
-				\node at (0.21\textwidth,0.17\textwidth) {Observation cell};
-				\node at (0.21\textwidth,0.125\textwidth){Filter};
-				\node[above right,blue] at (0.21\textwidth,0.08\textwidth) {Salt diffusion};
-				\node[above right] at (0.21\textwidth, 0) {Reservoir};
-			\end{scope}
-		\end{scope}
-
-		\begin{semilogyaxis}[%
-			at={(0.5\textwidth,0)}, anchor=left of south west,%
-			name={phasediag},%
-			width=0.425\textwidth, height=0.3\textwidth,%
-			xmin=0, xmax=40, xlabel={$\phi$}, x unit={\%},
-			ymin=0.08, ymax=3.5, ylabel={$c_p$}, y unit={\si{\gram\per\litre}},%
-			ytick={0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,2}, yticklabels={0.1,0.2,,,0.5,,,,,1,2},%
-			legend pos=outer north east,%
-			legend style={font=\footnotesize},%
-			only marks,%
-			]%
-			\addplot[sharp plot, no marks] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_sg.phd};
-			\addplot[sharp plot, no marks, dashed] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_bg.phd};
-			\addplot[sharp plot, no marks, dotted] table [x expr=100*\thisrowno{0}, y index=1] {fluidsolid_f.phd};
-			%\addplot+[forget plot] table [x index=1,y index=2] {phase_diag_capillary.csv};
-			\addplot table [x index=1,y index=2] {phase_diag_gel.csv};
-			\addplot table [x index=1,y index=2] {phase_diag_fluid.csv};
-			\addplot table [x index=1,y index=2] {phase_diag_transient.csv};
-			\legend{spinodal, binodal, gas-solid, gel, fluid, transient};
-			\node[circle, draw, gray] at (axis cs:7.4, 0.98) (155C) {};
-			\node[draw, gray] at (axis cs:30, 1) (Cap1) {};
-		\end{semilogyaxis}
-		\node[lab] at (phasediag.outer north west) {b};
-
-		\begin{scope}[pic3d]
-			\node[below left=0 of phasediag.outer south east] (threeD_20min) {\includegraphics[width=0.3\textwidth]{155C_percolation_1645_p2size_t084.png}};
-			\node[left=0.01\textwidth of threeD_20min] (threeD_10min){\includegraphics[width=0.3\textwidth]{155C_percolation_1645_p2size_t044.png}};
-			\node[left=0.01\textwidth of threeD_10min] (threeD_5min) {\includegraphics[width=0.3\textwidth]{155C_percolation_1645_p2size_t024.png}};
-			\node[below=0.01\textwidth of threeD_5min] (threeD_30min) {\includegraphics[width=0.3\textwidth]{155C_1715_ageing_p2size_t00.png}};
-			\node[right=0.01\textwidth of threeD_30min] (threeD_40min) {\includegraphics[width=0.3\textwidth]{155C_1715_ageing_p2size_t20.png}};
-			\node[right=0.01\textwidth of threeD_40min] (threeD_50min) {\includegraphics[width=0.3\textwidth]{155C_1715_ageing_p2size_t40.png}};
-		\end{scope}
-		%\node[right=0.01\textwidth of threeD_10min] (threeD_20min){\includegraphics[width=0.3\textwidth]{3d_draft_20min.jpg}};
-		\begin{scope}[lab]
-			\node at (threeD_5min.north west) {c};
-			\node at (threeD_10min.north west) {d};
-			\node at (threeD_20min.north west) {e};
-			\node at (threeD_30min.north west) {f};
-			\node at (threeD_40min.north west) {g};
-			\node at (threeD_50min.north west) {h};
-		\end{scope}
-		\begin{scope}[above right]
-			\node at (threeD_5min.south west) {\SI{5}{\minute}};
-			\node at (threeD_10min.south west) {\SI{10}{\minute}};
-			\node at (threeD_20min.south west) {\SI{20}{\minute}};
-			\node at (threeD_30min.south west) {\SI{30}{\minute}};
-			\node at (threeD_40min.south west) {\SI{40}{\minute}};
-			\node at (threeD_50min.south west) {\SI{50}{\minute}};
-		\end{scope}
-	\end{tikzpicture}
-	\caption{\textbf{Observing gelation.} \textbf{a} Sketch of our experimental setup.
-The observation cell contains initially colloids, polymer and no salt.
-\textbf{b} Phase diagram of our system (the line is a guide for the eye).
-\textbf{c-h} Early stage of gelation observed experimentally (state point is circled in \textbf{b}).
-Pictures are computer reconstruction of the experimental coordinates coloured by the number of particles in clusters.}
-	\label{fig:methods}
-\end{figure*}
-\tikzset{external/force remake=false}
-
-\begin{figure}
-	\centering
-	\begin{tikzpicture}[
-		pic3d/.style={inner sep=0}, %
-		lab/.style={below left, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
-		every axis/.style={xlabel near ticks, ylabel near ticks, legend cell align=left, legend style={font=\tiny}},%
-		]%
-		\begin{axis}[%
-			width=0.45\textwidth,%
-			xlabel={$t/\tau_B$}, xmin=0, xmax=20,%
-			ylabel={$R_g/\sigma$}, %ymin=1, %ymax=0.8,%
-			]%
-			%\node[pic3d, above right] at(axis cs:2.5,1.55) {\includegraphics[width=0.075\textwidth]{N3_0.png}};
-			%\node[pic3d, below right] at(axis cs:3,1.45) {\includegraphics[width=0.075\textwidth]{N3_1.png}};
-			%\node[pic3d, above left] at(axis cs:20,1.35) {\includegraphics[width=0.075\textwidth]{N3_2.png}};
-			\begin{scope}[every node/.style={inner sep=0}]
-				\node[circle, ball color=gray] at (axis cs:2.5,1.6) (n3_01){};
-				\node[circle, ball color=gray, right=0 of n3_01] (n3_02){};
-				\node[circle, ball color=gray, above right= -0.3em and +0.3em of n3_02] (n3_03){};
-				\node[circle, ball color=gray] at (axis cs:4,1.4) (n3_11){};
-				\node[circle, ball color=gray, below right=-0.3em and 0.3em of n3_11] (n3_12){};
-				\node[circle, ball color=gray, above right= +0 and -0 of n3_12] (n3_13){};
-				\node[circle, ball color=gray] at (axis cs:18,1.35) (n3_21){};
-				\node[circle, ball color=gray, above right=0.2em and -0.3em of n3_21] (n3_22){};
-				\node[circle, ball color=gray, right=0 of n3_21] (n3_23){};
-			\end{scope}
-			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{1}]{cluster_Rg_dynamics_N3.csv};
-			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{2}]{cluster_Rg_dynamics_N3.csv};
-			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{3}]{cluster_Rg_dynamics_N3.csv};
-			\legend{All triplets, Most elongated 20\%, Most compact 20\%};
-		\end{axis}
-		\begin{semilogxaxis}[%
-			at={(0.5\textwidth, 0)},%
-			width=0.45\textwidth,%
-			xlabel={$t/\tau_B$}, xmin=1, %xmax=200,%
-			ylabel={$\phi_\text{eff}$}, ymin=0, ymax=0.8,%
-			legend style={legend pos=north west},%
-			]%
-			\addplot table [x expr=\thisrowno{0}*6-49, y expr=\thisrowno{5}]{201A.csv};
-			\addplot table [x expr=(\thisrowno{0}+0.75)*6-45, y expr=\thisrowno{5}]{188B.csv};
-			\addplot table [x expr=(\thisrowno{0}+0.75)*6-60, y expr=\thisrowno{5}]{154B.csv};
-			\legend{Fluid, Shallow gel, Deep gel};
-		\end{semilogxaxis}
-		%\node[anchor=south west] at(0.4\textwidth, 0) {\includegraphics[width=0.45\textwidth]{4_EffectiveVolumeFraction_Results.pdf}};
-		\begin{semilogxaxis}[%
-			at={(0, -0.4\textwidth)},%
-			width=0.45\textwidth,%
-			xlabel={$t/\tau_B$}, xmin=1, %xmax=160,%
-			ylabel={$d_f$}, ymin=1, %ymax=2,%
-			legend style={legend pos=south east},%
-			no markers,%
-			]%
-			\addplot table [x expr=\thisrowno{0}/10-49, y expr=\thisrowno{1}]{201A.df};
-			%\addplot table [x expr=(\thisrowno{0}+45)/10, y expr=\thisrowno{1}]{155C.df};
-			\addplot table [x expr=(\thisrowno{0}+45)/10-45, y expr=\thisrowno{1}]{188B.df};
-			\addplot table [x expr=(\thisrowno{0}+45)/10-60, y expr=\thisrowno{1}]{154B.df};
-			\legend{Fluid, Shallow gel, Deep gel};
-		\end{semilogxaxis}
-	\end{tikzpicture}
-	\caption{\textbf{Fluid and dilute gel.} \textbf{a} Compaction mechanism of 3-particle-clusters in a fluid.
-The characteristic time to reach the stable compact cluster is much longer than $\tau_B$.
-\textbf{b} Effective volume fraction for various percolating and non-percolating samples.
-Dilute gels reach effective volume fractions comparable to dense phases due to their lack of compactness.
-\textbf{c-d} Time-evolution of the fractal dimension of the non-percolation clusters below (\textbf{c}) and above (\textbf{d}) the gelation boundary.
-Insets: typical $d_f$ plots for various times.}
-	\label{fig:fluid_dilute}
-\end{figure}
-
-%\tikzset{external/force remake}
-\begin{figure}
-	\centering
-	\begin{tikzpicture}[
-		pic3d/.style={inner sep=0}, %
-		lab/.style={below left, text height=0.8em, text depth=0.2em, font=\Large\bfseries}%
-		]%
-		\node (im) {%\includegraphics[width=0.4\textwidth]{draft_compaction_dense}
-		};
-		\node[left=0 of im] {%\includegraphics[width=0.25\textwidth]{draft_nwk_dense_perco}
-		};
-		\node[right=0 of im] {%\includegraphics[width=0.25\textwidth]{draft_nwk_dense_compact}
-		};
-		\matrix [below=0of im, inner sep=0.005\textwidth]{%
-			\node (arm1) {\includegraphics[width=0.3\textwidth]{gaussian_forces_10.png}};&%
-			\node (arm2) {\includegraphics[width=0.3\textwidth]{gaussian_forces_60.png}};&%
-			\node (arm3) {\includegraphics[width=0.3\textwidth]{gaussian_forces_65.png}};\\%
-			};
-		\node[above right=0 of arm1.south west] {$t=0$};
-		\node[above right=0 of arm2.south west] {$t=30\tau_B$};
-		\node[above right=0 of arm3.south west] {$t=33\tau_B$};
-	\end{tikzpicture}
-	\caption{\textbf{Gelation in dense samples.} \textbf{a} Typical time evolution of the largest cluster size and of the mean coordination number.
-Insets: Confocal images (2D) at percolation and at final stage.
-\textbf{b-d} Typical arm-breaking event, from relaxed, to stretched, to rupture ($\phi=29~\%$ and $c_p=\SI{0.71}{\gram\per\litre}$).
-Particles are drawn to scale and colors indicate potential energies from blue (low) to red (high).
-The smooth surface is a Gaussian coarse-graining of the network pattern.
-%\textbf{e-f} Typical loop compaction event.
-\textbf{b-f} are top views, thus there is no direct role of sedimentation.
-	}
-	\label{fig:dense}
-\end{figure}
-
-\begin{figure}
-	%\tikzset{external/force remake}
-	\tikzsetnextfilename{hydro}
-	\begin{tikzpicture}[lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries}]
-		\begin{groupplot}[%
-			group style={
-				group name=g, group size=2 by 1,
-				horizontal sep=4em,
-				},
-			width=0.5\columnwidth+1em,%
-			height=0.5\columnwidth,
-			ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
-			]
-			\nextgroupplot[
-			xlabel={$t/\tau_B$}, xmin=0, xmax=20,%
-			ylabel={$R_g/\sigma$},
-			]%
-			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{1}]{cluster_Rg_dynamics_N3.csv} node[pos=0, above right] {all};
-			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{2}]{cluster_Rg_dynamics_N3.csv} node[pos=0, right] {most elongated};
-			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{3}]{cluster_Rg_dynamics_N3.csv} node[pos=0, above right] {least elongated};
-			%\legend{All triplets, Most elongated 20\%, Most compact 20\%};
-
-		\nextgroupplot[
-			width=0.5\columnwidth,
-			xlabel={$t/\tau_B$}, xmin=0, xmax=400,
-			ymin=0, ymax=1, ylabel={aspect ratio},
-			only marks,]
-		\addplot table[x expr=\thisrowno{0}*6-19] {172A_1206_percolation.aspect} node[below left] {$\lambda_3/\lambda_1$};
-		\addplot table[x expr=\thisrowno{0}*6-19, y index=3] {172A_1206_percolation.aspect} node[above left] {$\lambda_2/\lambda_1$};
-	\end{groupplot}
-
-	\begin{axis}[
-		name=hist,
-		anchor=above north west,
-		at={(g c1r1.below south west)},
-		xlabel={angle (degree)}, xmin=0,xmax=180,%
-		ylabel={probability (degree${}^{-2}$)}, ymin=0,
-		no markers,%
-		width=\columnwidth,
-		height=0.6\columnwidth,
-		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
-		]
-			\addplot+[gray!50, fill=gray!50, area legend] file {all.angles} \closedcycle;
-			\addplot file {new.angles};
-			\addplot+[blue] file {alone.angles};
-			\legend{existing, future, isolated};
-
-			%sketch future
-			\fill[radius=0.6em, red!50] (axis cs:20,0.02) circle[] +(0,1.2em) circle[] ++(1.2em,0) circle[] +(-120:1.2em) circle[];
-			\draw[ultra thick] (axis cs:20,0.02) -- ++(1.2em,0) -- +(-120:1.2em);
-			\draw[thick, dotted] (axis cs:20,0.02) +(1.2em,0) -- +(0,1.2em);
-
-			%sketch alone
-			\fill[radius=0.6em, blue!50] (axis cs:90,0.04) circle[] +(-1.2em,0) circle[] +(-120:1.2em) circle[] +(30:1.5em) circle[];
-			\draw[ultra thick] (axis cs:90,0.04) -- +(-1.2em,0) (axis cs:90,0.04)-- +(-120:1.2em);
-			\draw[thick, dotted] (axis cs:90,0.04) -- +(30:1.5em);
-		\end{axis}
-
-		\node[lab] at (g c1r1.outer north west) {a};
-		\node[lab] at (g c2r1.outer north west) {b};
-		\node[lab] at (hist.outer north west) {c};
-	\end{tikzpicture}
-	\caption{\textbf{Hydrodynamics} \textbf{a} Evolution of triplet radii of gyration in a non percolating sample ($\phi=4~\%$, $c_p=\SI{1}{\gram\per\litre}$).
-The characteristic time to reach the stable compact cluster is much longer than the Brownian time.
-\textbf{b} Evolution of the aspect ratios of clusters of 4 particles and more in a percolating sample ($\phi=8~\%$, $c_p=\SI{1.5}{\gram\per\litre}$) \textbf{c} Bond angle distribution relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue).
-Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles.
-Insets sketch both cases, with present bonds drawn thick and future bonds drawn dotted.}
-	\label{fig:hydro}
-\end{figure}
-%\tikzset{external/force remake=false}
 
@@
 \end{figure*}
+
+\begin{figure}
+	%\tikzset{external/force remake}
+	\tikzsetnextfilename{hydro}
+	\begin{tikzpicture}[lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries}]
+		\begin{groupplot}[%
+			group style={
+				group name=g, group size=2 by 1,
+				horizontal sep=4em,
+				},
+			width=0.5\columnwidth+1em,%
+			height=0.5\columnwidth,
+			ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
+			]
+			\nextgroupplot[
+			xlabel={$t/\tau_B$}, xmin=0, xmax=20,%
+			ylabel={$R_g/\sigma$},
+			]%
+			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{1}]{cluster_Rg_dynamics_N3.csv} node[pos=0, above right] {all};
+			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{2}]{cluster_Rg_dynamics_N3.csv} node[pos=0, right] {most elongated};
+			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{3}]{cluster_Rg_dynamics_N3.csv} node[pos=0, above right] {least elongated};
+			%\legend{All triplets, Most elongated 20\%, Most compact 20\%};
+
+		\nextgroupplot[
+			width=0.5\columnwidth,
+			xlabel={$t/\tau_B$}, xmin=0, xmax=400,
+			ymin=0, ymax=1, ylabel={aspect ratio},
+			only marks,]
+		\addplot table[x expr=\thisrowno{0}*6-19] {172A_1206_percolation.aspect} node[below left] {$\lambda_3/\lambda_1$};
+		\addplot table[x expr=\thisrowno{0}*6-19, y index=3] {172A_1206_percolation.aspect} node[above left] {$\lambda_2/\lambda_1$};
+	\end{groupplot}
+
+	\begin{axis}[
+		name=hist,
+		anchor=above north west,
+		at={(g c1r1.below south west)},
+		xlabel={angle (degree)}, xmin=0,xmax=180,%
+		ylabel={probability (degree${}^{-2}$)}, ymin=0,
+		no markers,%
+		width=\columnwidth,
+		height=0.6\columnwidth,
+		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
+		]
+			\addplot+[gray!50, fill=gray!50, area legend] file {all.angles} \closedcycle;
+			\addplot file {new.angles};
+			\addplot+[blue] file {alone.angles};
+			\legend{existing, future, isolated};
+
+			%sketch future
+			\fill[radius=0.6em, red!50] (axis cs:20,0.02) circle[] +(0,1.2em) circle[] ++(1.2em,0) circle[] +(-120:1.2em) circle[];
+			\draw[ultra thick] (axis cs:20,0.02) -- ++(1.2em,0) -- +(-120:1.2em);
+			\draw[thick, dotted] (axis cs:20,0.02) +(1.2em,0) -- +(0,1.2em);
+
+			%sketch alone
+			\fill[radius=0.6em, blue!50] (axis cs:90,0.04) circle[] +(-1.2em,0) circle[] +(-120:1.2em) circle[] +(30:1.5em) circle[];
+			\draw[ultra thick] (axis cs:90,0.04) -- +(-1.2em,0) (axis cs:90,0.04)-- +(-120:1.2em);
+			\draw[thick, dotted] (axis cs:90,0.04) -- +(30:1.5em);
+		\end{axis}
+
+		\node[lab] at (g c1r1.outer north west) {a};
+		\node[lab] at (g c2r1.outer north west) {b};
+		\node[lab] at (hist.outer north west) {c};
+	\end{tikzpicture}
+	\caption{\textbf{Hydrodynamics} \textbf{a} Evolution of triplet radii of gyration in a non percolating sample ($\phi=4~\%$, $c_p=\SI{1}{\gram\per\litre}$).
+The characteristic time to reach the stable compact cluster is much longer than the Brownian time.
+\textbf{b} Evolution of the aspect ratios of clusters of 4 particles and more in a percolating sample ($\phi=8~\%$, $c_p=\SI{1.5}{\gram\per\litre}$) \textbf{c} Bond angle distribution relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue).
+Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles.
+Insets sketch both cases, with present bonds drawn thick and future bonds drawn dotted.}
+	\label{fig:hydro}
+\end{figure}
+%\tikzset{external/force remake=false}
 

### 2015-07-21 paper.tex
Start rewrinting the paper.

@@
 \begin{abstract}
-
+A colloidal gel is an important non-ergodic state of matter with a heterogeneous structure, which can have mechanical elasticity and fluidity at the same time.
+This coexistence of solid and fluid properties is unique to gels and crucial in many applications.
+Colloidal gels are known to be formed by phase separation accompanying dynamical arrest of a colloid-rich phase due to glass transition.
+Even at a low colloid volume fraction, the system forms a space-spanning network structure.
+Using confocal microscopy, we follow the entire process of gelation from the very beginning with a single-particle resolution for the first time.
+We switch off long-range Coulomb interactions between charged colloids by injecting salt at $t=0$ through an osmotic membrane and make depletion attractions due to polymers operative.
+This initiates phase demixing without inducing disturbing flow, which is inevitable for a conventional method, i.e., simple mixing of colloids and polymers at $t=0$.
+Our method allows us to experimentally access the role of hydrodynamics in the formation process of a percolated network structure.
+We also succeeded in experimentally revealing an elementary coarsening process of a network, i.e., mechanical-tension-induced breakup of a network and the resulting network coarsening.
+Thus, we clarify the roles of hydrodynamics and mechanics in gelation, which has not been accessed experimentally.
+This would contribute to our fundamental understanding of the physical mechanism of gelation and its structural formation.
 \end{abstract}
@@
 
-We use a novel experimental set-up that allows the observation of the entire process of gelation at a single particle level (see Methods).
-In a suspension of sticky colloids with long range repulsion, we suddenly turn off the repulsion.
-The short range attraction become dominant, eventually leading to the formation of a gel.
-The whole process takes place on the microscope stage and can thus be observed dynamically in three dimensions from the very beginning.
+\begin{figure*}
+	\includegraphics{cell_vs_cap.pdf}
+	\caption{\textbf{Reservoir cell} \textbf{a} Sketch of our experimental setup.
+The observation cell contains initially colloids, polymer and no salt.
+\textbf{b} Confocal picture of a gel formed in situ ($\phi=25.5~\%$, $c_p=\SI{1.4}{\gram\per\litre}$), \SI{1}{\hour} after gelation.
+\textbf{c} Confocal picture of a gel at the same state point formed ex situ, \SI{1}{\hour} after shear melting.
+\textbf{d} Phase diagram obtained in reservoir cell.
+Spinodal line is obtained from free volume theory.
+State points analysed in the text are circled.
+The state point of \textbf{b-c} is highlighted by a square.}
+	\label{fig:cell_vs_cap}
+\end{figure*}
 
-Our protocol is not equivalent to a redispersion of an existing gel at the same state point either by shaking or shear melting like in  e.g.~\cite{lu2008gelation,Teece2011,Bartlett2012}.
-It is closer to a quench, however we expect differences compared to a quench simulated via molecular or Brownian dynamics, because of the presence of a solvent mediating hydrodynamic interactions~\cite{Furukawa2010}.
+We designed an experimental set-up that allows the observation of the entire process of gelation at a single particle level.
+For that, we use a colloidal system that is charge stabilised at long range, has a short range depletion attraction, and is sterically stabilised causing nearly hard sphere repulsion at contact.
+We use sterically stabilised particles of diameter $\sigma=\SI{3}{\micro\metre}$ in a refractive index matching and density matching mixture of organic solvents.
+In weakly polar solvent, here dielectric constant $\epsilon_r = 5\sim6$, Debye screening length is about $\kappa^{-1}=\SI{10}{\micro\metre}$, enough to keep apart even the large colloids suitable for particle-level confocal microscopy~\cite{Royall2003}.
+The short ranged, $\sigma/10$, depletion attraction caused by non-adsorbing polymers is masked by the electrostatic repulsion.
+
+We enclose the suspension in a thin microscopy cell sketched in Figure~\ref{fig:cell_vs_cap}a.
+The bottom wall of the cell is an osmotic membrane providing contact with a long channel full of the same solvent mixture.
+We introduce solid salt at the other end of the channel that we seal immediately.
+Salt dissolution and subsequent migration of the ions along the channel and through the membrane induce screening of the electrostatic repulsion, revealing the depletion potential well.
+This method causes gelation without any solvent flow and allows \textit{in situ} confocal microscopy observation throughout the process.
+
+In Figure~\ref{fig:cell_vs_cap}b and c we show the final structures for two gels prepared at the same state point, one by our protocol, the other by introducing in a capillary an existing gel and thus shear melting it.
+The later is coarser, highlighting that shaking or shear melting protocols~\cite{lu2008gelation,Teece2011,Bartlett2012} are not equivalent to a quench.
+However even in our case we expect differences compared to a quench simulated via molecular or Brownian dynamics, because of the presence of a solvent mediating hydrodynamic interactions~\cite{Furukawa2010}.
+Thus our protocol might be very close to application relevant processes where the sudden addition of a component (e.g.
+salt, acid, depletion agent) induces aggregation in an otherwise stable suspension (e.g.
+milk).
+
+In Figure~\ref{fig:cell_vs_cap}d we show the phase diagram obtained by our protocol.
+We observe three possible behaviours: at low polymer concentration ($c_p<0.2\SI{\gram\per\litre}$) sample fully relax to a fluid state; at very low colloid volume fraction ($\phi<0.05$) and high polymer concentration the particles condense into long-lived well separated clusters as observed in~\cite{Lu2006}; in the rest of the explored phase space we observe a long-lived network.
+We rationalise these observations by superimposing the spinodal line obtained by generalised free volume theory~\cite{Fleer2008}.
+As expectect
+
+Using our protocol, we explored the phase diagram () and found three possible behaviours: permanent gelation as above, transient gelation and cluster formation.
+Transient gelation is characterised by the formation of a percolating network that melts into separate clusters over a few tens of Brownian times (the time needed for an isolated particle to diffuse over its own radius, here about $\SI{10}{second}$).
+
+The  of the gel shown i highlight that our protocol is not equivalent to a redispersion of an existing gel at the same state point either by shaking or shear melting like in  e.g.~\cite{lu2008gelation,Teece2011,Bartlett2012}.
+Our protocol is closer to a quench, however we expect differences compared to a quench simulated via molecular or Brownian dynamics, because of the presence of a solvent mediating hydrodynamic interactions~\cite{Furukawa2010}.
 Thus our protocol might be very close to application relevant processes where the sudden addition of a component (e.g.

### 2015-07-22 paper.tex
Description of fig:cell_vs_cap and fig:wholeprocess Time for ions to diffuse

@@
 \begin{figure*}
-	\includegraphics{cell_vs_cap.pdf}
+	\includegraphics{figs/cell_vs_cap.pdf}
 	\caption{\textbf{Reservoir cell} \textbf{a} Sketch of our experimental setup.
@@
 Salt dissolution and subsequent migration of the ions along the channel and through the membrane induce screening of the electrostatic repulsion, revealing the depletion potential well.
-This method causes gelation without any solvent flow and allows \textit{in situ} confocal microscopy observation throughout the process.
+The time needed for the ions to diffuse from the membrane across the cell thickness is of the same order of magnitude as the Brownian time of the particles $\tau_B=\SI{10}{\second}$.
+This method causes uniform gelation without any solvent flow and allows \textit{in situ} confocal microscopy observation throughout the process.
 
@@
 In Figure~\ref{fig:cell_vs_cap}d we show the phase diagram obtained by our protocol.
-We observe three possible behaviours: at low polymer concentration ($c_p<0.2\SI{\gram\per\litre}$) sample fully relax to a fluid state; at very low colloid volume fraction ($\phi<0.05$) and high polymer concentration the particles condense into long-lived well separated clusters as observed in~\cite{Lu2006}; in the rest of the explored phase space we observe a long-lived network.
+We observe three possible behaviours: at low polymer concentration ($c_p<\SI{0.2}{\gram\per\litre}$) sample fully relax to a fluid state; at very low colloid volume fraction ($\phi<0.05$) and high polymer concentration the particles condense into long-lived well separated clusters as observed in~\cite{Lu2006}; in the rest of the explored phase space we observe a long-lived network.
 We rationalise these observations by superimposing the spinodal line obtained by generalised free volume theory~\cite{Fleer2008}.
-As expectect
 
-Using our protocol, we explored the phase diagram () and found three possible behaviours: permanent gelation as above, transient gelation and cluster formation.
-Transient gelation is characterised by the formation of a percolating network that melts into separate clusters over a few tens of Brownian times (the time needed for an isolated particle to diffuse over its own radius, here about $\SI{10}{second}$).
+XXX discuss differences between theory and experiment. What is cluster phase? XXX
 
-The  of the gel shown i highlight that our protocol is not equivalent to a redispersion of an existing gel at the same state point either by shaking or shear melting like in  e.g.~\cite{lu2008gelation,Teece2011,Bartlett2012}.
-Our protocol is closer to a quench, however we expect differences compared to a quench simulated via molecular or Brownian dynamics, because of the presence of a solvent mediating hydrodynamic interactions~\cite{Furukawa2010}.
-Thus our protocol might be very close to application relevant processes where the sudden addition of a component (e.g.
-salt, acid, depletion agent) induces aggregation in an otherwise stable suspension (e.g.
-milk).
+\begin{figure}
+\includegraphics{figs/wholeprocess.pdf}
+\caption{\textbf{Gelation process} \textbf{a} Reconstruction of experimental coordinates coloured by the number of particles in clusters in a typical sample close to the cluster-gel line ($\phi=7.5~\%$, $c_p=\SI{1}{\gram\per\litre}$).
+Origin of time is the last frame before melting of Wigner crystal.
+\textbf{b} Comparision of system evolution in terms of largest cluster extent and of mean coordination number.
+By increasing density: $\phi=4.2,\,8,\,16,\,27~\%$, $c_p=1,\,1.5,\,1.2,\,\SI{1}{\gram\per\litre}$ for \textcolor{red!40!yellow}{$*$}, \textcolor{red!80!yellow}{$\circ$}, \textcolor{red!80!black}{\tiny$\blacksquare$} and \textcolor{red!40!black}{$\bullet$} respectively.\textbf{c} Growth of the characteristic wave number for the same samples.}
+\label{fig:wholeprocess}
+\end{figure}
 
-Figure~\ref{fig:methods}c-h shows a computer reconstruction from experimental coordinates of a typical gelation experiment.
-We are able to follow the state of the system from (Fig.~\ref{fig:methods}c) a Wigner crystal where the particles are far apart due to repulsion to (Fig.~\ref{fig:methods}h) a fully percolated network.
+Figure~\ref{fig:wholeprocess}a shows a computer reconstruction from experimental coordinates of a typical gelation experiment close to the cluster-gel boundary.
+Immediately before ions enter the cell ($t=0$), the suspension is in a Wigner crystal state where the particles are far apart due to long range repulsion.
+As soon as the charges are screened, the particles begin to aggregate and form clusters that progressively connect to each other while coarsening to finally percolate through the field of view at $t=\SI{35}{\minute}$.
+
+However, this sequence of events is not universal, as shown in Figure~\ref{fig:wholeprocess}b.
+At higher densities, percolation happen first, within the first few $\tau_B$ after charge screening and then coarsening proceed with an increasing average coordination number $\bar{N}_C$.
+At lower densities, percolation never takes place and we observe the compaction of individual clusters.
+
+Universality is recovered when investigating the dynamics of the coarsening process.
+We compute the characteristic wave number $\langle q \rangle$ of the structure factor $S(q)$ and show its temporal evolution in Figure~\ref{fig:wholeprocess}c.
+We confirm the appearance of a low $q$ peak in $S(q)$, see Supplementary Figure XXX, which is characteristic of spinodal decomposition in a system of a conserved order parameter.
+At short times $\langle q \rangle$ shows a plateau indicating that the low $q$ peak builds up at constant wave number.
+At intermediate times, $\langle q \rangle$ scales as $t^{-1/3}$, again coherent with spinodal decomposition kinetics.
+Finally at longer times each sample deviates from the universal slope to form a plateau indicating arrest.
+The more dilute samples arrest sooner.
+
+Our observations indicate that both cluster and gel phases are due to an arrested spinodal decomposition: network-type spinodal for the gel, and droplet-type spinodal for the clusters where the initial state is too far from equicomposition to allow a bicontinuous structure.
+
 Using this protocol, we explored the phase diagram (Fig.~\ref{fig:methods}b) and found three possible behaviours: permanent gelation as above, transient gelation and cluster formation.
@@
 \bibliography{ico_dyn}
-
-\clearpage
-\begin{figure}
-	\begin{center}
-	\includegraphics{generate-figure0.pdf}
-	\end{center}
-	\caption{\textbf{Observing gelation.} \textbf{a} Sketch of our experimental setup.
-The blue arrows stands for the diffusion of the salt through the membrane into the observation cell.
-\textbf{b} Phase diagram of our system.
-Theoretical lines represent the gas-liquid spinodal (full) and binodal (dashed) as well as the gas-solid coexistence.
-\textbf{c-h} Early stage of gelation observed experimentally (state point is circled in \textbf{b}).
-Pictures are computer reconstruction of the experimental coordinates coloured by the number of particles in clusters.}
-	\label{fig:methods}
-\end{figure}
-
-\clearpage
-\begin{figure}
-	\begin{center}
-	\includegraphics{generate-figure1.pdf}
-	\end{center}
-	\caption{\textbf{Fluid and dilute gel.} \textbf{a} Compaction mechanism of 3-particle-clusters in a fluid.
-The characteristic time to reach the stable compact cluster is much longer than $\tau_B$.
-\textbf{b} Effective volume fraction for various percolating and non-percolating samples.
-Dilute gels reach effective volume fractions comparable to dense phases due to their lack of compactness.
-\textbf{c-d} Time-evolution of the fractal dimension of the non-percolation clusters below (\textbf{c}) and above (\textbf{d}) the gelation boundary.
-Insets: typical $d_f$ plots for various times.}
-	\label{fig:fluid_dilute}
-\end{figure}
-
-\clearpage
-\begin{figure}
-	\begin{center}
-	\includegraphics{generate-figure2.pdf}
-	\end{center}
-	\caption{\textbf{Gelation in dense samples.} \textbf{a} Typical time evolution of the largest cluster size and of the mean coordination number.
-Insets: Confocal images (2D) at percolation and at final stage.
-\textbf{b-d} Typical arm-breaking event, from relaxed, to stretched, to rupture.
-Particles are drawn to scale and colors indicate potential energies from blue (low) to red (high).
-The smooth surface is a Gaussian coarse-graining of the network pattern.
-%\textbf{e-f} Typical loop compaction event.
-\textbf{b-f} are top views, thus there is no direct role of sedimentation.
-	}
-	\label{fig:dense}
-\end{figure}
-
-\clearpage
-\begin{figure}
-	\begin{center}
-	%\includegraphics{generate-figure3.pdf}
-	\end{center}
-	\caption{\textbf{Percolation vs compaction} for the three systems studied here: fluid (not percolating), dilute gel and dense gel.}
-	\label{fig:general}
-\end{figure}
 \end{document}

### 2015-07-23 gel_cond/trunk/paper.tex
replace fig:cell_vs_cap by cell_vs_cap2 and fig:wholeprocess with fig:phasediagram Finishish there description in the text.

@@
 
-\subsection*{Observation of the initial stage}
+\subsection*{System design}
 
-We use a novel experimental set-up that allows the observation of the entire process of gelation at a single particle level (see Methods).
-In a suspension of sticky colloids with long range repulsion, we suddenly turn off the repulsion.
-The short range attraction become dominant, eventually leading to the formation of a gel.
-The whole process takes place on the microscope stage and can thus be observed dynamically in three dimensions from the very beginning.
+\begin{figure*}
+	\includegraphics{figs/cell_vs_cap2.pdf}
+	\caption{\textbf{Reservoir cell.} \textbf{a} Sketch of our experimental setup.
+The observation cell contains initially colloids, polymer and no salt.
+\textbf{b} Confocal slice of a gel formed \textit{in situ} by our method ($\phi=25.5~\%$, $c_p=\SI{1.4}{\gram\per\litre}$), \SI{1}{\hour} after gelation.
+\textbf{c} Idem for a gel at the same state point formed \textit{ex situ} and immediately pumped into a capillary.
+\textbf{d} Gelation observed by our method.
+Experimental coordinates are reconstructed and coloured by the number of particles in clusters in a typical sample close to the cluster-gel line ($\phi=7.5~\%$, $c_p=\SI{1}{\gram\per\litre}$).
+Origin of time is the last frame before melting of Wigner crystal.
+	%Phase diagram obtained in reservoir cell.
+Spinodal line is obtained from free volume theory.
+State points analysed in the text are circled.
+The state point of \textbf{b-c} is highlighted by a square.
+	}
+	\label{fig:cell_vs_cap}
+\end{figure*}
 
-Our protocol is not equivalent to a redispersion of an existing gel at the same state point either by shaking or shear melting like in  e.g.~\cite{lu2008gelation,Teece2011,Bartlett2012}.
-It is closer to a quench, however we expect differences compared to a quench simulated via molecular or Brownian dynamics, because of the presence of a solvent mediating hydrodynamic interactions~\cite{Furukawa2010}.
+We designed an experimental set-up that allows the observation of the entire process of gelation at a single particle level.
+For that, we use a colloidal system that is charge stabilised at long range, has a short range depletion attraction, and is sterically stabilised causing nearly hard sphere repulsion at contact.
+We use sterically stabilised particles of diameter $\sigma=\SI{3}{\micro\metre}$ in a refractive index matching and density matching mixture of organic solvents.
+In weakly polar solvent, here dielectric constant $\epsilon_r = 5\sim6$, Debye screening length is about $\kappa^{-1}=\SI{10}{\micro\metre}$, enough to keep apart even the large colloids suitable for particle-level confocal microscopy~\cite{Royall2003}.
+The short ranged, $\sigma/10$, depletion attraction caused by non-adsorbing polymers is masked by the electrostatic repulsion.
+
+We enclose the suspension in a thin microscopy cell sketched in Figure~\ref{fig:cell_vs_cap}a.
+The bottom wall of the cell is an osmotic membrane providing contact with a long channel full of the same solvent mixture.
+We introduce solid salt at the other end of the channel that we seal immediately.
+Salt dissolution and subsequent migration of the ions along the channel and through the membrane induce screening of the electrostatic repulsion, revealing the depletion potential well.
+The time needed for the ions to diffuse from the membrane across the cell thickness is of the same order of magnitude as the Brownian time of the particles $\tau_B=\SI{10}{\second}$.
+This method causes uniform gelation without any solvent flow and allows \textit{in situ} confocal microscopy observation throughout the process.
+
+In Figure~\ref{fig:cell_vs_cap}b and c we show the final structures for two gels prepared at the same state point, one by our protocol, the other by introducing in a capillary an existing gel and thus shear melting it.
+The later is coarser, highlighting that shaking or shear melting protocols~\cite{lu2008gelation,Teece2011,Bartlett2012} are not equivalent to a quench.
+However even in our case we expect differences compared to a quench simulated via molecular or Brownian dynamics, because of the presence of a solvent mediating hydrodynamic interactions~\cite{Furukawa2010}.
 Thus our protocol might be very close to application relevant processes where the sudden addition of a component (e.g.
@@
 
-Figure~\ref{fig:methods}c-h shows a computer reconstruction from experimental coordinates of a typical gelation experiment.
-We are able to follow the state of the system from (Fig.~\ref{fig:methods}c) a Wigner crystal where the particles are far apart due to repulsion to (Fig.~\ref{fig:methods}h) a fully percolated network.
-Using this protocol, we explored the phase diagram (Fig.~\ref{fig:methods}b) and found three possible behaviours: permanent gelation as above, transient gelation and cluster formation.
-Transient gelation is characterised by the formation of a percolating network that melts into separate clusters over a few tens of Brownian times (the time needed for an isolated particle to diffuse over its own radius, here about $\SI{10}{second}$).
+In Figure~\ref{fig:cell_vs_cap}d shows a computer reconstruction from experimental coordinates of a typical gelation experiment close to the cluster-gel boundary.
+Immediately before ions enter the cell ($t=0$), the suspension is in a Wigner crystal state where the particles are far apart due to long range repulsion.
+As soon as the charges are screened, the particles begin to aggregate and form clusters that progressively connect to each other while coarsening to finally percolate through the field of view at $t=\SI{35}{\minute}$.
 
-We observe in Fig.~\ref{fig:methods}b that the spinodal line predicted by the generalized free volume theory~\cite{Fleer2008} corresponds roughly to the boundary between permanent and transient gelation.
-Furthermore, it means that in our system gelation can happen transiently without an underlying spinodal decomposition dynamics, somewhat in contradiction to~\cite{lu2008gelation}.
+\subsection*{Observation of the initial stage}
+
+\begin{figure}
+\includegraphics{figs/phasediag.pdf}
+\caption{\textbf{Different regimes of gelation.} \textbf{a} Phase diagram.
+Experimental points are categorised based on the final state obtained in reservoir cell.
+The spinodal line is obtained from free volume theory.
+State points analysed in the text are circled.
+The state point of Figure~\ref{fig:cell_vs_cap}b-c is highlighted by a square.
+\textbf{b} Comparison of system evolution in terms of largest cluster extent and of mean coordination number.
+By increasing density: $\phi=4.2,\,8,\,16,\,27~\%$, $c_p=1,\,1.5,\,1.2,\,\SI{1}{\gram\per\litre}$ for \textcolor{red!40!yellow}{$\blacklozenge$}, \textcolor{red!80!yellow}{$\circ$}, \textcolor{red!80!black}{\tiny$\blacksquare$} and \textcolor{red!40!black}{$\bullet$} respectively.
+\textbf{c} Growth of the characteristic wave number for the same samples.}
+\label{fig:phasediag}
+\end{figure}
+
+In Figure~\ref{fig:phasediag}a, we divide the phase diagram in three regions based on the final state obtained by our protocol: at low polymer concentration ($c_p<\SI{0.2}{\gram\per\litre}$) sample fully relax to a fluid state; at very low colloid volume fraction ($\phi<0.05$) and high polymer concentration the particles condense into long-lived well separated clusters as observed in~\cite{Lu2006}; in the rest of the explored phase space we observe a long-lived space spanning network.
+We rationalise these observations by superimposing the spinodal line obtained by generalised free volume theory~\cite{Fleer2008}.
+
+XXX discuss differences between theory and experiment.XXX
+
+With our technique we are not limited to observation of the final state.
+We found that the path leading to the final state is not universal and depends on the colloid volume fraction even within the gel region.
+In Figure~\ref{fig:phasediag}b, we represent this path in the $(l_\text{max}/L, \bar{N}_C)$ plane.
+Here $\bar{N}_C$ is the mean number of neighbours, or coordination number quantifying the compacity of the structure.
+$l_\text{max}$ is the spatial extent of the largest cluster that we normalize by the size of the field of view $L$ to obtain a measure of the distance to percolation of the system.
+$l_\text{max}/L\approx 1$ indicates percolation.
+At high densities, percolation takes place first, within the first few $\tau_B$ after charge screening and then coarsening proceed.
+At low densities, percolation never takes place and we observe the compaction of individual clusters.
+In between, we observe the process detailed in Figure~\ref{fig:cell_vs_cap}d: formation of low-compacity clusters that then slowly connect together to build the percolating network.
+This process can take hundreds of $\tau_B$ and is competing with cluster compaction, as indicated by the oblique trajectory in Figure~\ref{fig:phasediag}b.
+
+The initial similarity between the trajectories of dilute gels and cluster phase is striking, as if their dynamics were ruled by the same phenomenon.
+To confront this hypothesis, we compute the time dependent static structure factor $S(q,t)$.
+For all gel and cluster samples we observe the appearance of a low $q$ peak in $S(q)$, see Supplementary Figure XXX, which is characteristic of spinodal decomposition in a system of a conserved order parameter.
+To track the position of this peak, we compute the characteristic wave number $\langle q \rangle$ and show its temporal evolution in Figure~\ref{fig:phasediag}c.
+The curves for all samples follow a master curve coherent with spinodal decomposition kinetics: at short times $\langle q \rangle(t)$ shows a plateau indicating that the low $q$ peak builds up at constant wave number whereas, whereas at intermediate times we observe coarsening with $\langle q \rangle \sim t^{-1/3}$.
+Finally at longer times each sample deviates from the master curve to form a plateau indicating arrest.
+The more dilute samples arrest sooner.
+
+Our observations indicate that both cluster and gel phases are due to an arrested spinodal decomposition: network-type spinodal for the gel, and droplet-type spinodal for the clusters where the initial state is too far from equicomposition to allow a bicontinuous structure.
 

### 2015-07-24 gel_cond/trunk/paper.tex
insert fig:hydro

@@
 Our observations indicate that both cluster and gel phases are due to an arrested spinodal decomposition: network-type spinodal for the gel, and droplet-type spinodal for the clusters where the initial state is too far from equicomposition to allow a bicontinuous structure.
+
+\subsection*{Role of hydrodynamics}
+
+\begin{figure}
+	\includegraphics{figs/hydro.pdf}
+	\caption{\textbf{Hydrodynamics} \textbf{a} Evolution of triplet radii of gyration in a non percolating sample ($\phi=4~\%$, $c_p=\SI{1}{\gram\per\litre}$).
+The characteristic time to reach the stable compact cluster is much longer than the Brownian time.
+\textbf{b} Evolution of the aspect ratios of clusters of 4 particles and more in the same sample (dashed lines) and in a percolating sample ($\phi=8~\%$, $c_p=\SI{1.5}{\gram\per\litre}$, continuous lines) \textbf{c} Bond angle distribution relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue) obtained in the percolating sample.
+Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles.
+Insets sketch both cases, with present bonds drawn thick and future bonds drawn dotted.}
+	\label{fig:hydro}
+\end{figure}
+
+In Figure~\ref{fig:hydro}a, we follow the compaction of clusters made of only three particles in a non percolating sample.
 

### 2015-08-10 gel_cond/trunk/paper.tex
Fix Debye lengths with and without salt

@@
 
-In the absence of salt, the Debye length is expected to reach \SI{100}{\nano\metre} and the (weakly) charged colloids experience a long range electrostatic repulsion.
+In the absence of salt, the Debye length is expected to reach several \si{\micro\metre} and the (weakly) charged colloids experience a long range electrostatic repulsion.
 We confirm that colloids never come close enough to feel the short-ranged attraction.
-Screening by tetrabutylammonium bromide (Fluka) at saturated concentration brings down the Debye length to about \SI{13}{\nano\metre}, practically discarding the repulsion.
+Screening by tetrabutylammonium bromide (Fluka) at saturated concentration brings down the Debye length to about \SI{100}{\nano\metre}, practically discarding the repulsion.
 

### 2015-09-09 gel_cond/trunk/paper.tex
rephrase the description of the c+p mixture

@@
 We designed an experimental set-up that allows the observation of the entire process of gelation at a single particle level.
-For that, we use a colloidal system that is charge stabilised at long range, has a short range depletion attraction, and is sterically stabilised causing nearly hard sphere repulsion at contact.
-We use sterically stabilised particles of diameter $\sigma=\SI{3}{\micro\metre}$ in a refractive index matching and density matching mixture of organic solvents.
-In weakly polar solvent, here dielectric constant $\epsilon_r = 5\sim6$, Debye screening length is about $\kappa^{-1}=\SI{10}{\micro\metre}$, enough to keep apart even the large colloids suitable for particle-level confocal microscopy~\cite{Royall2003}.
-The short ranged, $\sigma/10$, depletion attraction caused by non-adsorbing polymers is masked by the electrostatic repulsion.
+For that, we use a colloidal system that is charge stabilised at long range, has a short range depletion attraction, and is also sterically stabilised causing nearly hard sphere repulsion at contact.
+We disperse colloidal particles and non-adsorbing polymers in a  mixture of organic solvents that matches both the refractive index and the density of the particles.
+In such weakly polar solvent, here dielectric constant $\epsilon_r = 5\sim6$, Debye screening length is about $\kappa^{-1}=\SI{10}{\micro\metre}$, enough to keep apart even the large colloids suitable for particle-level confocal microscopy~\cite{Royall2003}, here diameter $\sigma=\SI{3}{\micro\metre}$.
+The short ranged, $\sigma/10$, depletion attraction caused by the polymers is masked by the electrostatic repulsion.
 

### 2015-09-09 phasediag.py
Fix phase diagram by using consistent values of q and qR. Now gasliquid_*.phd volume fractions are in %

@@ -7,7 +7,7 @@ q = qR2q(qR)
 
 fig = figure('experimental phase diagram')
 clf()
-for phase, color in [('gel', 'r'), ('fluid', 'b'), ('transient', 'g')]:
+for phase, color in [('gel', 'r'), ('fluid', 'b'), ('transient', 'g'), ('clusters', 'y')]:
     phi, cp = np.loadtxt('phase_diag_%s.csv'%phase, unpack=True, skiprows=1, usecols=[1,2])
     sample = np.loadtxt('phase_diag_%s.csv'%phase, usecols=[0], skiprows=1, dtype='str')
     scatter(phi, cp, c=color, label=phase)
@@ -52,7 +52,7 @@ def xp2th(cp, phi, q=0.1):
     """Converts experimental polymer concentration in osmotic pressure"""
     return y2piv(cp/alpha(vf2f(phi), qR2q(q)), q)
 
-for phase, color in [('gel', 'r'), ('fluid', 'b'), ('transient', 'g')]:
+for phase, color in [('gel', 'r'), ('fluid', 'b'), ('transient', 'g'), ('clusters', 'y')]:
     phi, cp = np.loadtxt('phase_diag_%s.csv'%phase, unpack=True, skiprows=1, usecols=[1,2])
     sample = np.loadtxt('phase_diag_%s.csv'%phase, usecols=[0], skiprows=1, dtype='str')
     scatter(phi, xp2th(cp, phi*1e-2, 0.1), c=color, label=phase)

### 2015-09-09 paper.tex
Spinodal by free volume theory is a poor predictor of the gel boundary

@@
 
-\subsection*{Observation of the initial stage}
+\subsection*{System design}
 
 \begin{figure*}
-	\includegraphics{figs/cell_vs_cap.pdf}
-	\caption{\textbf{Reservoir cell} \textbf{a} Sketch of our experimental setup.
+	\includegraphics{figs/cell_vs_cap2.pdf}
+	\caption{\textbf{Reservoir cell.} \textbf{a} Sketch of our experimental setup.
 The observation cell contains initially colloids, polymer and no salt.
-\textbf{b} Confocal picture of a gel formed in situ ($\phi=25.5~\%$, $c_p=\SI{1.4}{\gram\per\litre}$), \SI{1}{\hour} after gelation.
-\textbf{c} Confocal picture of a gel at the same state point formed ex situ, \SI{1}{\hour} after shear melting.
-\textbf{d} Phase diagram obtained in reservoir cell.
+\textbf{b} Confocal slice of a gel formed \textit{in situ} by our method ($\phi=25.5~\%$, $c_p=\SI{1.4}{\gram\per\litre}$), \SI{1}{\hour} after gelation.
+\textbf{c} Idem for a gel at the same state point formed \textit{ex situ} and immediately pumped into a capillary.
+\textbf{d} Gelation observed by our method.
+Experimental coordinates are reconstructed and coloured by the number of particles in clusters in a typical sample close to the cluster-gel line ($\phi=7.5~\%$, $c_p=\SI{1}{\gram\per\litre}$).
+Origin of time is the last frame before melting of Wigner crystal.
+	%Phase diagram obtained in reservoir cell.
 Spinodal line is obtained from free volume theory.
 State points analysed in the text are circled.
-The state point of \textbf{b-c} is highlighted by a square.}
+The state point of \textbf{b-c} is highlighted by a square.
+	}
 	\label{fig:cell_vs_cap}
@@
 
-In Figure~\ref{fig:cell_vs_cap}b and c we show the final structures for two gels prepared at the same state point, one by our protocol, the other by introducing in a capillary an existing gel and thus shear melting it.
+In Figure~\ref{fig:cell_vs_cap}b and c we show confocal microscopy images of the final structures for two gels prepared at the same state point, one by our protocol, the other by introducing in a capillary an existing gel and thus shear melting it.
 The later is coarser, highlighting that shaking or shear melting protocols~\cite{lu2008gelation,Teece2011,Bartlett2012} are not equivalent to a quench.
@@
 
-In Figure~\ref{fig:cell_vs_cap}d we show the phase diagram obtained by our protocol.
-We observe three possible behaviours: at low polymer concentration ($c_p<\SI{0.2}{\gram\per\litre}$) sample fully relax to a fluid state; at very low colloid volume fraction ($\phi<0.05$) and high polymer concentration the particles condense into long-lived well separated clusters as observed in~\cite{Lu2006}; in the rest of the explored phase space we observe a long-lived network.
-We rationalise these observations by superimposing the spinodal line obtained by generalised free volume theory~\cite{Fleer2008}.
-
-XXX discuss differences between theory and experiment. What is cluster phase? XXX
-
-\begin{figure}
-\includegraphics{figs/wholeprocess.pdf}
-\caption{\textbf{Gelation process} \textbf{a} Reconstruction of experimental coordinates coloured by the number of particles in clusters in a typical sample close to the cluster-gel line ($\phi=7.5~\%$, $c_p=\SI{1}{\gram\per\litre}$).
-Origin of time is the last frame before melting of Wigner crystal.
-\textbf{b} Comparision of system evolution in terms of largest cluster extent and of mean coordination number.
-By increasing density: $\phi=4.2,\,8,\,16,\,27~\%$, $c_p=1,\,1.5,\,1.2,\,\SI{1}{\gram\per\litre}$ for \textcolor{red!40!yellow}{$*$}, \textcolor{red!80!yellow}{$\circ$}, \textcolor{red!80!black}{\tiny$\blacksquare$} and \textcolor{red!40!black}{$\bullet$} respectively.\textbf{c} Growth of the characteristic wave number for the same samples.}
-\label{fig:wholeprocess}
-\end{figure}
-
-Figure~\ref{fig:wholeprocess}a shows a computer reconstruction from experimental coordinates of a typical gelation experiment close to the cluster-gel boundary.
+In Figure~\ref{fig:cell_vs_cap}d shows a computer reconstruction from experimental coordinates of a typical gelation experiment at a relatively low volume fraction ($\phi=7.5\%$).
 Immediately before ions enter the cell ($t=0$), the suspension is in a Wigner crystal state where the particles are far apart due to long range repulsion.
@@
 
-However, this sequence of events is not universal, as shown in Figure~\ref{fig:wholeprocess}b.
-At higher densities, percolation happen first, within the first few $\tau_B$ after charge screening and then coarsening proceed with an increasing average coordination number $\bar{N}_C$.
-At lower densities, percolation never takes place and we observe the compaction of individual clusters.
+\subsection*{Observation of the initial stage}
 
-Universality is recovered when investigating the dynamics of the coarsening process.
-We compute the characteristic wave number $\langle q \rangle$ of the structure factor $S(q)$ and show its temporal evolution in Figure~\ref{fig:wholeprocess}c.
-We confirm the appearance of a low $q$ peak in $S(q)$, see Supplementary Figure XXX, which is characteristic of spinodal decomposition in a system of a conserved order parameter.
-At short times $\langle q \rangle$ shows a plateau indicating that the low $q$ peak builds up at constant wave number.
-At intermediate times, $\langle q \rangle$ scales as $t^{-1/3}$, again coherent with spinodal decomposition kinetics.
-Finally at longer times each sample deviates from the universal slope to form a plateau indicating arrest.
+\begin{figure}
+\includegraphics{figs/phasediag.pdf}
+\caption{\textbf{Different regimes of gelation.} \textbf{a} Phase diagram.
+Experimental points are categorised based on the final state obtained in reservoir cell.
+The spinodal line is obtained from free volume theory.
+State points analysed in the text are circled.
+The state point of Figure~\ref{fig:cell_vs_cap}b-c is highlighted by a square.
+\textbf{b} Comparison of system evolution in terms of largest cluster extent and of mean coordination number.
+By increasing density: $\phi=4.2,\,8,\,16,\,27~\%$, $c_p=1,\,1.5,\,1.2,\,\SI{1}{\gram\per\litre}$ for \textcolor{red!40!yellow}{$\blacklozenge$}, \textcolor{red!80!yellow}{$\circ$}, \textcolor{red!80!black}{\tiny$\blacksquare$} and \textcolor{red!40!black}{$\bullet$} respectively.
+\textbf{c} Growth of the characteristic wave number for the same samples.}
+\label{fig:phasediag}
+\end{figure}
+
+In Figure~\ref{fig:phasediag}a, we divide the phase diagram in three regions based on the final state obtained by our protocol: at low polymer concentration ($c_p<\SI{0.2}{\gram\per\litre}$) sample fully relax to a fluid state; at very low colloid volume fraction ($\phi<0.05$) and high polymer concentration the particles condense into long-lived well separated clusters as observed in~\cite{Lu2006}; in the rest of the explored phase space we observe a long-lived space spanning network.
+As observed by others~\cite{Shah2003,Bergenholtz2003,lu2008gelation}, the theoretical spinodal line obtained by generalised free volume theory~\cite{Fleer2008} is a poor predictor of the gel boundary, especially at low volume fraction.
+
+With our technique we are not limited to observation of the final state.
+We found that the path leading to the final state is not universal and depends on the colloid volume fraction even within the gel region.
+In Figure~\ref{fig:phasediag}b, we represent this path in the $(l_\text{max}/L, \bar{N}_C)$ plane.
+Here $\bar{N}_C$ is the mean number of neighbours, or coordination number quantifying the compacity of the structure.
+$l_\text{max}$ is the spatial extent of the largest cluster that we normalize by the size of the field of view $L$ to obtain a measure of the distance to percolation of the system.
+$l_\text{max}/L\approx 1$ indicates percolation.
+At high densities, percolation takes place first, within the first few $\tau_B$ after charge screening and then coarsening proceed.
+At low densities, percolation never takes place and we observe the compaction of individual clusters.
+In between, we observe the process detailed in Figure~\ref{fig:cell_vs_cap}d: formation of low-compacity clusters that then slowly connect together to build the percolating network.
+This process can take hundreds of $\tau_B$ and is competing with cluster compaction, as indicated by the oblique trajectory in Figure~\ref{fig:phasediag}b.
+
+The initial similarity between the trajectories of dilute gels and cluster phase is striking, as if their dynamics were ruled by the same phenomenon.
+To confront this hypothesis, we compute the time dependent static structure factor $S(q,t)$.
+For all gel and cluster samples we observe the appearance of a low $q$ peak in $S(q)$, see Supplementary Figure XXX, which is characteristic of spinodal decomposition in a system of a conserved order parameter.
+To track the position of this peak, we compute the characteristic wave number $\langle q \rangle$ and show its temporal evolution in Figure~\ref{fig:phasediag}c.
+The curves for all samples follow a master curve coherent with spinodal decomposition kinetics: at short times $\langle q \rangle(t)$ shows a plateau indicating that the low $q$ peak builds up at constant wave number whereas, whereas at intermediate times we observe coarsening with $\langle q \rangle \sim t^{-1/3}$.
+Finally at longer times each sample deviates from the master curve to form a plateau indicating arrest.
 The more dilute samples arrest sooner.
@@
 
-Using this protocol, we explored the phase diagram (Fig.~\ref{fig:methods}b) and found three possible behaviours: permanent gelation as above, transient gelation and cluster formation.
-Transient gelation is characterised by the formation of a percolating network that melts into separate clusters over a few tens of Brownian times (the time needed for an isolated particle to diffuse over its own radius, here about $\SI{10}{second}$).
+\subsection*{Role of hydrodynamics}
 
-We observe in Fig.~\ref{fig:methods}b that the spinodal line predicted by the generalized free volume theory~\cite{Fleer2008} corresponds roughly to the boundary between permanent and transient gelation.
-Furthermore, it means that in our system gelation can happen transiently without an underlying spinodal decomposition dynamics, somewhat in contradiction to~\cite{lu2008gelation}.
+\begin{figure}
+	\includegraphics{figs/hydro.pdf}
+	\caption{\textbf{Hydrodynamics} \textbf{a} Evolution of triplet radii of gyration in a non percolating sample ($\phi=4~\%$, $c_p=\SI{1}{\gram\per\litre}$).
+The characteristic time to reach the stable compact cluster is much longer than the Brownian time.
+\textbf{b} Evolution of the aspect ratios of clusters of 4 particles and more in the same sample (dashed lines) and in a percolating sample ($\phi=8~\%$, $c_p=\SI{1.5}{\gram\per\litre}$, continuous lines) \textbf{c} Bond angle distribution relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue) obtained in the percolating sample.
+Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles.
+Insets sketch both cases, with present bonds drawn thick and future bonds drawn dotted.}
+	\label{fig:hydro}
+\end{figure}
+
+In Figure~\ref{fig:hydro}a, we follow the compaction of clusters made of only three particles in a non percolating sample.
 

### 2015-09-11 paper.tex
rephrase the description of gelation path

@@
 
-With our technique we are not limited to observation of the final state.
-We found that the path leading to the final state is not universal and depends on the colloid volume fraction even within the gel region.
-In Figure~\ref{fig:phasediag}b, we represent this path in the $(l_\text{max}/L, \bar{N}_C)$ plane.
-Here $\bar{N}_C$ is the mean number of neighbours, or coordination number quantifying the compacity of the structure.
-$l_\text{max}$ is the spatial extent of the largest cluster that we normalize by the size of the field of view $L$ to obtain a measure of the distance to percolation of the system.
-$l_\text{max}/L\approx 1$ indicates percolation.
+With our technique we can observe the path leading to the final state.
+To characterise this path, we compute the instantaneous mean number of neighbours $\bar{N}_C$, or coordination number that quantifies the compacity of the structure.
+We also compute the the spatial extent of the largest cluster $l_\text{max}$ that we normalize by the size of the field of view $L$ to obtain a measure of the distance to percolation of the system.
+Figure~\ref{fig:phasediag}b shows system trajectory in the $(l_\text{max}/L, \bar{N}_C)$ plane for various colloidal volume fractions.
 At high densities, percolation takes place first, within the first few $\tau_B$ after charge screening and then coarsening proceed.
@@
 This process can take hundreds of $\tau_B$ and is competing with cluster compaction, as indicated by the oblique trajectory in Figure~\ref{fig:phasediag}b.
+The path to gelation is thus not universal and depends on the colloid volume fraction even within the gel region.
 
@@
 To track the position of this peak, we compute the characteristic wave number $\langle q \rangle$ and show its temporal evolution in Figure~\ref{fig:phasediag}c.
-The curves for all samples follow a master curve coherent with spinodal decomposition kinetics: at short times $\langle q \rangle(t)$ shows a plateau indicating that the low $q$ peak builds up at constant wave number whereas, whereas at intermediate times we observe coarsening with $\langle q \rangle \sim t^{-1/3}$.
+The curves for all samples follow a master curve coherent with spinodal decomposition kinetics: at short times $\langle q \rangle(t)$ shows a plateau indicating that the low $q$ peak builds up at constant wave number, whereas at intermediate times we observe coarsening with $\langle q \rangle \sim t^{-1/3}$.
 Finally at longer times each sample deviates from the master curve to form a plateau indicating arrest.

### 2015-09-16 gel_cond/trunk/paper.tex
fig:hydro Probability of staying elongated for a triplet as panel a Histogram of Rg as inset

@@
 
-In Figure~\ref{fig:cell_vs_cap}d shows a computer reconstruction from experimental coordinates of a typical gelation experiment close to the cluster-gel boundary.
+In Figure~\ref{fig:cell_vs_cap}d shows a computer reconstruction from experimental coordinates of a typical gelation experiment at a relatively low volume fraction ($\phi=7.5\%$).
 Immediately before ions enter the cell ($t=0$), the suspension is in a Wigner crystal state where the particles are far apart due to long range repulsion.
@@
 In Figure~\ref{fig:phasediag}a, we divide the phase diagram in three regions based on the final state obtained by our protocol: at low polymer concentration ($c_p<\SI{0.2}{\gram\per\litre}$) sample fully relax to a fluid state; at very low colloid volume fraction ($\phi<0.05$) and high polymer concentration the particles condense into long-lived well separated clusters as observed in~\cite{Lu2006}; in the rest of the explored phase space we observe a long-lived space spanning network.
-We rationalise these observations by superimposing the spinodal line obtained by generalised free volume theory~\cite{Fleer2008}.
+As observed by others~\cite{Shah2003,Bergenholtz2003,lu2008gelation}, the theoretical spinodal line obtained by generalised free volume theory~\cite{Fleer2008} is a poor predictor of the gel boundary, especially at low volume fraction.
 
-XXX discuss differences between theory and experiment.XXX
-
-With our technique we are not limited to observation of the final state.
-We found that the path leading to the final state is not universal and depends on the colloid volume fraction even within the gel region.
-In Figure~\ref{fig:phasediag}b, we represent this path in the $(l_\text{max}/L, \bar{N}_C)$ plane.
-Here $\bar{N}_C$ is the mean number of neighbours, or coordination number quantifying the compacity of the structure.
-$l_\text{max}$ is the spatial extent of the largest cluster that we normalize by the size of the field of view $L$ to obtain a measure of the distance to percolation of the system.
-$l_\text{max}/L\approx 1$ indicates percolation.
+With our technique we can observe the path leading to the final state.
+To characterise this path, we compute the instantaneous mean number of neighbours $\bar{N}_C$, or coordination number that quantifies the compacity of the structure.
+We also compute the the spatial extent of the largest cluster $l_\text{max}$ that we normalize by the size of the field of view $L$ to obtain a measure of the distance to percolation of the system.
+Figure~\ref{fig:phasediag}b shows system trajectory in the $(l_\text{max}/L, \bar{N}_C)$ plane for various colloidal volume fractions.
 At high densities, percolation takes place first, within the first few $\tau_B$ after charge screening and then coarsening proceed.
@@
 	\includegraphics{figs/hydro.pdf}
-	\caption{\textbf{Hydrodynamics} \textbf{a} Evolution of triplet radii of gyration in a non percolating sample ($\phi=4~\%$, $c_p=\SI{1}{\gram\per\litre}$).
-The characteristic time to reach the stable compact cluster is much longer than the Brownian time.
+	\caption{\textbf{Hydrodynamics} \textbf{a} Probability of compaction of an elongated triplet in a non percolating sample ($\phi=4~\%$, $c_p=\SI{1}{\gram\per\litre}$).
+The continuous line is the best exponential fit of characteristic time $27\tau_B$.
+Inset: probability distribution of radii of gyration of triplets.
 \textbf{b} Evolution of the aspect ratios of clusters of 4 particles and more in the same sample (dashed lines) and in a percolating sample ($\phi=8~\%$, $c_p=\SI{1.5}{\gram\per\litre}$, continuous lines) \textbf{c} Bond angle distribution relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue) obtained in the percolating sample.

### 2015-09-16 gel_cond/trunk/phasediag.py
in xp2th uses qR instead of q for clarity

@@ -48,14 +48,14 @@ savefig('phasediag.pdf')
 fig = figure('theoretical phase diagram')
 clf()
 
-def xp2th(cp, phi, q=0.1):
+def xp2th(cp, phi, qR=0.1):
     """Converts experimental polymer concentration in osmotic pressure"""
-    return y2piv(cp/alpha(vf2f(phi), qR2q(q)), q)
+    return y2piv(cp/alpha(vf2f(phi), qR2q(qR)), qR)
 
 for phase, color in [('gel', 'r'), ('fluid', 'b'), ('transient', 'g'), ('clusters', 'y')]:
     phi, cp = np.loadtxt('phase_diag_%s.csv'%phase, unpack=True, skiprows=1, usecols=[1,2])
     sample = np.loadtxt('phase_diag_%s.csv'%phase, usecols=[0], skiprows=1, dtype='str')
-    scatter(phi, xp2th(cp, phi*1e-2, 0.1), c=color, label=phase)
+    scatter(phi, xp2th(cp, phi*1e-2, qR), c=color, label=phase)
     for s, p, c in zip(np.atleast_1d(sample), np.atleast_1d(phi), np.atleast_1d(xp2th(cp, phi*1e-2, 0.1))):
         gca().annotate(s, (p,c))
 

### 2015-09-16 paper.tex
Describe fig:hydro a and b Define P_\text{el}

@@
 
+Two questions remain, corresponding respectively to the dilute or dense routes to gelation: (i) How can individual clusters percolate a long time after their formation?
+(ii) How does a percolated network evolve toward more compact states?
+We will show that the answers come from mechanical effects: respectively hydrodynamics and internal stresses.
+
 \subsection*{Role of hydrodynamics}
@@
 	\includegraphics{figs/hydro.pdf}
-	\caption{\textbf{Hydrodynamics} \textbf{a} Evolution of triplet radii of gyration in a non percolating sample ($\phi=4~\%$, $c_p=\SI{1}{\gram\per\litre}$).
-The characteristic time to reach the stable compact cluster is much longer than the Brownian time.
+	\caption{\textbf{Hydrodynamics} \textbf{a} Probability of staying elongated for a triplet in a non percolating sample ($\phi=4~\%$, $c_p=\SI{1}{\gram\per\litre}$).
+The continuous line is the best exponential fit of characteristic time $27\tau_B$.
+Inset: probability distribution of radii of gyration of triplets.
 \textbf{b} Evolution of the aspect ratios of clusters of 4 particles and more in the same sample (dashed lines) and in a percolating sample ($\phi=8~\%$, $c_p=\SI{1.5}{\gram\per\litre}$, continuous lines) \textbf{c} Bond angle distribution relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue) obtained in the percolating sample.
@@
 In Figure~\ref{fig:hydro}a, we follow the compaction of clusters made of only three particles in a non percolating sample.
+The probability distribution of the radius of gyration $R_g$ of these triplets shows two peaks on both sides of $R_g^*=0.8\sigma$.
+For $R_g<R_g^*$ the cluster is compact, with a structure close to an equilateral triangle.
+For $R_g>R_g^*$ the three particles are aligned and the cluster is elongated.
+We found that just after the quench most triplets are elongated and then either connect to other clusters or relax to the more stable compact state.
+To follow this relaxation, we define the probability to stay elongated as
+\begin{equation}
+P_\text{el}(\Delta t) = \langle P(\delta_i(t+\Delta t)|\delta_i(t))\rangle_{t,i}
+\end{equation}
+where $\delta_i(t)$ is the probability for the triplet $i$ to be elongated at time $t$.
+The decay of $P_\text{el}(\Delta t)$ has a characteristic time of $27\tau_B$, much longer than the Brownian time.
+
+The shape of clusters of more than 3 particles cannot be followed in the same way.
+We compute the principal moments of gyrations $\lambda_j$ with $\lambda_1\geq\lambda_2\geq\lambda_3$.
+Low values of the aspect ratios $\lambda_2/\lambda_1$ and $\lambda_3/\lambda_1$ indicate that the cluster is flat or even linear.
+In Figure~\ref{fig:hydro}b, we show the evolution of the average value of these aspect ratios either for a non-percolating sample or before percolation for a percolating one.
+In both cases, we observe that the clusters are originally not compact and become more isotropic over tens of $\tau_B$.
+
+Figure~\ref{fig:hydro}c
+
+These observations can be rationalised by the invocation of hydrodynamic effects.
+Indeed in a solvent, particles cannot converge freely to form compact structures~\cite{Furukawa2010}.
+The compaction is delayed by the incompressibility of the solvent.
+Furthermore, clusters influenced by hydrodynamic interactions tend to be more elongated, less compact.
 

### 2015-09-17 paper.tex
Hydrodynamic hypothesis, fig:hydro c, conclusion of the hydro subsection

@@
 \begin{equation}
-P_\text{el}(\Delta t) = \langle P(\delta_i(t+\Delta t)|\delta_i(t))\rangle_{t,i}
+P_\text{el}(\Delta t) = \left\langle P\left(\delta_i(t+\Delta t)|\delta_i(t)\right)\right\rangle_{t,i}
 \end{equation}
@@
 In both cases, we observe that the clusters are originally not compact and become more isotropic over tens of $\tau_B$.
-
-Figure~\ref{fig:hydro}c
+As visible in Figure~\ref{fig:cell_vs_cap}d, isotropy is recovered by the fusion of many anisotropic clusters into a branched structure.
 
@@
 Furthermore, clusters influenced by hydrodynamic interactions tend to be more elongated, less compact.
+We can test this hypothesis by measuring at which angle particles meet relative to existing neighbours.
+If influenced by hydrodynamics, particles should avoid the direction of existing neighbours and come from more open angles.
+
+In Figure~\ref{fig:hydro}c we show the bond angle distribution from three points of view: (i) existing bonds, (ii) bonds that will form within the next $\tau_B$ (iii) bonds that will form within the next $\tau_B$ involving a isolated particle.
+As expected, existing bonds are preferentially at a \SI{60}{\degree} angle indicating stable packing, with secondary peaks coherent with a mixture of tetrahedral and hexagonal packings.
+Future bonds have more acute angles and almost never \SI{180}{\degree}, since they are mostly due to particles attached to second neighbours, see sketch on Figure~\ref{fig:hydro}c.
+Here hydrodynamics plays no role.
+By contrast, future bonds involving isolated particles form at more obtuse angles, with a clear peak around \SI{180}{\degree}.
+This confirms that hydrodynamics influences particle aggregation and explains why clusters are initially elongated.
+
+Consequently, long-lived elongated clusters have a higher probability to meet via either rotational or translational diffusion than compact spherical clusters.
+In Supplementary Figure~\ref{fig:effectiveVF} we show that indeed at all colloidal volume fraction percolation takes place when the effective volume fraction $\phi_\text{eff} = \sum\frac{4\pi}{3}R_g^3$ of the clusters reaches random close packing.
+Hydrodynamics explains why in a rather dilute regime we can observe immediate formation of elongated clusters and then their slow, diffusion limited aggregation into a percolated structure.
+
+\subsection*{Internal stresses}
 

### 2015-09-17 gel_cond/trunk/paper.tex
describe fig:breaking a, introduce q_2 and L

@@
 	\includegraphics{figs/hydro.pdf}
-	\caption{\textbf{Hydrodynamics} \textbf{a} Probability of compaction of an elongated triplet in a non percolating sample ($\phi=4~\%$, $c_p=\SI{1}{\gram\per\litre}$).
+	\caption{\textbf{Hydrodynamics} \textbf{a} Probability of staying elongated for a triplet in a non percolating sample ($\phi=4~\%$, $c_p=\SI{1}{\gram\per\litre}$).
 The continuous line is the best exponential fit of characteristic time $27\tau_B$.
@@
 In Figure~\ref{fig:hydro}a, we follow the compaction of clusters made of only three particles in a non percolating sample.
+The probability distribution of the radius of gyration $R_g$ of these triplets shows two peaks on both sides of $R_g^*=0.8\sigma$.
+For $R_g<R_g^*$ the cluster is compact, with a structure close to an equilateral triangle.
+For $R_g>R_g^*$ the three particles are aligned and the cluster is elongated.
+We found that just after the quench most triplets are elongated and then either connect to other clusters or relax to the more stable compact state.
+To follow this relaxation, we define the probability to stay elongated as
+\begin{equation}
+P_\text{el}(\Delta t) = \left\langle P\left(\delta_i(t+\Delta t)|\delta_i(t)\right)\right\rangle_{t,i}
+\end{equation}
+where $\delta_i(t)$ is the probability for the triplet $i$ to be elongated at time $t$.
+The decay of $P_\text{el}(\Delta t)$ has a characteristic time of $27\tau_B$, much longer than the Brownian time.
+
+The shape of clusters of more than 3 particles cannot be followed in the same way.
+We compute the principal moments of gyrations $\lambda_j$ with $\lambda_1\geq\lambda_2\geq\lambda_3$.
+Low values of the aspect ratios $\lambda_2/\lambda_1$ and $\lambda_3/\lambda_1$ indicate that the cluster is flat or even linear.
+In Figure~\ref{fig:hydro}b, we show the evolution of the average value of these aspect ratios either for a non-percolating sample or before percolation for a percolating one.
+In both cases, we observe that the clusters are originally not compact and become more isotropic over tens of $\tau_B$.
+As visible in Figure~\ref{fig:cell_vs_cap}d, isotropy is recovered by the fusion of many anisotropic clusters into a branched structure.
+
+These observations can be rationalised by the invocation of hydrodynamic effects.
+Indeed in a solvent, particles cannot converge freely to form compact structures~\cite{Furukawa2010}.
+The compaction is delayed by the incompressibility of the solvent.
+Furthermore, clusters influenced by hydrodynamic interactions tend to be more elongated, less compact.
+We can test this hypothesis by measuring at which angle particles meet relative to existing neighbours.
+If influenced by hydrodynamics, particles should avoid the direction of existing neighbours and come from more open angles.
+
+In Figure~\ref{fig:hydro}c we show the bond angle distribution from three points of view: (i) existing bonds, (ii) bonds that will form within the next $\tau_B$ (iii) bonds that will form within the next $\tau_B$ involving a isolated particle.
+As expected, existing bonds are preferentially at a \SI{60}{\degree} angle indicating stable packing, with secondary peaks coherent with a mixture of tetrahedral and hexagonal packings.
+Future bonds have more acute angles and almost never \SI{180}{\degree}, since they are mostly due to particles attached to second neighbours, see sketch on Figure~\ref{fig:hydro}c.
+Here hydrodynamics plays no role.
+By contrast, future bonds involving isolated particles form at more obtuse angles, with a clear peak around \SI{180}{\degree}.
+This confirms that hydrodynamics influences particle aggregation and explains why clusters are initially elongated.
+
+Consequently, long-lived elongated clusters have a higher probability to meet via either rotational or translational diffusion than compact spherical clusters.
+In Supplementary Figure~\ref{fig:effectiveVF} we show that indeed at all colloidal volume fraction percolation takes place when the effective volume fraction $\phi_\text{eff} = \sum\frac{4\pi}{3}R_g^3$ of the clusters reaches random close packing.
+Hydrodynamics explains why in a rather dilute regime we can observe immediate formation of elongated clusters and then their slow, diffusion limited aggregation into a percolated structure.
+
+\subsection*{Internal stresses}
+
+\begin{figure*}
+\includegraphics{figs/breaking.pdf}
+\caption{\textbf{Mechanical tension drives coarsening} 
+\textbf{a} Reconstruction from experimental coordinates ($\phi=29~\%$, $c_p=\SI{0.7}{\gram\per\litre}$) of coarsening process geometry (top) and topology (bottom).
+Particles are drawn to scale and coloured by $q_2$ from blue (low) to red (high).
+The meshed surface is a Gaussian coarse-graining of the network pattern.
+The red line indicates the shortest on-graph path between the two particles of interest.
+\textbf{b} Number of bond breaking function of the future on-graph distance $L$ (after percolation) for the three percolating state points of figure 2 (same colours and markers).
+%three state points of increasing density: $\phi=8,\,16,\,27~\%$, $c_p=1.5,\,1.2,\,\SI{1}{\gram\per\litre}$ for \textcolor{red!80!yellow}{$\circ$}, \textcolor{red!80!black}{\tiny$\blacksquare$} and \textcolor{red!40!black}{$\bullet$} respectively.
+\textbf{c} Probability for a bond to break during $3\tau_B$ function of bond-centred $q_2$ for all events (blue) and for events with $L>1$ (thick red) in the same sample as \textbf{a}.
+\textbf{d} Evolution of the topologically relevant bond breaking probability ($L>3$) for the same state points  as in b. Vertical lines indicate the respective percolation times.
+}
+\label{fig:breaking}
+\end{figure*}
+
+We now change our focus to percolated samples.
+As we saw in Figure~\ref{fig:phasediag}c, the coarsening in these samples is much slower than what is expected from spinodal decomposition dynamics.
+The phase separation is arrested, but the system is still ageing, a process sometimes leading to delayed sudden collapse of gels~\cite{Teece2011,Bartlett2012}, a catastrophic phenomenon from the industrial point of view.
+Previous studies~\cite{Tanaka2007,Bartlett2012} have shown that the main coarsening mechanism is the rupture of strands in the network, a process that to our knowledge has not been followed experimentally at the particle level.
+
+Figure~\ref{fig:breaking}a shows a strand rupture reconstructed from confocal 3D images, the colours mapping the intensity of internal stresses acting on each particle.
+In practice, the attraction potential well is too narrow relative to the particle localisation errors for us to extract directly the force acting on a particle.
+Therefore, we use the elongation of the particle neighbourhood as a proxy.
+The more the bonds around a particle are oriented along a single axis, the more tension is exerted on the particle.
+This local elongation is quantified using~\cite{steinhardt1983boo} bond orientational order for the 2-fold symmetry $q_2$, see Methods for a precise definition.
+On Figure~\ref{fig:breaking}a we observe the slow build up of tension over the first \SI{30}{\minute}, until the tension is concentrated on a one particle thin strand.
+This strand breaks and the particles involved merge in their respective part of the network than can diffuse away from each other.
+
+To detect strand rupture, we use the topology of the bond network.
+We can consider the gel as a graph with the particles as nodes and the bonds as edges.
+This graph evolves from frame to frame separated by $3\tau_B$.
+In the lower part of Figure~\ref{fig:breaking}a we draw in red the shortest on-graph path between two particles of interest.
+Before the strand rupture, this path is a single bond long.
+After the rupture, the shortest path is much longer.
+In general, when two particles were bonded on the previous frame and are no more bonded on the present frame, we define the post-breaking topological distance $L$ as the new shortest distance on the graph between them, minus 1.
+If the particles still have a common neighbour then $L=1$, because two bonds are needed to go from one to the other.
+$L=2$ when three bonds are needed, etc.
 

### 2015-09-17 gel_cond/trunk/paper.tex
describe fig:breaking b and c

@@
 
+$L$ is a good measure of the significance of a bond breaking event.
+Small values indicate a local rearrangement whereas large values are the signature of important changes in the topology of the network, namely strand rupture.
+Figure~\ref{fig:breaking}b shows the distribution of $L$ for three colloidal volume fractions.
+Excluding the largest values that are dominated by the limited size of the field of view, $L$ seems to follow a power-law distribution of exponent between $-3$ and $-4$.
+However the values at $L=1$ seems in excess.
+Figure~\ref{fig:breaking}c compares the probability distribution of $q_2$ for all bond breaking events versus for evens with $L>1$.
+In both cases bonds about to break have a higher probability of being under tension, but this trend is much clearer when excluding local events.
+Both observations point to spurious detection of bond breaking events due to localisation errors comparable to the short attraction range and rattling of particles.
+For this reason, but also to focus on topologically relevant strand rupture, we discard all events with $L<4$ in the following analysis.
+
 \section{Cluster aggregation} % Subject I: Cluster formation

### 2015-09-17 gel_cond/trunk/paper.tex
Remove old text.

@@
 
-\section{Cluster aggregation} % Subject I: Cluster formation
-% Topic sentence
-Figure~\ref{fig:methods}a shows the phase diagram of all samples.
-First of all, we focus on cluster formation since clusters constitute ``building blocks'' of gels.
-% Results of birth
-Figure~\ref{fig:fluid_dilute} a shows the compaction dynamics of the clusters with three colloids in the early stage.
-The results show that the clusters can hardly accomplish compaction within one Brownian motion time and clusters with four and five colloids show very similar tendency (Supplement).
-% Explanation 1) Local energy minimization.
-If one assumes that each colloid can move independently by Brownian motion and static short-range attractions are induced between colloids, the clusters with three colloids should reach the compact states within one Brownian motion time.
-This explanation contradicts to our results.
-% Addressing our question
-In other words, some interactions stabilize linear structures, competing with the principle of energy minimization.
-% Explanation 2) Electrostatic repulsion.
-Although the effect of electrostatic repulsions has been studied, our results are observed after salt screens surface charges and electrostatic repulsions can be negligible in our system.
-% Explanation 3) Hydrodynamic interactions.
-Thus, the only possible explanation is the effect of hydrodynamic interactions.
-Hydrodynamic interactions originate from the incompressivility of the solvent, whose effect between colloids have been demonstrated by both numerical simulations and the experiments of optical tweezers.
-For compaction, clusters must squeeze the solvent inside the cluster to the outside.
-% Conclusion.
-Our results suggest that squeezing process can be the bottleneck of compaction and hydrodynamic interactions enhance linear structures in clusters.
-
-% Results of growth
-% topic sentence
-To investigate whether clusters can reach compact states in their growing stage, fractal dimension of each time is analysed in Figure~\ref{fig:fluid_dilute}b.
-% General explanation about fractal dimension.
-In general, compact clusters have df around three, whereas chain-like clusters have df around one.
-%Our results of fractal dimensions
-Our results show that df increases from 1 in the early stage to 2 in the late stage but df is much lower than three.
-% Explanation 1) DLCA
-Previously diffusion limited cluster aggregation model has been proposed to explain uncompact structures of clusters, assuming sticky attractions.
-But DLCA model predicts that df is always fixed around 1.85, which contradicts to our results.
-% Addressing our question
-Therefore, other mechanism should decrease df close to 1 from condensation equilibrium.
-% Explanation 2) Hydrodynamic interactions
-As discussed in the early stage of cluster formation, hydrodynamic interactions can frustrate condensation of clusters.
-If clusters form chain-like structures, clusters can both avoid squeezing process and decrease resistance from external flow.
-Therefore, structures of df = 1 are hydrodynamically favored though energetically disfavored.
-% Conclusion
-Our results suggest that hydrodynamic interactions dominate the system in the early stage.
-As the cluster aggregation proceeds, each colloid can access to a more compact state, squeezing out the solvent in the cluster, and df gradually increases.
-
-\section{Dilute gels} % Subject II: Dilute gels
-% Topic sentence
-Next, we focus on the mechanism of gelation in a dilute system.
-% Our results
-Figure~\ref{fig:general}c-h shows the process of gelation of phi = 7\%.
-Clusters grow by connecting with each other and the radius of gyration of the biggest cluster finally becomes comparable to the system size as shown in Figure~\ref{fig:fluid_dilute}c. 
-Figure~\ref{fig:fluid_dilute}b shows that fractal dimension of clusters increase from 1 in the early stage to 2 in the late stage as similar with the case of cluster aggregation.
-% Addressing our question
-One can address a natural question about dilute gels: Why can the system percolate with phi of only 7\%?
-% Introduction to effective phi
-Number density of colloids has little importance since fractal dimension of the system is much lower than three and it changes during the gelation process.
-% Procedure to calculate the effective volume
-To calculate the ‘ effective ’ volume fraction of colloid, we replace each cluster with the effective sphere whose radius is equal to the radius gyration of the cluster.
-% Results of effective phi
-As shown in Figure~\ref{fig:fluid_dilute}, the effective volume fraction increases from 7\% in the early stage to 60\% in the late stage.
-% Discuss the mechanism of percolation in a dilute gel
-Our results clearly reveal that the system cannot avoid percolation because the effective volume fraction is too high.
-The reason for the 10 times increase of the effective phi is that df is much lower than three.
-The low df originates from hydrodynamic interactions.
-% Conclusion
-Therefore, percolation in a dilute system is a consequence of condensation frustrated by hydrodynamic interactions.
-
-\section{Dense gels} % Subject III: Dense gels
-% Topic sentence
-Gelation in a dense system, on the other hand, behaves different patterns than in a dilute system.
-% Results of the entire process of dense gelation
-As shown in Figure~\ref{fig:dense}a, the system accomplishes percolation in a few minutes, whereas coarsening process proceeds for several hours.
-% Focusing on percolation mechanism
-% Results of percolation
-When the system percolates at t = 5 min, the averaged number of nearest neighbours is only three and the averaged bond-bond angle is 105 deg.
-Thus, the network right after percolated has chain-like structures instead of condensed domains.
-% Discussions of percolation
-As shown in Figure~\ref{fig:fluid_dilute}a, the aggregated clusters in the early stage have linear structures by the effect of hydrodynamic interactions.
-In a dense system, linear clusters are generated simultaneously in a high density.
-The clusters connect with each other before they can reach compact states and form chain-like networks within a few Tb.
-% Conclusion
-Therefore, percolation in a dense system is a consequence of condensation frustrated by hydrodynamic interactions.
-
-% Focusing on coarsening mechanism
-The coarsening proceeds for a long term.
-% General discussion
-So, each colloid can access an energetically favoured structure by thermal fluctuations.
-As condensation proceeds, each colloid is captured in a ‘ cage ’ of nearest neighbours and finally arrested in a deep energy potential.
-This model is consistent with the previous suggestions based on the glass transition.
-% Introduction for elementary process of coarsening
-But the elementary process of coarsening has been unknown.
-In the early stage at t = 5 min, more than 99\% of all colloids connect with a single network.
-When one colloid moves to form a compact domain, the network interconnected with the colloid should cooperatively move.
-Therefore, coarsening process is frustrated by mechanical tensions and the mechanism to overcome the frustration for further condensation has great importance in basic research.
-% Results of NW cutting
-Figure~\ref{fig:dense}b-d shows an elementary process of coarsening, in which networks coarsens by seizing a part of the network.
-The single strand is strained between two strong chains.
-After stretched straight, the strand is seized and the fragments are integrated into strong chains.
-% Conclusion of elementary process of NW coarsening
-Therefore, the system can selectively seize weak chains of the network by inducing mechanical tensions and condensation proceeds until the local structures of the network are strong enough.
-
-\section{Conclusion} % Conclusion of this study
-% Topic sentence
-In this study, we analyse the entire process of colloidal gelation in a single particle level.
-% Universality of colloidal gelation
-To show the universality of colloidal gelation, Figure~\ref{fig:general} summarizes the processes of all our data of gel samples.
-In a dilute system, local condensation proceeds simultaneously as percolation.
-In contrast, dense systems accomplish percolation in the early stage, whereas local condensation proceeds until the late stage.
-% Conclusion of colloidal gelation
-In both cases of gelation, percolation is a consequence of condensation frustrated by hydrodynamic interactions, whereas the coarsening process is frustrated by mechanical tensions.
-%General impacts
-Generally, colloidal suspensions are model cases of the binary mixtures that consist of small and big components.
-Our study shed a new light on not only colloidal gelation but also dynamically asymmetric mixtures, which include polymer solutions and protein solutions.
+\section{Conclusion}
 

### 2015-09-22 gel_cond/trunk/paper.tex
Start describing fig:breaking d (stopped by possible master curve) Rewrite methods

@@
 To track the position of this peak, we compute the characteristic wave number $\langle q \rangle$ and show its temporal evolution in Figure~\ref{fig:phasediag}c.
-The curves for all samples follow a master curve coherent with spinodal decomposition kinetics: at short times $\langle q \rangle(t)$ shows a plateau indicating that the low $q$ peak builds up at constant wave number, whereas at intermediate times we observe coarsening with $\langle q \rangle \sim t^{-1/3}$.
+The curves for all samples follow a master curve coherent with spinodal decomposition kinetics: at short times $\langle q \rangle(t)$ shows a plateau indicating that the low $q$ peak builds up at constant wave number corresponding to distances of about $2\sigma$, whereas at intermediate times we observe coarsening with $\langle q \rangle \sim t^{-1/3}$.
 Finally at longer times each sample deviates from the master curve to form a plateau indicating arrest.
@@
 
-\subsection*{Internal stresses}
+\subsection*{Network ageing}
 
@@
 On Figure~\ref{fig:breaking}a we observe the slow build up of tension over the first \SI{30}{\minute}, until the tension is concentrated on a one particle thin strand.
-This strand breaks and the particles involved merge in their respective part of the network than can diffuse away from each other.
+This strand breaks and the particles involved merge in their respective part of the network that then stay apart from each other.
 
@@
 
+In Figure~\ref{fig:breaking}d we show the time evolution of the probability for a topologically relevant strand rupture $P_\text{break}(L>3)$, i.e.
+the ratio of the number of bond breaking events with $L>3$ by the number of bonds.
+Interestingly, for all samples that show percolation before coarse graining, see Figure~\ref{fig:phasediag}b, strand rupture is maximum just after percolation.
+
+We saw in Figure~\ref{fig:phasediag}c that at these times, the strands are in average only one or two particles thick and thus easily break under tension.
+
 \section{Conclusion}
@@
 Here the solvent may be regarded as ``good'' and a Flory scaling of the measurements of~\cite{lu2008gelation} yields $R_g=\SI{148}{\nano\metre}$.
+In the absence of salt, the Debye length is expected to reach several \si{\micro\metre} and the (weakly) charged colloids experience a long range electrostatic repulsion~\cite{Royall2003}.
+We confirm that colloids never come close enough to feel the short-ranged attraction and form a Wigner crystal.
 
-The data were collected on a Leica SP5 confocal microscope, using \SI{532}{\nano\metre} laser excitation.
-The temperature was controlled on both stage and objective lens, allowing a more precise density matching.
-The scanned volume is at least $82 \times 82 \times \SI{85}{\micro\metre}$.
-Standard particle tracking techniques allow us to localise our particles with errors below $1\%$ of a diameter.
-We carefully set the scanning time in order to be able to follow between two successive time steps all the colloids that stay in the field of view.
-
-From direct confocal measurement~\cite{Royall2007, Poon2012}, we estimate the hard-core diameter of our colloids ($\sigma=\SI{2.75}{\micro\metre}$) and the range of the interaction potential (that confirmed our scaling of $R_g$ within $1\%$), leading to a polymer-colloid size ratio $q = 2R_g/\sigma = 0.10(6)$.
-Spinodal and binodal lines on Fig.~\ref{fig:methods}b are calculated from this size ratio using the generalized free volume theory~\cite{Fleer2008}.
-In principle two particles are considered bonded when their centres are within $\sigma+2R_g$, however resolution-dependent tracking imprecisions and systematic errors do not give a precise enough estimate of such short distance.
-Therefore we use the first minimum of $g(r)$ as a threshold, which is $3.40 \text{ or } \SI{3.55}{\micro\metre}$ depending on the resolution.
-
-In the absence of salt, the Debye length is expected to reach several \si{\micro\metre} and the (weakly) charged colloids experience a long range electrostatic repulsion.
-We confirm that colloids never come close enough to feel the short-ranged attraction.
-Screening by tetrabutylammonium bromide (Fluka) at saturated concentration brings down the Debye length to about \SI{100}{\nano\metre}, practically discarding the repulsion.
-
-% Salt-reservoir system
-%% Design of the cell
-The colloids and polymers are contained in an observation cell ($\SI{1}{\milli\metre^2} \times \SI{200}{\micro\metre}$) in contact with an half-open reservoir approximately 400 larger in volume, via a millipore filter with pore size of \SI{100}{\nano\metre} that allows the salt through but neither polymer nor colloid (see Fig.~\ref{fig:methods}).
-
-Initially the system is salt-free and colloids repel each-other to form a Wigner crystal~\cite{Royall2003}.
-A super-saturated salt solution at density matching composition is then added to the reservoir, which is immediately sealed to prevent evaporation.
+The colloids and polymers are contained in an observation cell ($\SI{1}{\milli\metre^2} \times \SI{200}{\micro\metre}$) made of glass in contact with an half-open glass channel approximately 400 larger in volume, via a millipore filter with pore size of \SI{100}{\nano\metre} that allows the salt through but neither polymer nor colloid (see Fig.~\ref{fig:cell_vs_cap}a).
+The channel is filled with the same solvents at density matching composition.
+At the beginning of the experiment, solid tetrabutylammonium bromide (Fluka) is introduced to the channel which is immediately sealed to prevent evaporation.
+Data acquisition starts within \SI{30}{\second} after salt introduction.
 Our procedure induces practically no solvent flow in the observation cell.
 We confirmed the presence of undissolved salt several days after mixing, indicating that the observation cell was brought to saturation concentration.
-Data acquisition starts within \SI{30}{\second} after salt introduction.
 
@@
 
+We collect the data on a Leica SP5 confocal microscope, using \SI{532}{\nano\metre} laser excitation.
+The temperature was controlled on both stage and objective lens, allowing a more precise density matching.
+The scanned volume is at least $82 \times 82 \times \SI{85}{\micro\metre}$.
+The particle coordinates are tracked in three dimensions (3D) with an accuracy of around $0.03\sigma$~\cite{LeocmachColloids}.
+
 \subsection*{Analysis}
 
-%% Track clusters
-To analyse compaction dynamics of clusters with three colloids, we search trajectory of each colloid such that the size of the cluster that contains the colloid is equal to three for continuous time steps.
-%% Colouring the picture of cutting NW
-???.
+From direct confocal measurement~\cite{Royall2007, Poon2012}, we estimate the hard-core diameter of our colloids ($\sigma=\SI{2.75}{\micro\metre}$) and the range of the interaction potential (that confirmed our scaling of $R_g$ within $1\%$), leading to a polymer-colloid size ratio $q = 2R_g/\sigma = 0.10(6)$.
+Spinodal line on Fig.~\ref{fig:phasediag}b are calculated from this size ratio using the generalized free volume theory~\cite{Fleer2008}.
+
+In principle the attraction well of the depletion extends to $\sigma+2R_g$, however resolution-dependent tracking imprecisions and systematic errors do not give a precise enough estimate of such short distance.
+Therefore we consider two particles bonded when their distance is shorter the first minimum of $g(r)$, i.e.
+\SI{3.55}{\micro\metre}.
+This defines the bond graph that we analyse using connected components and shortest path analysis algorithms~\cite{Hagberg2008}.
+
+To detect local 2-fold symmetry and thus elongation, we use \citet{steinhardt1983boo} bond orientational order for the particle $i$,
+\begin{align}
+	q_2(i) =& \sqrt{\frac{4\pi}{5} \sum_{m=-2}^{2} |q_{2,m}(i)|^2 }, \label{eq:ql}\\
+	q_{2,m}(i) =& \frac{1}{N_i}\sum_{j=1}^{N_i} Y_{2,m}(\theta(\mathbf{r}_{ij}),\phi(\mathbf{r}_{ij})),
+	\label{eq:qlm}
+\end{align}
+where the $Y_{\ell, m}$ are spherical harmonics and $\mathbf{r}_{ij}$ is one of the $N_i$ bonds involving particle $i$.
 

### 2015-09-25 paper.tex
Power -4/3 in rupture rate Explain by spinodal and then arrested phase separation

@@
 
-\subsection*{Internal stresses}
+\subsection*{Network ageing}
 
-\section{Cluster aggregation} % Subject I: Cluster formation
-% Topic sentence
-Figure~\ref{fig:methods}a shows the phase diagram of all samples.
-First of all, we focus on cluster formation since clusters constitute ``building blocks'' of gels.
-% Results of birth
-Figure~\ref{fig:fluid_dilute} a shows the compaction dynamics of the clusters with three colloids in the early stage.
-The results show that the clusters can hardly accomplish compaction within one Brownian motion time and clusters with four and five colloids show very similar tendency (Supplement).
-% Explanation 1) Local energy minimization.
-If one assumes that each colloid can move independently by Brownian motion and static short-range attractions are induced between colloids, the clusters with three colloids should reach the compact states within one Brownian motion time.
-This explanation contradicts to our results.
-% Addressing our question
-In other words, some interactions stabilize linear structures, competing with the principle of energy minimization.
-% Explanation 2) Electrostatic repulsion.
-Although the effect of electrostatic repulsions has been studied, our results are observed after salt screens surface charges and electrostatic repulsions can be negligible in our system.
-% Explanation 3) Hydrodynamic interactions.
-Thus, the only possible explanation is the effect of hydrodynamic interactions.
-Hydrodynamic interactions originate from the incompressivility of the solvent, whose effect between colloids have been demonstrated by both numerical simulations and the experiments of optical tweezers.
-For compaction, clusters must squeeze the solvent inside the cluster to the outside.
-% Conclusion.
-Our results suggest that squeezing process can be the bottleneck of compaction and hydrodynamic interactions enhance linear structures in clusters.
+\begin{figure*}
+\includegraphics{figs/breaking.pdf}
+\caption{\textbf{Mechanical tension drives coarsening} 
+\textbf{a} Reconstruction from experimental coordinates ($\phi=29~\%$, $c_p=\SI{0.7}{\gram\per\litre}$) of coarsening process geometry (top) and topology (bottom).
+Particles are drawn to scale and coloured by $q_2$ from blue (low) to red (high).
+The meshed surface is a Gaussian coarse-graining of the network pattern.
+The red line indicates the shortest on-graph path between the two particles of interest.
+\textbf{b} Number of bond breaking function of the future on-graph distance $L$ (after percolation) for the three percolating state points of figure 2 (same colours and markers).
+%three state points of increasing density: $\phi=8,\,16,\,27~\%$, $c_p=1.5,\,1.2,\,\SI{1}{\gram\per\litre}$ for \textcolor{red!80!yellow}{$\circ$}, \textcolor{red!80!black}{\tiny$\blacksquare$} and \textcolor{red!40!black}{$\bullet$} respectively.
+\textbf{c} Probability for a bond to break during $3\tau_B$ function of bond-centred $q_2$ for all events (blue) and for events with $L>1$ (thick red) in the same sample as \textbf{a}.
+\textbf{d} Evolution of the topologically relevant bond breaking probability ($L>3$) for the same state points  as in b. Vertical lines indicate the respective percolation times.
+}
+\label{fig:breaking}
+\end{figure*}
 
-% Results of growth
-% topic sentence
-To investigate whether clusters can reach compact states in their growing stage, fractal dimension of each time is analysed in Figure~\ref{fig:fluid_dilute}b.
-% General explanation about fractal dimension.
-In general, compact clusters have df around three, whereas chain-like clusters have df around one.
-%Our results of fractal dimensions
-Our results show that df increases from 1 in the early stage to 2 in the late stage but df is much lower than three.
-% Explanation 1) DLCA
-Previously diffusion limited cluster aggregation model has been proposed to explain uncompact structures of clusters, assuming sticky attractions.
-But DLCA model predicts that df is always fixed around 1.85, which contradicts to our results.
-% Addressing our question
-Therefore, other mechanism should decrease df close to 1 from condensation equilibrium.
-% Explanation 2) Hydrodynamic interactions
-As discussed in the early stage of cluster formation, hydrodynamic interactions can frustrate condensation of clusters.
-If clusters form chain-like structures, clusters can both avoid squeezing process and decrease resistance from external flow.
-Therefore, structures of df = 1 are hydrodynamically favored though energetically disfavored.
-% Conclusion
-Our results suggest that hydrodynamic interactions dominate the system in the early stage.
-As the cluster aggregation proceeds, each colloid can access to a more compact state, squeezing out the solvent in the cluster, and df gradually increases.
+We now change our focus to percolated samples.
+As we saw in Figure~\ref{fig:phasediag}c, the coarsening in these samples is much slower than what is expected from spinodal decomposition dynamics.
+The phase separation is arrested, but the system is still ageing, a process sometimes leading to delayed sudden collapse of gels~\cite{Teece2011,Bartlett2012}, a catastrophic phenomenon from the industrial point of view.
+Previous studies~\cite{Tanaka2007,Bartlett2012} have shown that the main coarsening mechanism is the rupture of strands in the network, a process that to our knowledge has not been followed experimentally at the particle level.
 
-\section{Dilute gels} % Subject II: Dilute gels
-% Topic sentence
-Next, we focus on the mechanism of gelation in a dilute system.
-% Our results
-Figure~\ref{fig:general}c-h shows the process of gelation of phi = 7\%.
-Clusters grow by connecting with each other and the radius of gyration of the biggest cluster finally becomes comparable to the system size as shown in Figure~\ref{fig:fluid_dilute}c. 
-Figure~\ref{fig:fluid_dilute}b shows that fractal dimension of clusters increase from 1 in the early stage to 2 in the late stage as similar with the case of cluster aggregation.
-% Addressing our question
-One can address a natural question about dilute gels: Why can the system percolate with phi of only 7\%?
-% Introduction to effective phi
-Number density of colloids has little importance since fractal dimension of the system is much lower than three and it changes during the gelation process.
-% Procedure to calculate the effective volume
-To calculate the ‘ effective ’ volume fraction of colloid, we replace each cluster with the effective sphere whose radius is equal to the radius gyration of the cluster.
-% Results of effective phi
-As shown in Figure~\ref{fig:fluid_dilute}, the effective volume fraction increases from 7\% in the early stage to 60\% in the late stage.
-% Discuss the mechanism of percolation in a dilute gel
-Our results clearly reveal that the system cannot avoid percolation because the effective volume fraction is too high.
-The reason for the 10 times increase of the effective phi is that df is much lower than three.
-The low df originates from hydrodynamic interactions.
-% Conclusion
-Therefore, percolation in a dilute system is a consequence of condensation frustrated by hydrodynamic interactions.
+Figure~\ref{fig:breaking}a shows a strand rupture reconstructed from confocal 3D images, the colours mapping the intensity of internal stresses acting on each particle.
+In practice, the attraction potential well is too narrow relative to the particle localisation errors for us to extract directly the force acting on a particle.
+Therefore, we use the elongation of the particle neighbourhood as a proxy.
+The more the bonds around a particle are oriented along a single axis, the more tension is exerted on the particle.
+This local elongation is quantified using~\cite{steinhardt1983boo} bond orientational order for the 2-fold symmetry $q_2$, see Methods for a precise definition.
+On Figure~\ref{fig:breaking}a we observe the slow build up of tension over the first \SI{30}{\minute}, until the tension is concentrated on a one particle thin strand.
+This strand breaks and the particles involved merge in their respective part of the network that then stay apart from each other.
 
-\section{Dense gels} % Subject III: Dense gels
-% Topic sentence
-Gelation in a dense system, on the other hand, behaves different patterns than in a dilute system.
-% Results of the entire process of dense gelation
-As shown in Figure~\ref{fig:dense}a, the system accomplishes percolation in a few minutes, whereas coarsening process proceeds for several hours.
-% Focusing on percolation mechanism
-% Results of percolation
-When the system percolates at t = 5 min, the averaged number of nearest neighbours is only three and the averaged bond-bond angle is 105 deg.
-Thus, the network right after percolated has chain-like structures instead of condensed domains.
-% Discussions of percolation
-As shown in Figure~\ref{fig:fluid_dilute}a, the aggregated clusters in the early stage have linear structures by the effect of hydrodynamic interactions.
-In a dense system, linear clusters are generated simultaneously in a high density.
-The clusters connect with each other before they can reach compact states and form chain-like networks within a few Tb.
-% Conclusion
-Therefore, percolation in a dense system is a consequence of condensation frustrated by hydrodynamic interactions.
+To detect strand rupture, we use the topology of the bond network.
+We can consider the gel as a graph with the particles as nodes and the bonds as edges.
+This graph evolves from frame to frame separated by $3\tau_B$.
+In the lower part of Figure~\ref{fig:breaking}a we draw in red the shortest on-graph path between two particles of interest.
+Before the strand rupture, this path is a single bond long.
+After the rupture, the shortest path is much longer.
+In general, when two particles were bonded on the previous frame and are no more bonded on the present frame, we define the post-breaking topological distance $L$ as the new shortest distance on the graph between them, minus 1.
+If the particles still have a common neighbour then $L=1$, because two bonds are needed to go from one to the other.
+$L=2$ when three bonds are needed, etc.
 
-% Focusing on coarsening mechanism
-The coarsening proceeds for a long term.
-% General discussion
-So, each colloid can access an energetically favoured structure by thermal fluctuations.
-As condensation proceeds, each colloid is captured in a ‘ cage ’ of nearest neighbours and finally arrested in a deep energy potential.
-This model is consistent with the previous suggestions based on the glass transition.
-% Introduction for elementary process of coarsening
-But the elementary process of coarsening has been unknown.
-In the early stage at t = 5 min, more than 99\% of all colloids connect with a single network.
-When one colloid moves to form a compact domain, the network interconnected with the colloid should cooperatively move.
-Therefore, coarsening process is frustrated by mechanical tensions and the mechanism to overcome the frustration for further condensation has great importance in basic research.
-% Results of NW cutting
-Figure~\ref{fig:dense}b-d shows an elementary process of coarsening, in which networks coarsens by seizing a part of the network.
-The single strand is strained between two strong chains.
-After stretched straight, the strand is seized and the fragments are integrated into strong chains.
-% Conclusion of elementary process of NW coarsening
-Therefore, the system can selectively seize weak chains of the network by inducing mechanical tensions and condensation proceeds until the local structures of the network are strong enough.
+$L$ is a good measure of the significance of a bond breaking event.
+Small values indicate a local rearrangement whereas large values are the signature of important changes in the topology of the network, namely strand rupture.
+Figure~\ref{fig:breaking}b shows the distribution of $L$ for three colloidal volume fractions.
+Excluding the largest values that are dominated by the limited size of the field of view, $L$ seems to follow a power-law distribution of exponent between $-3$ and $-4$.
+However the values at $L=1$ seems in excess.
+Figure~\ref{fig:breaking}c compares the probability distribution of $q_2$ for all bond breaking events versus for evens with $L>1$.
+In both cases bonds about to break have a higher probability of being under tension, but this trend is much clearer when excluding local events.
+Both observations point to spurious detection of bond breaking events due to localisation errors comparable to the short attraction range and rattling of particles.
+For this reason, but also to focus on topologically relevant strand rupture, we discard all events with $L<4$ in the following analysis.
 
-\section{Conclusion} % Conclusion of this study
-% Topic sentence
-In this study, we analyse the entire process of colloidal gelation in a single particle level.
-% Universality of colloidal gelation
-To show the universality of colloidal gelation, Figure~\ref{fig:general} summarizes the processes of all our data of gel samples.
-In a dilute system, local condensation proceeds simultaneously as percolation.
-In contrast, dense systems accomplish percolation in the early stage, whereas local condensation proceeds until the late stage.
-% Conclusion of colloidal gelation
-In both cases of gelation, percolation is a consequence of condensation frustrated by hydrodynamic interactions, whereas the coarsening process is frustrated by mechanical tensions.
-%General impacts
-Generally, colloidal suspensions are model cases of the binary mixtures that consist of small and big components.
-Our study shed a new light on not only colloidal gelation but also dynamically asymmetric mixtures, which include polymer solutions and protein solutions.
+In Figure~\ref{fig:breaking}d we show the time evolution of the probability for a topologically relevant strand rupture $P_\text{break}(L>3)$, i.e.
+the ratio of the number of bond breaking events with $L>3$ by the number of particles.
+$P_\text{break}$ is maximum at percolation and then decreases and finally saturates.
+Strikingly all curves collapse after percolation, indicating common physical ingredients for the ageing of gels at all concentrations.
+
+Initially, clusters are in elongated, unstable configurations.
+When isolated, a cluster is able to relax to a more compact and stable shape.
+However in dense samples, elongated clusters meet before any compaction into large branched clusters able to transmit stresses.
+The compaction trend exerts internal stresses on the strands inside those clusters large enough to make them rupture.
+This effect is maximum when the sample is fully percolated and thus the internal stresses are maximum.
+
+The characteristic size of a spinodal network is $\xi(t)\sim t^{1/3}$.
+Strands being linear objects, their volume is linear in $\xi$ and thus the number of strands in the field of view $N_s$ evolves as $t^{-1/3}$.
+If we suppose that after the percolation no new strands are created, the variation in the number of strands is only given by the strand rupture rate:
+\begin{equation}
+P_\text{break} = -\frac{d N_s}{dt} \sim t^{-4/3}.
+\end{equation}
+Indeed in Figure~\ref{fig:breaking}d we observe that the initial regime of the master curve is well described by a power law of exponent $-4/3$.
+
+At longer times, most of the internal stresses have been released and the system reaches arrested phase separation, where the strand rupture rate becomes comparable to the strand creation rate.
+
+For dilute samples, percolation happens later, after the end of the power law regime. The clusters have already compacted to stable configurations and internal stresses are low.
+
+\section{Conclusion}
 

### 2015-10-19 gel_cond/trunk/manuscript4.tex

\documentclass[preprint,footinbib,amsmath,amssymb]{revtex4}
\usepackage{graphicx,amsmath}
\usepackage{color}
\begin{document}
\draft

\title{Gelation as condensation frustrated by hydrodynamics and mechanical tension}
\author{Hideyo Tsurusawa}
%\thanks{These authors contributed equally to this work}
\author{Mathieu Leocmach}
%\thanks{These authors contributed equally to this work}
\author{Hajime Tanaka}
%\email{tanaka@iis.u-tokyo.ac.jp}
\affiliation{ {Institute of Industrial Science, University of Tokyo, 4-6-1 Komaba, Meguro-ku, Tokyo 153-8505, Japan} }

\begin{abstract}
{\bf A colloidal gel is an important non-ergodic state of matter, which can have elasticity and fluidity at the same time. Colloidal gels are known to be formed by phase separation accompanying dynamical arrest of a colloid-rich phase due to glass transition \cite{piazza1994phase,verhaegh1997,tanaka1999colloid,poon2002,lu2008gelation}. 
The presence of a liquid component should play crucial roles in the formation of a network structure and its time evolution, since it gives a constraint from the conservation of fluid momentum, which is known to affect the kinetic pathway of non-equilibrium phenomena \cite{tanaka2000viscoelastic}. However, there has so far been no experimental study on this important problem.  
Using a novel experimental protocol initiating phase separation, we successfully follow by confocal microscopy observation the entire process of gelation from the very beginning with a single-particle resolution   
and reveal the roles of hydrodynamics and mechanics in gelation, for the first time. 
%We switch off long-range Coulomb interactions between charged colloids by injecting salt at $t=0$ through an osmotic membrane and make depletion attractions due to polymers operative. This initiates phase demixing without inducing disturbing flow, which is inevitable for a conventional method, i.e., simple mixing of colloids and polymers at $t=0$. 
We show that hydrodynamic interactions between colloids mediated by a liquid component are the key to formation of a percolated network structure in  
a dilute system. Furthermore, the network formed by this mechanism is inevitably in a high energy state and under self-generated mechanical tension due to its connectivity. We find clear experimental evidence that network coarsening proceeds by sequentially repeating stress-driven mechanical fracture of a network strand. A stable gel is then formed when the network breaking rate becomes negligible. 
%Thus, we succeeded in clarifying the roles of momentum conservation, more specifically hydrodynamics and mechanics, in gelation, which has not been accessed experimentally. 
These findings provide an experimental basis for understanding the microscopic physical mechanism of gelation and its structural formation, whose kinetic pathway is selected not by a thermodynamics factor but by mechanical factors.}
\end{abstract}

\maketitle

%\section*{Introduction} 
Gels do not flow and behave as soft solids in a macroscopic scale, but have excellent fluid-like transport characteristics in a microscopic scale, 
which often provides essential functions of many biological gels including those in our body.  
For any gels, elasticity comes from the presence of a space-spanning percolated network that can transmit mechanical stress.
However, the network can be formed by different mechanisms: chemical reaction and physical processes such as phase separation. 
Gels spontaneously formed by phase separation are an important class of gels, which can be seen commonly in various soft matter \cite{tanaka2013phase} such as colloidal suspensions, emulsions, protein solutions, surfactant solutions, and polymer solutions, and now widely known as ``spinodal gels''.  This type of gels are not only of fundamental importance in physical, materials, and biological science, but also of technological importance in food, cosmetics, and medical industries.

The mechanism of spinodal gelation has particularly been studied for colloidal suspensions since they can be regarded as a model system for other systems. Thanks to the extensive study in past, we now have a reasonable physical picture: Gelation is induced by spinodal decomposition to two phases whose dynamics are very different \cite{tanaka1999colloid,tanaka2000viscoelastic} and the resulting vitrification of the slower phase \cite{piazza1994phase,verhaegh1997,tanaka1999colloid,poon2002,lu2008gelation}. 
However, the knowledge of ordinary spinodal decomposition cannot explain the observed behaviour since it predicts that the minority colloid-rich phase should form isolated clusters rather than a percolated network. This mystery was solved by using an analogy of phase separation of colloidal suspensions to that of polymer solutions on the basis of the concept of dynamic asymmetry \cite{tanaka1999colloid}. 
What is common in these two systems is that a mixture is composed of large slow components (colloid or polymer) and small fast components (solvent). 
On a macroscopic level, such dynamically asymmetric mixtures are known to show universal pattern formation, known as ``viscoelastic phase separation'' \cite{tanaka2000viscoelastic}. 
On a microscopic level, however, there are essential differences between colloidal suspensions and polymer solutions coming from the topological difference (sphere vs. chain), leading to 
distinct rheological behaviours. Thus there are many open questions about the elementary process of phase separation of colloidal suspensions and the resulting colloidal gelation.   
From the physical viewpoint, the presence of a fluid component indicates the importance of fluid momentum conservation in phase separation, which makes hydrodynamics and mechanics active in structural evolution. This is the key for viscoelastic phase separation \cite{tanaka1999colloid,tanaka2000viscoelastic}. There have been some numerical studies on the role of hydrodynamics~\cite{tanaka2000simulation,Furukawa2010} and mechanics~\cite{Tanaka2007,colombo2014self,testard2014intermittent} in colloidal gelation, however, there has so far been no experimental study that directly addresses these effects by dynamical observation of the process.

%However, there have remained many open questions: (1) Spinodal decomposition usually form compact clusters (or, droplet) at low volume fractions where colloidal gels are formed, but actually it produces a space-spanning percolated network.  According to the common knowledge of ordinary phase separation, bicontinuous network can be formed only when the volume fraction is near 50 \%. (2) Even after forming a percolated network, i.e. a gel, structural evolution often slowly continues to proceed. This kind of ageing behaviour is quite important for a long-time stability of a gel state and a crucial problem in industries. (3) It is intuitively appealing that vitrification leads to dynamical arrest of spinodal decomposition and freezes the network structure of gels. But vitrification, or glass transition, is originally defined for bulk materials. On noting that the strands of a gel network are often very thin, and thus it is hardly clear whether we can apply the concept of glass transition as it is to describe dynamic arrest in gelation.

To access these fundamental problems experimentally, we need to study the entire process of gelation from the beginning to the end at the single-particle resolution. 
Thus, confocal microscopy observation is necessary. However, it has been very difficult to study the very early and late stage of gelation by this method. 
Gelation of micron-size colloids is usually induced by depletion attractions due to polymers in the solvent. 
%Polymers used for this purpose usually have high molecular weights because colloids have to be large enough for realizing particle-level resolution, which results in a high viscosity of the polymer solution. Ideally we want to switch on attractive interactions at $t=0$. But a high viscosity of a polymer solution prevents its rapid mixing with a colloidal suspension at $t=0$. 
The experimental protocols used so far for studying the kinetics of phase separation and gelation are as follows: (1) Colloidal suspensions and polymer solutions are mixed just before an experiment and after mixing transferred to a capillary tube as quick as possible. 
(2) A mixture, which is already in a final state point in the phase diagram and intrinsically unstable, or phase-separated, is vigorously mixed just before an experiment to break pre-existing phase separated structures by shear melting. 
However, these protocols have two common serious deficiencies: Firstly the initial state can never been homogeneous perfectly and there already exist particle aggregates at $t=0$. Secondly, the mixing inevitably involves 
turbulent flow, which does not decay but remain when the observation is initiated. 
Because of these intrinsic problems of the conventional protocols, it has been almost impossible to access the very initial stage of gelation without interference of pre-existing aggregates and/or turbulent flow.  
Strictly speaking, the gelation process observed by these conventional protocols inevitablly suffers from the influence of ill-defined initial static and dynamic conditions. 
%On the other hand, to access the late stage, we need to achieve a very accurate density matching to prevent gravitational effects and also a very accurate determination of coordinates of particles.  
%Now we review what has so far been known for the above open questions. On question (1), some time ago we proposed an explanation on the basis of the concept of viscoelastic phase separation. When the two components of a mixture have large size disparity and the resulting strong dynamic asymmetry, even the minority phase can form a percolated network structure. This is supported by numerical simulations using the viscoelastic model on the basis of an empirical constitutive relation \cite{tanaka2000viscoelastic}, however, how we can explain this at a microscopic level. We stress that there is no well-defined constitutive (stress-strain) relation for colloidal suspensions \cite{tanaka1999colloid}. We have studied numerically colloidal gelation by incorporating many-body hydrodynamic equation \cite{Furukawa2010} and showed the incompressibility of a fluid component prevents the formation of compact clusters but assists the formation of elongated clusters. However, there has been no experimental observation of the dynamical process of particle aggregation that shows a clear signature of the important roles of hydrodynamic interactions, although there is a work studying the characteristics of instantaneous cluster structures. However, we cannot deny a possibility that elongated clusters are formed not due to many-body hydrodynamic interactions, but rather by the above-mentioned turbulent flow induced by the conventional protocol. To reveal hydrodynamic effects in a convincing manner, thus, we need to study the dynamical process of particle clustering without any interference of perturbative flow.  On question (2), we have some numerical evidence for the important role of mechanical stress in network coarsening ~\cite{Tanaka2007,colombo2014self,testard2014intermittent}, but there has so far been no experimental evidence to our knowledge. On question (3), we need to clarify the relation between mechanical stress and yield stress. 
In this Letter, we study roles of hydrodynamics and mechanics in colloidal gelation experimentally by dynamical confocal microscopy observation of the entire gelation process from the beginning to the end with particle-level resolution. 
To access roles of hydrodynamics in the initial stage of gelation, we develop a new protocol to initiate phase separation without causing any harmful flow. 
To access roles of mechanics in the late stage, we realize the density matching of the order of 10$^{-4}$ and use a very accurate particle tracking method \cite{leocmach2013novel}. 
%In previous studies, the process of gelation has been studied experimentally by following the structural evolution. However, the roles of hydrodynamic interactions and mechanical stresses have never been addressed experimentally. 
These allow us to experimentally reveal (i) the importance of hydrodynamic interactions in forming and stabilizing elongated clusters and their percolation and (ii) the crucial role of mechanical stress 
in ageing of gels and a microscopic mechanism of the network breakup events. These findings will provide crucial information on the mechanisms of gel formation and coarsening and also 
on the fate of gels.

%\section*{Results}

%\subsection*{System design}

We designed an experimental set-up that allows the observation of the entire process of gelation at a single particle level. For that, we use a colloidal system that is charge stabilised at long range, has a short range depletion attraction, and is also sterically stabilised causing nearly hard sphere repulsion at contact. We disperse colloidal particles and non-adsorbing polymers in a  mixture of organic solvents that matches both the refractive index and the density of the particles. Because of the weakly polar nature of the solvent mixture (its dielectric constant $\epsilon_r = 5\sim6$), the Debye screening length is about $\kappa^{-1}=10$ $\mu$m, long enough for the large colloids (diameter $\sigma=2.75$ $\mu$m) to form a homogeneous Wigner crystal in the mixture~\cite{klix2010structural}, since the short ranged ($\sim \sigma/10$), depletion attraction caused by the polymers is masked by the electrostatic repulsion.

We enclose the suspension in a thin microscopy cell sketched in Fig.~\ref{fig:cell_vs_cap}a. The bottom wall of the cell is an osmotic membrane providing contact with a long channel full of the same solvent mixture. We introduce solid salt at the other end of the channel that we seal immediately. Salt dissolution and subsequent migration of the ions along the channel and through the membrane induce screening of the electrostatic repulsion, well revealing the depletion potential due to the pre-existing polymers. The time needed for the ions to diffuse from the membrane across the cell thickness is of the same order of magnitude as the Brownian time of the particles $\tau_B=10$ s. This method causes uniform gelation starting from the homogeneous Wigner crystal state without any solvent flow, allowing \textit{in situ} confocal microscopy observation throughout the process from $t \sim 0$.

As noted above, the conventional shaking or shear melting protocols for the initiation of phase separation cause severe non-ideal perturbation to a system. To show this,  
we compare, in Fig.~\ref{fig:cell_vs_cap}b and c, confocal microscopy images of the final structures for two gels prepared at the same state point: one by our protocol and the other by introducing in a capillary an existing gel and thus shear melting it, respectively. The later is coarser, highlighting that shaking or shear melting protocols~\cite{lu2008gelation,Teece2011,Bartlett2012} are not equivalent to a quench. 
Our novel quench protocol provides an ideal experimental platform to make a comparison with theory and simulations. However, we note that Brownian Dynamics simulations cannot reproduce our experimental results even with the same quench, because of the lack of a solvent mediating hydrodynamic interactions~\cite{tanaka2000simulation,Furukawa2010}. 
%Thus our protocol might be very close to application relevant processes where the sudden addition of a component (e.g. salt, acid, depletion agent) induces aggregation in an otherwise stable suspension (e.g. milk).

In Fig.~\ref{fig:cell_vs_cap}d, we show a computer reconstruction from experimental coordinates of a typical gelation experiment at a relatively low volume fraction ($\phi=7.5\%$). Immediately before ions enter the cell ($t=0$), the suspension is in a Wigner crystal state where the particles are far apart due to long range Coulomb repulsion. As soon as the charges are screened, the particles begin to aggregate and form clusters that progressively connect to each other while coarsening to finally percolate over the field of view around $t=35$ min.

%\subsection*{Observation of the initial stage}

In Fig.~\ref{fig:phasediag}a, we show the phase diagram, where we can divide the state points into three regions based on the final state obtained by our protocol: at low polymer concentration ($c_p<0.2$ g/$\ell$) a sample fully relaxes to a fluid state; at very low colloid volume fraction ($\phi<0.05$) and high polymer concentration the particles condense into long-lived well separated clusters as observed in~\cite{Lu2006}; in the rest of the explored phase space we observe a long-lived space spanning network. 
We also show the theoretical spinodal line obtained by generalised free volume theory~\cite{Fleer2008}, which is in good agreement with our experimental points 
(the small discrepancy at small colloidal volume fractions is common in free volume theory~\cite{Shah2003,Bergenholtz2003,lu2008gelation}).

With our technique we can observe the entire kinetic path leading to the final state at a single-particle level. To characterise this path, we compute the instantaneous mean number of neighbours $\bar{N}_C$, or coordination number that quantifies the compactness of the structure. We also compute the the spatial extent of the largest cluster $l_\text{max}$ that we normalize by the size of the field of view $L$ to obtain a measure of the distance to percolation of the system. Figure~\ref{fig:phasediag}b shows a system trajectory in the $(l_\text{max}/L, \bar{N}_C)$ plane for various colloidal volume fractions. At high densities, percolation takes place first, within the first few $\tau_B$ after charge screening by salt, and then coarsening proceeds. At low densities, percolation never takes place and we observe the compaction of individual clusters. In between, we observe the process detailed in Fig.~\ref{fig:cell_vs_cap}d: formation of low-compacity clusters that then slowly connect together to build the percolating network. This process can take hundreds of $\tau_B$ and is competing with cluster compaction, as indicated by the oblique trajectory (red open circles) in Fig.~\ref{fig:phasediag}b. The path to gelation in this plane is thus not universal and depends on the colloid volume fraction even within the gelation region.

The initial similarity between the trajectories of dilute gels and cluster phase is striking, as if their dynamics were ruled by the same phenomenon. To confront this hypothesis, we compute the time dependent static structure factor $S(q,t)$. For all gel and cluster samples, we observe the appearance of a low $q$ peak in $S(q)$, see Supplementary Figure XXX, which is characteristic of spinodal decomposition in a system of a conserved order parameter. To track the position of this peak, we compute the characteristic wave number $\langle q \rangle$ and show its temporal evolution in Fig.~\ref{fig:phasediag}c. The curves for all samples follow a master curve coherent with spinodal decomposition kinetics: At short times $\langle q \rangle(t)$ shows a plateau indicating that the low $q$ peak builds up at constant wave number corresponding to distances of about $2\sigma$. This plateau is characteristic of the early stage spinodal decomposition, which is described by Cahn's linear theory \cite{onuki2002phase}. At intermediate times, on the other hand, we observe coarsening with \textcolor{blue}{$\langle q \rangle \sim t^{-1/2}$, which is often observed in viscoelastic phase separation 
(see, e.g., \cite{Furukawa2010}).} Finally at longer times each sample deviates from the master curve to form a plateau indicating arrest. The more dilute samples arrest sooner, 
but the origin of arrest is different between clusters and percolated networks. For clusters, density fluctuations grow rather rapidly in the initial stage, but after the formation of isolated clusters it takes a long time since the diffusive evaporation-condensation mechanism does not work for colloidal viscoelastic phase separation and direct cluster collisions and coalescence are necessary for coarsening \cite{tanaka2000viscoelastic}. For networks, densification due to phase separation leads to dynamic arrest due to vitrification \cite{piazza1994phase,verhaegh1997,tanaka1999colloid,poon2002,zaccarelli2007,lu2008gelation} or formation of locally stable structures \cite{royall2008g}. 
Our observations indicate that both cluster and gel phases are due to viscoelastic spinodal decomposition: network-type spinodal for the gel, and droplet-type spinodal for the clusters where strong dynamical asymmetry between colloids and the solvent leads to unique roles of hydrodynamics and mechanics in phase separation \cite{tanaka1999colloid,tanaka2000viscoelastic}.

Here two questions remain, corresponding respectively to the dilute or dense routes to gelation: (i) How can individual clusters percolate a long time after their formation? (ii) How does a percolated network evolve toward more compact states? We will show that the answers come from mechanical effects: respectively hydrodynamics and internal mechanical stresses.

%\subsection*{Role of hydrodynamics}

First we focus on the role of hydrodynamics. 
In Fig.~\ref{fig:hydro}a, we follow the compaction of clusters made of only three particles in a non-percolating sample. The probability distribution of the radius of gyration $R_g$ of these triplets shows two peaks on both sides of $R_g^*=0.8\sigma$. For $R_g<R_g^*$ the cluster is compact, with a structure close to an equilateral triangle. For $R_g>R_g^*$ the three particles are aligned and the cluster is elongated. We found that just after the quench most triplets are elongated and then either connect to other clusters or relax to the more stable compact state. To follow this relaxation, we define the probability to stay elongated as
\begin{equation}
P_\text{el}(\Delta t) = \left\langle P\left(\delta_i(t+\Delta t)|\delta_i(t)\right)\right\rangle_{t,i}, 
\end{equation}
where $\delta_i(t)$ is the probability for the triplet $i$ to be elongated at time $t$. The decay of $P_\text{el}(\Delta t)$ has a characteristic time of $27\tau_B$, much longer than the Brownian time.

The shape of clusters of more than 3 particles cannot be followed in the same way. Thus we compute the principal moments of gyrations $\lambda_j$ with $\lambda_1\geq\lambda_2\geq\lambda_3$. Low values of the aspect ratios $\lambda_2/\lambda_1$ and $\lambda_3/\lambda_1$ indicate that the cluster is flat or even linear. In Fig.~\ref{fig:hydro}b, we show the evolution of the average value of these aspect ratios either for a non-percolating sample or before percolation for a percolating one. In both cases, we observe that the clusters are originally not compact and become more isotropic over tens of $\tau_B$. As can be seen in Fig.~\ref{fig:cell_vs_cap}d, structural isotropy is recovered only after the fusion of many anisotropic clusters into a branched structure.

These observations can be rationalised by the invocation of hydrodynamic effects. Indeed in a solvent, particles cannot converge freely to form compact structures~\cite{tanaka1999colloid,tanaka2000simulation,Furukawa2010}. The compaction is delayed by the incompressibility of the solvent, which allows only divergence-free transverse flow fields.  Furthermore, clusters influenced by hydrodynamic interactions tend to be more elongated, less compact. We can test this hypothesis by measuring at which angle particles meet relative to existing neighbours. If influenced by hydrodynamics, particles should avoid the direction of existing neighbours and come from more open angles.

In Fig.~\ref{fig:hydro}c we show the bond angle distribution from three points of view: (i) existing bonds, (ii) bonds that will form within the next $\tau_B$, (iii) bonds that will form within the next $\tau_B$ involving an isolated particle. As expected, existing bonds are preferentially at a 60$^\circ$ angle indicating stable packing, with secondary peaks coherent with a mixture of tetrahedral and hexagonal packings. Future bonds have more acute angles and almost never 180$^\circ$, since they are mostly due to particles attached to second neighbours, see sketch in Fig.~\ref{fig:hydro}c. Here hydrodynamics plays no role. By contrast, future bonds involving isolated particles form at more obtuse angles, with a clear peak around 180$^\circ$. This confirms that hydrodynamics influences particle aggregation and explains why clusters are initially elongated.

Consequently, long-lived elongated clusters have a higher probability to meet via either rotational or translational diffusion than compact spherical clusters. In Supplementary Figure~\ref{fig:effectiveVF} we show that indeed at all colloidal volume fraction percolation takes place when the effective volume fraction $\phi_\text{eff} = \sum\frac{4\pi}{3}R_g^3$ of the clusters reaches random close packing. Hydrodynamics explains why in a rather dilute regime we can observe immediate formation of elongated clusters and then their slow, hydrodynamically-assisted aggregation into a percolated structure.
We stress that this is a direct consequence of large-size disparity, which leads to the physical situation where discrete solid objects are floating in a continuum liquid.

%\subsection*{Network ageing}
In the above, we show that with a help of hydrodynamic interactions, particles first form
a transient gel even at very low volume fractions, and thus only later they increase the number of
nearest neighbours to minimize the energy of the structure. 
Thus, hydrodynamic interactions lead to the formation of gels that are very far from equilibrium and under a strong thermodynamic driving force 
towards more stable compact structures. 
Due to the connectivity of the network, the resulting transition from open to more compact networks can take place only through
the breaking of the bonds that have accumulated more stress. The process was called stress-driven ageing~\cite{Tanaka2007}, 
which is characteristic of viscoelastic phase separation \cite{tanaka2000viscoelastic}. 
As we saw in Fig.~\ref{fig:phasediag}c, the coarsening in these samples is indeed much slower than what is expected from ordinary spinodal decomposition dynamics \cite{onuki2002phase}, 
suggestive of mechanical frustration effects. The phase separation is arrested, but the system is still ageing slowly, a process sometimes leading to delayed sudden collapse of gels~\cite{poon1999delayed,Bartlett2012}, a catastrophic phenomenon from the industrial point of view. Previous numerical studies~\cite{Tanaka2007,colombo2014self,testard2014intermittent} have shown that the main coarsening mechanism is the rupture of strands in the network, a process that to our knowledge has not been followed experimentally at the particle level.
Below we provide the first experimental proof of this process.

Figure~\ref{fig:breaking}a shows a strand rupture reconstructed from confocal 3D images, the colours mapping the intensity of internal stresses acting on each particle. In practice, the attraction potential well is too narrow relative to the particle localisation errors for us to extract directly the force acting on a particle. Therefore, we use the elongation of the particle neighbourhood as a proxy. The more the bonds around a particle are oriented along a single axis, the more tension is exerted on the particle. This local elongation is quantified using bond orientational order~\cite{steinhardt1983boo} for the 2-fold symmetry $q_2$, see Methods for a precise definition. In Fig.~\ref{fig:breaking}a we observe the slow build up of tension over the first 30 min, until the tension is concentrated on a weak part, a one particle thin strand. This strand breaks and the particles involved merge in their respective part of the network that then stay apart from each other. This is the only elementary process allowed for a percolated network to lower the free energy and it is a mechanically driven coarsening process \cite{Tanaka2007}. The driving force is simply attractive interactions between particles favouring compact structures, which can be rephrased by 
interfacial energy in a coarse-grained picture.

To detect strand rupture, we use the topology of the bond network. We can consider the gel as a graph with the particles as nodes and the bonds as edges. This graph evolves from frame to frame separated by $3\tau_B$. In the lower part of Fig.~\ref{fig:breaking}a, we draw in red the shortest on-graph path between two particles of interest. Before the strand rupture, this path is a single bond long. After the rupture, the shortest path is much longer. In general, when two particles were bonded on the previous frame and are no more bonded on the present frame, we define the post-breaking topological distance $\Lambda$ as the new shortest distance on the graph between them, minus 1. If the particles still have a common neighbour then $\Lambda=1$, because two bonds are needed to go from one to the other. $\Lambda=2$ when three bonds are needed, etc.

This path length $\Lambda$ is a good measure of the significance of a bond breaking event. Small values indicate a local rearrangement whereas large values are the signature of important changes in the topology of the network, namely strand rupture. Figure~\ref{fig:breaking}b shows the distribution of $\Lambda$ for three colloidal volume fractions. Excluding the largest values that are dominated by the limited size of the field of view, $\Lambda$ seems to follow a power-law distribution of exponent between $-3$ and $-4$. However the values at $\Lambda=1$ seems in excess. Figure~\ref{fig:breaking}c compares the probability distribution of $q_2$ for all bond breaking events versus for evens with $\Lambda>1$. In both cases bonds about to break have a higher probability of being under tension, but this trend is much clearer when excluding local events. Both observations point to spurious detection of bond breaking events due to localisation errors comparable to the short attraction range and rattling of particles. For this reason, but also to focus on topologically relevant strand rupture, we discard all events with $L \leq 3$ in the following analysis.

In Fig.~\ref{fig:breaking}d we show the time evolution of the probability for a topologically relevant strand rupture $P_\text{break}(\Lambda>3)$, i.e. the ratio of the number of bond breaking events with $\Lambda>3$ by the number of particles. $P_\text{break}$ has its maximum at percolation and then decreases and finally saturates. Strikingly all curves collapse after percolation, indicating common physical ingredients for the ageing of gels at all concentrations.

Initially, clusters are in elongated, unstable configurations. When isolated, a cluster is able to relax to a more compact and stable shape. However in dense samples, elongated clusters meet, before any compaction, into large branched clusters able to transmit stresses. The compaction trend exerts internal stresses on the strands inside those clusters large enough to make them rupture. This effect is maximum when the sample is fully percolated and thus the network is most strongly stretched, and the internal stresses are maximum.

The characteristic size of a spinodal network is \textcolor{blue}{$\xi(t)\sim t^{1/2}$} (see Fig. 2c). Strands being linear objects, their volume is linear in $\xi$ and thus the number of strands in the field of view $N_s$ evolves as \textcolor{blue}{$t^{-1/2}$}. Since after the percolation no new strands are to be created, the variation in the number of strands is given only by the strand rupture rate:
\begin{equation}
\textcolor{blue}{P_\text{break} = -\frac{d N_s}{dt} \sim t^{-3/2}.}
\end{equation}
Indeed in Fig.~\ref{fig:breaking}d we observe that the initial regime of the master curve is well described by a power law of exponent \textcolor{blue}{$-3/2$}. 
\textcolor{blue}{The saturation of $P_{\rm break}$ at late times may be an artefact due to a choice of $\Lambda$ too small for characterising breaking events taking place in the late stage. 
The criterion $\Lambda>3$ is good for the initial stage, but may be too strict for the late stage and detect local rearrangements. 
Thus, $P_{\rm break}$ should actually be negligible in the very late stage and the structure evolution is arrested (see Fig. 2c).} 
At longer times, most of the internal stresses have been released and the system reaches arrested phase separation, where the yield stress emerging due to dynamical arrest 
exceeds the internal mechanical stress. 
For dilute samples, percolation happens later, after the end of the power law regime. Thus, the clusters have already compacted to stable configurations and internal stresses are low.

% \section{Conclusion}
To summarize, we successfully follow the entire process of colloidal gelation at a single particle level and 
show that spinodal gelation is induced by spinodal decomposition, but the process is heavily frustrated  by 
hydrodynamics and mechanics, both of which originates from the dynamical asymmetry due to the large size disparity between 
colloidal particles and solvent molecules. The hydrodynamic effect is the consequence of the fact that solvent molecules 
can be treated as a continuum fluid in the much larger length and time scales of colloids and thus obey the Navier-Stokes equation. 
We can preclude a possibility that the formation of elongated clusters is due to non-ideal flow induced by the mixing, which may be the case for the conventional protocols. 
In a dilute system, local condensation proceeds simultaneously as percolation.
In contrast, dense systems accomplish percolation in the early stage, whereas local condensation proceeds in the late stage; and this rapid percolation leads to high internal stress at the time of percolation. 
In both cases of gelation, percolation is a consequence of condensation frustrated by hydrodynamic interactions, whereas the coarsening process is frustrated by mechanical tensions.
We also find that the fate of a percolated network, more specifically, whether it is permanently stabilised as a gel or eventually breaks up into isolated clusters, 
crucially depends on whether the weak parts of the gel network can support the self-generated mechanical stress or not. 
%In the systems studied the rate of the network breakup events decreases with time, but tends to remain finite even after 10$^3$ $\tau_{B}$, 
%suggesting that network may eventually loose its connectivity. 
Since colloidal suspensions can be regarded as an ideal model system of binary mixtures that consist of small and big components, 
our study will shed new light on not only colloidal gelation but also dynamically asymmetric mixtures, which include polymer solutions, emulsions, and protein solutions. 
We hope that our findings will deepen our microscopic understanding of spinodal gelation concerning the lower bound of gelation and the long-term stability, both of 
which are important in industrial applications.

\vspace{1cm}
\noindent
{\bf METHODS}

\vspace{0.5cm}
\noindent
{\bf Experimental.}

We used \textsc{pmma} (poly(methyl methacrylate)) colloids sterically stabilized with methacryloxypropyl terminated \textsc{pdms}(poly(dimethyl siloxane)) and fluorescently labelled with rhodamine isothiocyanate chemically bonded to the \textsc{pmma}. Colloids are dispersed in a mixture of cis-decalin (Tokyo Kasei) and bromocyclohexane (Sigma-Aldrich) that matches both optical index and density of the colloids.

To induce short-ranged depletion attraction, we use polystyrene (TOSOH) of molecular weight 8.4$\times 10^6$ as non-adsorbing polymer. The radius of gyration in theta solvent is estimated to 110 nm. Here the solvent may be regarded as ``good'' and a Flory scaling of the measurements of~\cite{lu2008gelation} yields $R_g=148$ nm. In the absence of salt, the Debye length is expected to reach several $\mu$m and the (weakly) charged colloids experience a long range electrostatic repulsion~\cite{Royall2003}. We confirm that colloids never come close enough to feel the short-ranged attraction and form a Wigner crystal.

The colloids and polymers are contained in an observation cell ($1$ mm$^2$ $\times$ 200 $\mu$m) made of glass in contact with an half-open glass channel approximately 400 times larger in volume, via a millipore filter with pore size of 100 nm that allows the salt through but neither polymer nor colloid (see Fig.~\ref{fig:cell_vs_cap}a). The channel is filled with the same solvents at density matching composition. At the beginning of the experiment, solid tetrabutylammonium bromide (Fluka) is introduced to the channel which is immediately sealed to prevent evaporation. Data acquisition starts within 30 s after salt introduction. Our procedure induces practically no solvent flow in the observation cell. We confirmed the presence of undissolved salt several days after mixing, indicating that the observation cell was brought to saturation concentration.

Given the diffusion constants of Bromide and alkyl cation ($6$ and $2 \times 10^{-10}$ m$^2$/s~\cite{Campbell2005}), we estimate the characteristic diffusion time of salt from top to bottom of the order of 10 s. Therefore, we reach uniform final salt concentration into the observation cell within only a few Brownian times of the colloids. Indeed we measured a delay of about 1 min between the aggregation at the bottom and at the top of the cell. We define the initial time of the aggregation process when the maximum of the $g(r)$ jumps from the lattice constant of the Wigner crystal to the hard-core diameter $\sigma$.

We collect the data on a Leica SP5 confocal microscope, using 532 nm laser excitation. The temperature was controlled on both stage and objective lens, allowing a more precise density matching. The scanned volume is at least $82 \times 82 \times 85$ $\mu$m$^3$. The particle coordinates are tracked in three dimensions (3D) with an accuracy of around $0.03\sigma$~\cite{LeocmachColloids}.

\vspace{0.5cm}
\noindent
{\bf Analysis.}

From direct confocal measurements~\cite{Royall2007, Poon2012}, we estimate the hard-core diameter of our colloids ($\sigma=2.75$ $\mu$m) and the range of the interaction potential (that confirmed our scaling of $R_g$ within $1\%$), leading to a polymer-colloid size ratio $q = 2R_g/\sigma = 0.10(6)$. Spinodal line on Fig.~\ref{fig:phasediag}b are calculated from this size ratio using the generalized free volume theory~\cite{Fleer2008}.

In principle the attraction well of the depletion extends to $\sigma+2R_g$, however, resolution-dependent tracking imprecisions and systematic errors do not give a precise enough estimate of such short distance. Therefore we consider two particles bonded when their distance is shorter the first minimum of $g(r)$, i.e. 3.55 $\mu$m. This defines the bond graph that we analyse using connected components and shortest path analysis algorithms~\cite{Hagberg2008}.

To detect local 2-fold symmetry and thus elongation, we use \citet{steinhardt1983boo} bond orientational order for the particle $i$,
\begin{align}
	q_2(i) =& \sqrt{\frac{4\pi}{5} \sum_{m=-2}^{2} |q_{2,m}(i)|^2 }, \label{eq:ql}\\
	q_{2,m}(i) =& \frac{1}{N_i}\sum_{j=1}^{N_i} Y_{2,m}(\theta(\mathbf{r}_{ij}),\phi(\mathbf{r}_{ij})),
	\label{eq:qlm}
\end{align}
where the $Y_{\ell, m}$ are spherical harmonics and $\mathbf{r}_{ij}$ is one of the $N_i$ bonds involving particle $i$.

\bibliographystyle{naturemag3}
\bibliography{ico_dyn}

\vspace{1cm}
%\item[Supplementary Information] is linked to the online version of the paper at www.nature.com/nature.
\noindent
{\bf Acknowledgements.} This study was partly supported by Grants-in-Aid for Scientific Research (S) (Grand No. 21224011) and Specially Promoted Research (Grand No. 25000002) from 
the Japan Society for the Promotion of Science (JSPS).

%\vspace{0.3cm}
\noindent
{\bf Author Contributions.} H.Ts. and M.L. contributed equally to this work. 
H.Ta. conceived and supervised the project, H. Ts. performed experiments, M.L. analysed the data, and all authors discussed and wrote the manuscript.

%\vspace{0.3cm}
\noindent
{\bf Author Information} Reprints and permissions information is available at www.nature.com/reprints.
Correspondence and requests for materials should be addressed to H.T. ~(tanaka@iis.u-tokyo.ac.jp).

\clearpage
\begin{figure*}
	\includegraphics[width=16cm]{figure1.pdf}
	\caption{\textbf{Reservoir cell.} \textbf{a,} Sketch of our experimental setup. The observation cell contains initially colloids, polymer and no salt. \textbf{b,} Confocal slice of a gel formed \textit{in situ} by our method ($\phi=25.5~\%$, $c_p=1.4$ g/$\ell$), 1 hour after gelation. \textbf{c,} Idem for a gel at the same state point formed \textit{ex situ} and immediately pumped into a capillary. \textbf{d,} Gelation observed by our method. Experimental coordinates are reconstructed and coloured by the number of particles in clusters in a typical sample close to the cluster-gel line ($\phi=7.5~\%$, $c_p=1$ g/$\ell$). Origin of time is the last frame before melting of Wigner crystal.
	%Phase diagram obtained in reservoir cell. Spinodal line is obtained from free volume theory. State points analysed in the text are circled. The state point of \textbf{b-c} is highlighted by a square.
	}
	\label{fig:cell_vs_cap}
\end{figure*}

\clearpage 
\begin{figure}
\includegraphics[width=10cm]{figure2.pdf}
\caption{\textbf{Different regimes of gelation.} \textbf{a,} Phase diagram. Experimental points are categorised based on the final state obtained in reservoir cell. The spinodal line is obtained from free volume theory. State points analysed in the text are circled. The state point of Fig.~\ref{fig:cell_vs_cap}b-c is highlighted by a square. \textbf{b,} Comparison of system evolution in terms of largest cluster extent and of mean coordination number. By increasing density: $\phi=4.2,\,8,\,16,\,27~\%$, $c_p=1,\,1.5,\,1.2,\, 1$ g/$\ell$ for 
%\textcolor{red!40!yellow}
{$\blacklozenge$}, 
%\textcolor{red!80!yellow}
{$\circ$}, 
%\textcolor{red!80!black}
{\tiny$\blacksquare$} and 
%\textcolor{red!40!black}
{$\bullet$} respectively. \textbf{c,} Growth of the characteristic wave number for the same samples.}
\label{fig:phasediag}
\end{figure}

\clearpage
\begin{figure}
	\includegraphics[width=10cm]{figure3.pdf}
	\caption{\textbf{Hydrodynamics} \textbf{a,} Probability of staying elongated for a triplet in a non-percolating sample ($\phi=4~\%$, $c_p=1$ g/$\ell$). The continuous line is the best exponential fit of characteristic time $27\tau_B$. Inset: probability distribution of radii of gyration of triplets. \textbf{b,} Evolution of the aspect ratios of clusters of 4 particles and more in the same sample (dashed lines) and in a percolating sample ($\phi=8~\%$, $c_p=1.5$ g/$\ell$, continuous lines). \textbf{c,} Bond angle distribution relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue) obtained in the percolating sample. Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles. Insets sketch both cases, with present bonds drawn thick and future bonds drawn dotted.}
	\label{fig:hydro}
\end{figure}

\clearpage
\begin{figure*}
\includegraphics[width=16cm]{figure4.pdf}
\caption{\textbf{Mechanical tension drives coarsening} 
\textbf{a,} Reconstruction from experimental coordinates ($\phi=29~\%$, $c_p=0.7$ g/$\ell$) of coarsening process geometry (top) and topology (bottom). Particles are drawn to scale and coloured by $q_2$ from blue (low) to red (high). The meshed surface is a Gaussian coarse-graining of the network pattern. The red line indicates the shortest on-graph path between the two particles of interest. 
\textbf{b,} Number of bond breaking function of the future on-graph distance $\Lambda$ (after percolation) for the three percolating state points of Fig. 2a (same colours and markers).
%three state points of increasing density: $\phi=8,\,16,\,27~\%$, $c_p=1.5,\,1.2,\,1$g/$\ell$ for \textcolor{red!80!yellow}{$\circ$}, \textcolor{red!80!black}{\tiny$\blacksquare$} and \textcolor{red!40!black}{$\bullet$} respectively.
\textbf{c,} Probability for a bond to break during $3\tau_B$ function of bond-centred $q_2$ for all events (blue) and for events with $\Lambda>1$ (thick red) in the same sample as \textbf{a}.
\textbf{d,} Evolution of the topologically relevant bond breaking probability ($\Lambda>3$) for the same state points as in b. Vertical lines indicate the respective percolation times.
}
\label{fig:breaking}
\end{figure*}

\end{document}

### 2015-10-19 manuscript4.tex
Minor English fixes gravitational Peclet number

--- 2015-10-19 gel_cond/trunk/manuscript4.tex
@@
 The mechanism of spinodal gelation has particularly been studied for colloidal suspensions since they can be regarded as a model system for other systems.
-Thanks to the extensive study in past, we now have a reasonable physical picture: Gelation is induced by spinodal decomposition to two phases whose dynamics are very different \cite{tanaka1999colloid,tanaka2000viscoelastic} and the resulting vitrification of the slower phase \cite{piazza1994phase,verhaegh1997,tanaka1999colloid,poon2002,lu2008gelation}.
+Thanks to extensive studies in the past, we now have a reasonable physical picture: Gelation is induced by spinodal decomposition into two phases whose dynamics are very different \cite{tanaka1999colloid,tanaka2000viscoelastic} and the resulting vitrification of the slower phase \cite{piazza1994phase,verhaegh1997,tanaka1999colloid,poon2002,lu2008gelation}.
 However, the knowledge of ordinary spinodal decomposition cannot explain the observed behaviour since it predicts that the minority colloid-rich phase should form isolated clusters rather than a percolated network.
@@
 To access roles of hydrodynamics in the initial stage of gelation, we develop a new protocol to initiate phase separation without causing any harmful flow. 
-To access roles of mechanics in the late stage, we realize the density matching of the order of 10$^{-4}$ and use a very accurate particle tracking method \cite{leocmach2013novel}. 
+To access roles of mechanics in the late stage, we realize a density matching of the order of 10$^{-4}$ (gravitational Peclet number $Pe< 10^{-7}$) and use a very accurate particle tracking method \cite{leocmach2013novel}.
 %In previous studies, the process of gelation has been studied experimentally by following the structural evolution.
@@
 but the origin of arrest is different between clusters and percolated networks.
-For clusters, density fluctuations grow rather rapidly in the initial stage, but after the formation of isolated clusters it takes a long time since the diffusive evaporation-condensation mechanism does not work for colloidal viscoelastic phase separation and direct cluster collisions and coalescence are necessary for coarsening \cite{tanaka2000viscoelastic}.
+For clusters, density fluctuations grow rather rapidly in the initial stage, but after the formation of isolated clusters their growth takes a long time since the diffusive evaporation-condensation mechanism does not work for colloidal viscoelastic phase separation and direct cluster collisions and coalescence are necessary for coarsening \cite{tanaka2000viscoelastic}.
 For networks, densification due to phase separation leads to dynamic arrest due to vitrification \cite{piazza1994phase,verhaegh1997,tanaka1999colloid,poon2002,zaccarelli2007,lu2008gelation} or formation of locally stable structures \cite{royall2008g}.
@@
 \begin{figure*}
-	\includegraphics[width=16cm]{figure1.pdf}
+	%\includegraphics[width=16cm]{figure1.pdf}
+	\includegraphics{figs/cell_vs_cap2.pdf}
 	\caption{\textbf{Reservoir cell.} \textbf{a,} Sketch of our experimental setup.
@@
 \begin{figure}
-\includegraphics[width=10cm]{figure2.pdf}
+%\includegraphics[width=10cm]{figure2.pdf}
+\includegraphics{figs/phasediag.pdf}
 \caption{\textbf{Different regimes of gelation.} \textbf{a,} Phase diagram.
@@
 \begin{figure}
-	\includegraphics[width=10cm]{figure3.pdf}
+	%\includegraphics[width=10cm]{figure3.pdf}
+	\includegraphics{figs/hydro.pdf}
 	\caption{\textbf{Hydrodynamics} \textbf{a,} Probability of staying elongated for a triplet in a non-percolating sample ($\phi=4~\%$, $c_p=1$ g/$\ell$).
@@
 \begin{figure*}
-\includegraphics[width=16cm]{figure4.pdf}
+%\includegraphics[width=16cm]{figure4.pdf}
+\includegraphics{figs/breaking.pdf}
 \caption{\textbf{Mechanical tension drives coarsening} 

### 2015-10-19 gel_cond/trunk/manuscript4.tex
Forgot g in the estimate of the Peclet number

@@
 To access roles of hydrodynamics in the initial stage of gelation, we develop a new protocol to initiate phase separation without causing any harmful flow. 
-To access roles of mechanics in the late stage, we realize the density matching of the order of 10$^{-4}$ and use a very accurate particle tracking method \cite{leocmach2013novel}. 
+To access roles of mechanics in the late stage, we realize a density matching of the order of 10$^{-4}$ (gravitational Peclet number $Pe< 10^{-6}$) and use a very accurate particle tracking method \cite{leocmach2013novel}.
 %In previous studies, the process of gelation has been studied experimentally by following the structural evolution.

### 2015-10-21 manuscript4.tex
no sealing of the end of the channel 10 mm2 x 200 um for the cell

@@
 To access roles of hydrodynamics in the initial stage of gelation, we develop a new protocol to initiate phase separation without causing any harmful flow. 
-To access roles of mechanics in the late stage, we realize a density matching of the order of 10$^{-4}$ (gravitational Peclet number $Pe< 10^{-7}$) and use a very accurate particle tracking method \cite{leocmach2013novel}.
+To access roles of mechanics in the late stage, we realize a density matching of the order of 10$^{-4}$ (gravitational Peclet number $Pe< 10^{-6}$) and use a very accurate particle tracking method \cite{leocmach2013novel}.
 %In previous studies, the process of gelation has been studied experimentally by following the structural evolution.
@@
 The bottom wall of the cell is an osmotic membrane providing contact with a long channel full of the same solvent mixture.
-We introduce solid salt at the other end of the channel that we seal immediately.
+We introduce solid salt at the other end of the channel.
 Salt dissolution and subsequent migration of the ions along the channel and through the membrane induce screening of the electrostatic repulsion, well revealing the depletion potential due to the pre-existing polymers.
@@
 
-\vspace{1cm}
-\noindent
-{\bf METHODS}
+\section*{METHODS}
 
-\vspace{0.5cm}
-\noindent
-{\bf Experimental.}
+\subsection*{Experimental.}
 
@@
 
-The colloids and polymers are contained in an observation cell ($1$ mm$^2$ $\times$ 200 $\mu$m) made of glass in contact with an half-open glass channel approximately 400 times larger in volume, via a millipore filter with pore size of 100 nm that allows the salt through but neither polymer nor colloid (see Fig.~\ref{fig:cell_vs_cap}a).
+The colloids and polymers are contained in an observation cell ($10$ mm$^2$ $\times$ 200 $\mu$m) made of glass in contact with an half-open glass channel approximately 400 times larger in volume, via a millipore filter with pore size of 100 nm that allows the salt through but neither polymer nor colloid (see Fig.~\ref{fig:cell_vs_cap}a).
 The channel is filled with the same solvents at density matching composition.
-At the beginning of the experiment, solid tetrabutylammonium bromide (Fluka) is introduced to the channel which is immediately sealed to prevent evaporation.
+At the beginning of the experiment, solid tetrabutylammonium bromide (Fluka) is introduced to the channel.
 Data acquisition starts within 30 s after salt introduction.
@@
 
-Given the diffusion constants of Bromide and alkyl cation ($6$ and $2 \times 10^{-10}$ m$^2$/s~\cite{Campbell2005}), we estimate the characteristic diffusion time of salt from top to bottom of the order of 10 s.
+Given the diffusion constants of Bromide and alkyl cation ($6$ and $2 \times 10^{-10}$~m$^2$/s~\cite{Campbell2005}), we estimate the characteristic diffusion time of salt from top to bottom of the order of 10~s.
 Therefore, we reach uniform final salt concentration into the observation cell within only a few Brownian times of the colloids.
@@
 The temperature was controlled on both stage and objective lens, allowing a more precise density matching.
-The scanned volume is at least $82 \times 82 \times 85$ $\mu$m$^3$.
+The scanned volume is at least $82 \times 82 \times 85$~$\mu$m$^3$.
 The particle coordinates are tracked in three dimensions (3D) with an accuracy of around $0.03\sigma$~\cite{LeocmachColloids}.
 
-\vspace{0.5cm}
-\noindent
-{\bf Analysis.}
+\subsection*{Analysis.}
 
-From direct confocal measurements~\cite{Royall2007, Poon2012}, we estimate the hard-core diameter of our colloids ($\sigma=2.75$ $\mu$m) and the range of the interaction potential (that confirmed our scaling of $R_g$ within $1\%$), leading to a polymer-colloid size ratio $q = 2R_g/\sigma = 0.10(6)$.
+From direct confocal measurements~\cite{Royall2007, Poon2012}, we estimate the hard-core diameter of our colloids ($\sigma=2.75$~$\mu$m) and the range of the interaction potential (that confirmed our scaling of $R_g$ within $1\%$), leading to a polymer-colloid size ratio $q = 2R_g/\sigma = 0.10(6)$.
 Spinodal line on Fig.~\ref{fig:phasediag}b are calculated from this size ratio using the generalized free volume theory~\cite{Fleer2008}.
@@
 Therefore we consider two particles bonded when their distance is shorter the first minimum of $g(r)$, i.e.
-3.55 $\mu$m.
+3.55~$\mu$m.
 This defines the bond graph that we analyse using connected components and shortest path analysis algorithms~\cite{Hagberg2008}.
@@
 %\textcolor{red!40!black}
-{$\bullet$} respectively. \textbf{c,} Growth of the characteristic wave number for the same samples.}
+{$\bullet$} respectively. \textbf{c,} Growth of the characteristic wave number for the same samples. 
+The line is a scaling law for the intermediate coarsening regime for network-forming phase separation.}
 \label{fig:phasediag}

### 2015-11-02 manuscript4.tex

@@
 This is the key for viscoelastic phase separation \cite{tanaka1999colloid,tanaka2000viscoelastic}.
-There have been some numerical studies on the role of hydrodynamics~\cite{tanaka2000simulation,Furukawa2010} and mechanics~\cite{Tanaka2007,colombo2014self,testard2014intermittent} in colloidal gelation, however, there has so far been no experimental study that directly addresses these effects by dynamical observation of the process.
+There have been some numerical studies on the role of hydrodynamics~\cite{tanaka2000simulation,Furukawa2010} and mechanics~\cite{cipelletti2000universal,Tanaka2007,colombo2014self,testard2014intermittent} in colloidal gelation, however, there has so far been no experimental study that directly addresses these effects by dynamical observation of the process.
 

### 2015-11-10 gel_cond/trunk/phasediag.py
Dilute regime only

@@ -1,81 +1,123 @@
 from matplotlib.pyplot import *
 from colloids.phase import *
 from os.path import isfile
+from scipy.constants import N_A
 
-qR = 0.1
+#radius of gyration in nm
+R = 155.#122.
+#Molecular weight (Dalton or g/mol)
+Mw = 8.4e6
+#colloid diameter in nm
+sigma = 2800.
+#density of the solvent in g/mL
+d = 1.24
+
+qR = 2*R/sigma
+cpov = 1000 * (3 * Mw)/(4 * np.pi * (R*1e-9)**3 * N_A * d*1e6)
 q = qR2q(qR)
+print 'qR = %0.3f, q = %0.3f, Cov = %0.3f mg/g'%(qR, q, cpov)
 
-fig = figure('experimental phase diagram')
-clf()
-for phase, color in [('gel', 'r'), ('fluid', 'b'), ('transient', 'g'), ('clusters', 'y')]:
-    phi, cp = np.loadtxt('phase_diag_%s.csv'%phase, unpack=True, skiprows=1, usecols=[1,2])
-    sample = np.loadtxt('phase_diag_%s.csv'%phase, usecols=[0], skiprows=1, dtype='str')
-    scatter(phi, cp, c=color, label=phase)
-    for s, p, c in zip(np.atleast_1d(sample), np.atleast_1d(phi), np.atleast_1d(cp)):
-        gca().annotate(s, (p,c))
+#osmotic work at overlap
+pivmax = y2piv(1.0, qR)
 
 #load or compute theoretical phase diagram
+fc, pivc = Liu().critical_point(q)
+print 'At critical point colloid volume fraction is %0.3f and osmotic insertion work is %0.3f kT'%(f2vf(fc), pivc)
 if isfile('phasediag.txt'):
     GL = np.loadtxt('phasediag.txt')
 else:
-    GL = Liu().all_GL(q, maxpiv=3500)
+    GL = Liu().all_GL(q, maxpiv=pivmax)
     np.savetxt('phasediag.txt', GL)
-#draw binodal and spinodals
-for f,l in zip(GL.T[1:], ['--']*2+['-']*2):
-    cp = piv2y(GL[:,0], q) * alpha(f, qR)
-    plot(100*f2vf(f), cp, 'k'+l)
+if isfile('phasediagFS.txt'):
[…]

### 2015-11-10 figs/makevideo.sh
script to make videos out of files.pov. Calls povray and ffmpeg

@@ -1,0 +1,20 @@
+#!/bin/bash
+
+[ $# -eq 0 ] && { echo "Usage: $0 size" ; exit 1; }
+
+mkdir $1
+
+#run povray on percolation sequence
+for i in $(seq 8 120); do 
+    povray +O$1/$(printf "155C_p2size_t%03d.png" $i) +W$1 +H$1 -D $(printf "155C_percolation_1645_p2size_t%03d.pov" $i); 
+done
+
+#run povray on ageing sequence, so that numbers follow percolation sequence
+for i in $(seq 0 20); do 
+    povray +O$1/$(printf "155C_p2size_t%03d.png" $(($i+121))) +W$1 +H$1 -D $(printf "155C_1715_ageing_p2size_t%02d.pov" $i); 
+done
+
+#run ffmpeg to make the video
+cd $1
+ffmpeg -framerate 24 -pattern_type glob -i "155C_*.png" -vframes 130 -vcodec libx264 -preset veryslow -crf 24 -threads 0 output$1.mp4
+cd ..

### 2015-11-11 gel_cond/trunk/manuscript4.tex

@@
-\documentclass[preprint,footinbib,amsmath,amssymb]{revtex4}
+\documentclass[preprint,footinbib,amsmath,amssymb,superscriptaddress]{revtex4}
 \usepackage{graphicx,amsmath}
@@
 \author{Hideyo Tsurusawa}
+\affiliation{ {Institute of Industrial Science, University of Tokyo, 4-6-1 Komaba, Meguro-ku, Tokyo 153-8505, Japan} }
 %\thanks{These authors contributed equally to this work}
 \author{Mathieu Leocmach}
+\affiliation{Institut Lumière Matière, CNRS UMR 5306, Université Claude Bernard Lyon 1, Université de Lyon, Lyon, 69622 Villeurbanne Cedex, France}
 %\thanks{These authors contributed equally to this work}

### 2016-10-01 gel_cond/trunk/manuscript4.tex
Affiliation iLM depletion usual for colloids used in quantitative confocal

@@
 \author{Mathieu Leocmach}
-\affiliation{Institut Lumière Matière, CNRS UMR 5306, Université Claude Bernard Lyon 1, Université de Lyon, Lyon, 69622 Villeurbanne Cedex, France}
+\affiliation{Univ Lyon, Université Claude Bernard Lyon 1, CNRS, Institut Lumière Matière, F-69622, VILLEURBANNE, France}
 %\thanks{These authors contributed equally to this work}
@@
 Thus, confocal microscopy observation is necessary. However, it has been very difficult to study the very early and late stage of gelation by this method. 
-Gelation of micron-size colloids is usually induced by depletion attractions due to polymers in the solvent. 
+Gelation of micron-size colloids suitable for quantitative confocal microscopy is usually induced by depletion attractions due to polymers in the solvent. 
 %Polymers used for this purpose usually have high molecular weights because colloids have to be large enough for realizing particle-level resolution, which results in a high viscosity of the polymer solution.
@@
 We introduce solid salt at the other end of the channel.
-Salt dissolution and subsequent migration of the ions along the channel and through the membrane induce screening of the electrostatic repulsion, well revealing the depletion potential due to the pre-existing polymers.
+Salt dissolution and subsequent migration of the ions along the channel and through the membrane induce screening of the electrostatic repulsion, revealing the depletion potential well due to the pre-existing polymers.
 The time needed for the ions to diffuse from the membrane across the cell thickness is of the same order of magnitude as the Brownian time of the particles $\tau_B=10$ s.

### 2016-10-01 gel_cond/trunk/manuscript4.tex
Initiate supplementary materials with fig:structure_factor tweak space taken vertically by the figure

@@
 To confront this hypothesis, we compute the time dependent static structure factor $S(q,t)$.
-For all gel and cluster samples, we observe the appearance of a low $q$ peak in $S(q)$, see Supplementary Figure XXX, which is characteristic of spinodal decomposition in a system of a conserved order parameter.
+For all gel and cluster samples, we observe the appearance of a low $q$ peak in $S(q)$, see Supplementary Figure~1, which is characteristic of spinodal decomposition in a system of a conserved order parameter.
 To track the position of this peak, we compute the characteristic wave number $\langle q \rangle$ and show its temporal evolution in Fig.~\ref{fig:phasediag}c.

### 2016-10-01 gel_cond/trunk/supplementary.tex
Initiate supplementary materials with fig:structure_factor tweak space taken vertically by the figure

--- 2016-10-01 gel_cond/trunk/manuscript4.tex
@@
-\documentclass[preprint,footinbib,amsmath,amssymb,superscriptaddress]{revtex4}
+\documentclass[footinbib,amsmath,amssymb,%
+superscriptaddress,twocolumn]{revtex4}
 \usepackage{graphicx,amsmath}
 \usepackage{color}
+\usepackage{siunitx}
 \begin{document}
-\draft
 
-\title{Gelation as condensation frustrated by hydrodynamics and mechanical tension}
+\title{Supplementary Informations to:\\Gelation as condensation frustrated by hydrodynamics and mechanical tension}
 \author{Hideyo Tsurusawa}
@@
 
-\begin{abstract}
-{\bf A colloidal gel is an important non-ergodic state of matter, which can have elasticity and fluidity at the same time.
-Colloidal gels are known to be formed by phase separation accompanying dynamical arrest of a colloid-rich phase due to glass transition \cite{piazza1994phase,verhaegh1997,tanaka1999colloid,poon2002,lu2008gelation}.
-The presence of a liquid component should play crucial roles in the formation of a network structure and its time evolution, since it gives a constraint from the conservation of fluid momentum, which is known to affect the kinetic pathway of non-equilibrium phenomena \cite{tanaka2000viscoelastic}.
-However, there has so far been no experimental study on this important problem.
-Using a novel experimental protocol initiating phase separation, we successfully follow by confocal microscopy observation the entire process of gelation from the very beginning with a single-particle resolution
-and reveal the roles of hydrodynamics and mechanics in gelation, for the first time. 
-%We switch off long-range Coulomb interactions between charged colloids by injecting salt at $t=0$ through an osmotic membrane and make depletion attractions due to polymers operative.
-This initiates phase demixing without inducing disturbing flow, which is inevitable for a conventional method, i.e., simple mixing of colloids and polymers at $t=0$.
-We show that hydrodynamic interactions between colloids mediated by a liquid component are the key to formation of a percolated network structure in  
-a dilute system.
-Furthermore, the network formed by this mechanism is inevitably in a high energy state and under self-generated mechanical tension due to its connectivity.
-We find clear experimental evidence that network coarsening proceeds by sequentially repeating stress-driven mechanical fracture of a network strand.
-A stable gel is then formed when the network breaking rate becomes negligible.
-%Thus, we succeeded in clarifying the roles of momentum conservation, more specifically hydrodynamics and mechanics, in gelation, which has not been accessed experimentally. 
-These findings provide an experimental basis for understanding the microscopic physical mechanism of gelation and its structural formation, whose kinetic pathway is selected not by a thermodynamics factor but by mechanical factors.}
-\end{abstract}
-
 \maketitle
 
-%\section*{Introduction} 
-Gels do not flow and behave as soft solids in a macroscopic scale, but have excellent fluid-like transport characteristics in a microscopic scale, 
-which often provides essential functions of many biological gels including those in our body.  
-For any gels, elasticity comes from the presence of a space-spanning percolated network that can transmit mechanical stress.
-However, the network can be formed by different mechanisms: chemical reaction and physical processes such as phase separation. 
-Gels spontaneously formed by phase separation are an important class of gels, which can be seen commonly in various soft matter \cite{tanaka2013phase} such as colloidal suspensions, emulsions, protein solutions, surfactant solutions, and polymer solutions, and now widely known as ``spinodal gels''.
-This type of gels are not only of fundamental importance in physical, materials, and biological science, but also of technological importance in food, cosmetics, and medical industries.
-
-The mechanism of spinodal gelation has particularly been studied for colloidal suspensions since they can be regarded as a model system for other systems.
-Thanks to extensive studies in the past, we now have a reasonable physical picture: Gelation is induced by spinodal decomposition into two phases whose dynamics are very different \cite{tanaka1999colloid,tanaka2000viscoelastic} and the resulting vitrification of the slower phase \cite{piazza1994phase,verhaegh1997,tanaka1999colloid,poon2002,lu2008gelation}.
-However, the knowledge of ordinary spinodal decomposition cannot explain the observed behaviour since it predicts that the minority colloid-rich phase should form isolated clusters rather than a percolated network.
-This mystery was solved by using an analogy of phase separation of colloidal suspensions to that of polymer solutions on the basis of the concept of dynamic asymmetry \cite{tanaka1999colloid}.
-What is common in these two systems is that a mixture is composed of large slow components (colloid or polymer) and small fast components (solvent). 
-On a macroscopic level, such dynamically asymmetric mixtures are known to show universal pattern formation, known as ``viscoelastic phase separation'' \cite{tanaka2000viscoelastic}. 
-On a microscopic level, however, there are essential differences between colloidal suspensions and polymer solutions coming from the topological difference (sphere vs. chain), leading to 
-distinct rheological behaviours. Thus there are many open questions about the elementary process of phase separation of colloidal suspensions and the resulting colloidal gelation.   
-From the physical viewpoint, the presence of a fluid component indicates the importance of fluid momentum conservation in phase separation, which makes hydrodynamics and mechanics active in structural evolution.
-This is the key for viscoelastic phase separation \cite{tanaka1999colloid,tanaka2000viscoelastic}.
-There have been some numerical studies on the role of hydrodynamics~\cite{tanaka2000simulation,Furukawa2010} and mechanics~\cite{cipelletti2000universal,Tanaka2007,colombo2014self,testard2014intermittent} in colloidal gelation, however, there has so far been no experimental study that directly addresses these effects by dynamical observation of the process.
-
-%However, there have remained many open questions: (1) Spinodal decomposition usually form compact clusters (or, droplet) at low volume fractions where colloidal gels are formed, but actually it produces a space-spanning percolated network.
-According to the common knowledge of ordinary phase separation, bicontinuous network can be formed only when the volume fraction is near 50 \%.
-(2) Even after forming a percolated network, i.e.
-a gel, structural evolution often slowly continues to proceed.
-This kind of ageing behaviour is quite important for a long-time stability of a gel state and a crucial problem in industries.
-(3) It is intuitively appealing that vitrification leads to dynamical arrest of spinodal decomposition and freezes the network structure of gels.
-But vitrification, or glass transition, is originally defined for bulk materials.
-On noting that the strands of a gel network are often very thin, and thus it is hardly clear whether we can apply the concept of glass transition as it is to describe dynamic arrest in gelation.
-
-To access these fundamental problems experimentally, we need to study the entire process of gelation from the beginning to the end at the single-particle resolution. 
-Thus, confocal microscopy observation is necessary. However, it has been very difficult to study the very early and late stage of gelation by this method. 
-Gelation of micron-size colloids suitable for quantitative confocal microscopy is usually induced by depletion attractions due to polymers in the solvent. 
-%Polymers used for this purpose usually have high molecular weights because colloids have to be large enough for realizing particle-level resolution, which results in a high viscosity of the polymer solution.
-Ideally we want to switch on attractive interactions at $t=0$.
-But a high viscosity of a polymer solution prevents its rapid mixing with a colloidal suspension at $t=0$.
-The experimental protocols used so far for studying the kinetics of phase separation and gelation are as follows: (1) Colloidal suspensions and polymer solutions are mixed just before an experiment and after mixing transferred to a capillary tube as quick as possible.
-(2) A mixture, which is already in a final state point in the phase diagram and intrinsically unstable, or phase-separated, is vigorously mixed just before an experiment to break pre-existing phase separated structures by shear melting.
-However, these protocols have two common serious deficiencies: Firstly the initial state can never been homogeneous perfectly and there already exist particle aggregates at $t=0$.
-Secondly, the mixing inevitably involves
-turbulent flow, which does not decay but remain when the observation is initiated. 
-Because of these intrinsic problems of the conventional protocols, it has been almost impossible to access the very initial stage of gelation without interference of pre-existing aggregates and/or turbulent flow.
-Strictly speaking, the gelation process observed by these conventional protocols inevitablly suffers from the influence of ill-defined initial static and dynamic conditions. 
-%On the other hand, to access the late stage, we need to achieve a very accurate density matching to prevent gravitational effects and also a very accurate determination of coordinates of particles.  
-%Now we review what has so far been known for the above open questions.
-On question (1), some time ago we proposed an explanation on the basis of the concept of viscoelastic phase separation.
-When the two components of a mixture have large size disparity and the resulting strong dynamic asymmetry, even the minority phase can form a percolated network structure.
-This is supported by numerical simulations using the viscoelastic model on the basis of an empirical constitutive relation \cite{tanaka2000viscoelastic}, however, how we can explain this at a microscopic level.
-We stress that there is no well-defined constitutive (stress-strain) relation for colloidal suspensions \cite{tanaka1999colloid}.
-We have studied numerically colloidal gelation by incorporating many-body hydrodynamic equation \cite{Furukawa2010} and showed the incompressibility of a fluid component prevents the formation of compact clusters but assists the formation of elongated clusters.
-However, there has been no experimental observation of the dynamical process of particle aggregation that shows a clear signature of the important roles of hydrodynamic interactions, although there is a work studying the characteristics of instantaneous cluster structures.
-However, we cannot deny a possibility that elongated clusters are formed not due to many-body hydrodynamic interactions, but rather by the above-mentioned turbulent flow induced by the conventional protocol.
-To reveal hydrodynamic effects in a convincing manner, thus, we need to study the dynamical process of particle clustering without any interference of perturbative flow.
-On question (2), we have some numerical evidence for the important role of mechanical stress in network coarsening ~\cite{Tanaka2007,colombo2014self,testard2014intermittent}, but there has so far been no experimental evidence to our knowledge.
-On question (3), we need to clarify the relation between mechanical stress and yield stress.
-In this Letter, we study roles of hydrodynamics and mechanics in colloidal gelation experimentally by dynamical confocal microscopy observation of the entire gelation process from the beginning to the end with particle-level resolution.
-To access roles of hydrodynamics in the initial stage of gelation, we develop a new protocol to initiate phase separation without causing any harmful flow. 
-To access roles of mechanics in the late stage, we realize a density matching of the order of 10$^{-4}$ (gravitational Peclet number $Pe< 10^{-6}$) and use a very accurate particle tracking method \cite{leocmach2013novel}.
-%In previous studies, the process of gelation has been studied experimentally by following the structural evolution.
-However, the roles of hydrodynamic interactions and mechanical stresses have never been addressed experimentally.
-These allow us to experimentally reveal (i) the importance of hydrodynamic interactions in forming and stabilizing elongated clusters and their percolation and (ii) the crucial role of mechanical stress
-in ageing of gels and a microscopic mechanism of the network breakup events. These findings will provide crucial information on the mechanisms of gel formation and coarsening and also 
-on the fate of gels.
-
-%\section*{Results}
-
-%\subsection*{System design}
-
-We designed an experimental set-up that allows the observation of the entire process of gelation at a single particle level.
-For that, we use a colloidal system that is charge stabilised at long range, has a short range depletion attraction, and is also sterically stabilised causing nearly hard sphere repulsion at contact.
-We disperse colloidal particles and non-adsorbing polymers in a  mixture of organic solvents that matches both the refractive index and the density of the particles.
-Because of the weakly polar nature of the solvent mixture (its dielectric constant $\epsilon_r = 5\sim6$), the Debye screening length is about $\kappa^{-1}=10$ $\mu$m, long enough for the large colloids (diameter $\sigma=2.75$ $\mu$m) to form a homogeneous Wigner crystal in the mixture~\cite{klix2010structural}, since the short ranged ($\sim \sigma/10$), depletion attraction caused by the polymers is masked by the electrostatic repulsion.
-
-We enclose the suspension in a thin microscopy cell sketched in Fig.~\ref{fig:cell_vs_cap}a.
-The bottom wall of the cell is an osmotic membrane providing contact with a long channel full of the same solvent mixture.
-We introduce solid salt at the other end of the channel.
-Salt dissolution and subsequent migration of the ions along the channel and through the membrane induce screening of the electrostatic repulsion, revealing the depletion potential well due to the pre-existing polymers.
-The time needed for the ions to diffuse from the membrane across the cell thickness is of the same order of magnitude as the Brownian time of the particles $\tau_B=10$ s.
-This method causes uniform gelation starting from the homogeneous Wigner crystal state without any solvent flow, allowing \textit{in situ} confocal microscopy observation throughout the process from $t \sim 0$.
-
-As noted above, the conventional shaking or shear melting protocols for the initiation of phase separation cause severe non-ideal perturbation to a system. To show this,  
-we compare, in Fig.~\ref{fig:cell_vs_cap}b and c, confocal microscopy images of the final structures for two gels prepared at the same state point: one by our protocol and the other by introducing in a capillary an existing gel and thus shear melting it, respectively.
-The later is coarser, highlighting that shaking or shear melting protocols~\cite{lu2008gelation,Teece2011,Bartlett2012} are not equivalent to a quench.
-Our novel quench protocol provides an ideal experimental platform to make a comparison with theory and simulations.
-However, we note that Brownian Dynamics simulations cannot reproduce our experimental results even with the same quench, because of the lack of a solvent mediating hydrodynamic interactions~\cite{tanaka2000simulation,Furukawa2010}.
-%Thus our protocol might be very close to application relevant processes where the sudden addition of a component (e.g.
-salt, acid, depletion agent) induces aggregation in an otherwise stable suspension (e.g.
-milk).
-
-In Fig.~\ref{fig:cell_vs_cap}d, we show a computer reconstruction from experimental coordinates of a typical gelation experiment at a relatively low volume fraction ($\phi=7.5\%$).
-Immediately before ions enter the cell ($t=0$), the suspension is in a Wigner crystal state where the particles are far apart due to long range Coulomb repulsion.
-As soon as the charges are screened, the particles begin to aggregate and form clusters that progressively connect to each other while coarsening to finally percolate over the field of view around $t=35$ min.
-
-%\subsection*{Observation of the initial stage}
-
-In Fig.~\ref{fig:phasediag}a, we show the phase diagram, where we can divide the state points into three regions based on the final state obtained by our protocol: at low polymer concentration ($c_p<0.2$ g/$\ell$) a sample fully relaxes to a fluid state; at very low colloid volume fraction ($\phi<0.05$) and high polymer concentration the particles condense into long-lived well separated clusters as observed in~\cite{Lu2006}; in the rest of the explored phase space we observe a long-lived space spanning network.
-We also show the theoretical spinodal line obtained by generalised free volume theory~\cite{Fleer2008}, which is in good agreement with our experimental points 
-(the small discrepancy at small colloidal volume fractions is common in free volume theory~\cite{Shah2003,Bergenholtz2003,lu2008gelation}).
-
-With our technique we can observe the entire kinetic path leading to the final state at a single-particle level.
-To characterise this path, we compute the instantaneous mean number of neighbours $\bar{N}_C$, or coordination number that quantifies the compactness of the structure.
-We also compute the the spatial extent of the largest cluster $l_\text{max}$ that we normalize by the size of the field of view $L$ to obtain a measure of the distance to percolation of the system.
-Figure~\ref{fig:phasediag}b shows a system trajectory in the $(l_\text{max}/L, \bar{N}_C)$ plane for various colloidal volume fractions.
-At high densities, percolation takes place first, within the first few $\tau_B$ after charge screening by salt, and then coarsening proceeds.
-At low densities, percolation never takes place and we observe the compaction of individual clusters.
-In between, we observe the process detailed in Fig.~\ref{fig:cell_vs_cap}d: formation of low-compacity clusters that then slowly connect together to build the percolating network.
-This process can take hundreds of $\tau_B$ and is competing with cluster compaction, as indicated by the oblique trajectory (red open circles) in Fig.~\ref{fig:phasediag}b.
-The path to gelation in this plane is thus not universal and depends on the colloid volume fraction even within the gelation region.
-
-The initial similarity between the trajectories of dilute gels and cluster phase is striking, as if their dynamics were ruled by the same phenomenon.
-To confront this hypothesis, we compute the time dependent static structure factor $S(q,t)$.
-For all gel and cluster samples, we observe the appearance of a low $q$ peak in $S(q)$, see Supplementary Figure~1, which is characteristic of spinodal decomposition in a system of a conserved order parameter.
-To track the position of this peak, we compute the characteristic wave number $\langle q \rangle$ and show its temporal evolution in Fig.~\ref{fig:phasediag}c.
-The curves for all samples follow a master curve coherent with spinodal decomposition kinetics: At short times $\langle q \rangle(t)$ shows a plateau indicating that the low $q$ peak builds up at constant wave number corresponding to distances of about $2\sigma$.
-This plateau is characteristic of the early stage spinodal decomposition, which is described by Cahn's linear theory \cite{onuki2002phase}.
-At intermediate times, on the other hand, we observe coarsening with \textcolor{blue}{$\langle q \rangle \sim t^{-1/2}$, which is often observed in viscoelastic phase separation
-(see, e.g., \cite{Furukawa2010}).} Finally at longer times each sample deviates from the master curve to form a plateau indicating arrest. The more dilute samples arrest sooner, 
-but the origin of arrest is different between clusters and percolated networks.
-For clusters, density fluctuations grow rather rapidly in the initial stage, but after the formation of isolated clusters their growth takes a long time since the diffusive evaporation-condensation mechanism does not work for colloidal viscoelastic phase separation and direct cluster collisions and coalescence are necessary for coarsening \cite{tanaka2000viscoelastic}.
-For networks, densification due to phase separation leads to dynamic arrest due to vitrification \cite{piazza1994phase,verhaegh1997,tanaka1999colloid,poon2002,zaccarelli2007,lu2008gelation} or formation of locally stable structures \cite{royall2008g}.
-Our observations indicate that both cluster and gel phases are due to viscoelastic spinodal decomposition: network-type spinodal for the gel, and droplet-type spinodal for the clusters where strong dynamical asymmetry between colloids and the solvent leads to unique roles of hydrodynamics and mechanics in phase separation \cite{tanaka1999colloid,tanaka2000viscoelastic}.
-
-Here two questions remain, corresponding respectively to the dilute or dense routes to gelation: (i) How can individual clusters percolate a long time after their formation?
-(ii) How does a percolated network evolve toward more compact states?
-We will show that the answers come from mechanical effects: respectively hydrodynamics and internal mechanical stresses.
-
-%\subsection*{Role of hydrodynamics}
-
-First we focus on the role of hydrodynamics. 
-In Fig.~\ref{fig:hydro}a, we follow the compaction of clusters made of only three particles in a non-percolating sample.
-The probability distribution of the radius of gyration $R_g$ of these triplets shows two peaks on both sides of $R_g^*=0.8\sigma$.
-For $R_g<R_g^*$ the cluster is compact, with a structure close to an equilateral triangle.
-For $R_g>R_g^*$ the three particles are aligned and the cluster is elongated.
-We found that just after the quench most triplets are elongated and then either connect to other clusters or relax to the more stable compact state.
-To follow this relaxation, we define the probability to stay elongated as
-\begin{equation}
-P_\text{el}(\Delta t) = \left\langle P\left(\delta_i(t+\Delta t)|\delta_i(t)\right)\right\rangle_{t,i}, 
-\end{equation}
-where $\delta_i(t)$ is the probability for the triplet $i$ to be elongated at time $t$.
-The decay of $P_\text{el}(\Delta t)$ has a characteristic time of $27\tau_B$, much longer than the Brownian time.
-
-The shape of clusters of more than 3 particles cannot be followed in the same way.
-Thus we compute the principal moments of gyrations $\lambda_j$ with $\lambda_1\geq\lambda_2\geq\lambda_3$.
-Low values of the aspect ratios $\lambda_2/\lambda_1$ and $\lambda_3/\lambda_1$ indicate that the cluster is flat or even linear.
-In Fig.~\ref{fig:hydro}b, we show the evolution of the average value of these aspect ratios either for a non-percolating sample or before percolation for a percolating one.
-In both cases, we observe that the clusters are originally not compact and become more isotropic over tens of $\tau_B$.
-As can be seen in Fig.~\ref{fig:cell_vs_cap}d, structural isotropy is recovered only after the fusion of many anisotropic clusters into a branched structure.
-
-These observations can be rationalised by the invocation of hydrodynamic effects.
-Indeed in a solvent, particles cannot converge freely to form compact structures~\cite{tanaka1999colloid,tanaka2000simulation,Furukawa2010}.
-The compaction is delayed by the incompressibility of the solvent, which allows only divergence-free transverse flow fields.
-Furthermore, clusters influenced by hydrodynamic interactions tend to be more elongated, less compact.
-We can test this hypothesis by measuring at which angle particles meet relative to existing neighbours.
-If influenced by hydrodynamics, particles should avoid the direction of existing neighbours and come from more open angles.
-
-In Fig.~\ref{fig:hydro}c we show the bond angle distribution from three points of view: (i) existing bonds, (ii) bonds that will form within the next $\tau_B$, (iii) bonds that will form within the next $\tau_B$ involving an isolated particle.
-As expected, existing bonds are preferentially at a 60$^\circ$ angle indicating stable packing, with secondary peaks coherent with a mixture of tetrahedral and hexagonal packings.
-Future bonds have more acute angles and almost never 180$^\circ$, since they are mostly due to particles attached to second neighbours, see sketch in Fig.~\ref{fig:hydro}c.
-Here hydrodynamics plays no role.
-By contrast, future bonds involving isolated particles form at more obtuse angles, with a clear peak around 180$^\circ$.
-This confirms that hydrodynamics influences particle aggregation and explains why clusters are initially elongated.
-
-Consequently, long-lived elongated clusters have a higher probability to meet via either rotational or translational diffusion than compact spherical clusters.
-In Supplementary Figure~\ref{fig:effectiveVF} we show that indeed at all colloidal volume fraction percolation takes place when the effective volume fraction $\phi_\text{eff} = \sum\frac{4\pi}{3}R_g^3$ of the clusters reaches random close packing.
-Hydrodynamics explains why in a rather dilute regime we can observe immediate formation of elongated clusters and then their slow, hydrodynamically-assisted aggregation into a percolated structure.
-We stress that this is a direct consequence of large-size disparity, which leads to the physical situation where discrete solid objects are floating in a continuum liquid.
-
-%\subsection*{Network ageing}
-In the above, we show that with a help of hydrodynamic interactions, particles first form
-a transient gel even at very low volume fractions, and thus only later they increase the number of
-nearest neighbours to minimize the energy of the structure. 
-Thus, hydrodynamic interactions lead to the formation of gels that are very far from equilibrium and under a strong thermodynamic driving force 
-towards more stable compact structures. 
-Due to the connectivity of the network, the resulting transition from open to more compact networks can take place only through
-the breaking of the bonds that have accumulated more stress. The process was called stress-driven ageing~\cite{Tanaka2007}, 
-which is characteristic of viscoelastic phase separation \cite{tanaka2000viscoelastic}. 
-As we saw in Fig.~\ref{fig:phasediag}c, the coarsening in these samples is indeed much slower than what is expected from ordinary spinodal decomposition dynamics \cite{onuki2002phase}, 
-suggestive of mechanical frustration effects.
-The phase separation is arrested, but the system is still ageing slowly, a process sometimes leading to delayed sudden collapse of gels~\cite{poon1999delayed,Bartlett2012}, a catastrophic phenomenon from the industrial point of view.
-Previous numerical studies~\cite{Tanaka2007,colombo2014self,testard2014intermittent} have shown that the main coarsening mechanism is the rupture of strands in the network, a process that to our knowledge has not been followed experimentally at the particle level.
-Below we provide the first experimental proof of this process.
-
-Figure~\ref{fig:breaking}a shows a strand rupture reconstructed from confocal 3D images, the colours mapping the intensity of internal stresses acting on each particle.
-In practice, the attraction potential well is too narrow relative to the particle localisation errors for us to extract directly the force acting on a particle.
-Therefore, we use the elongation of the particle neighbourhood as a proxy.
-The more the bonds around a particle are oriented along a single axis, the more tension is exerted on the particle.
-This local elongation is quantified using bond orientational order~\cite{steinhardt1983boo} for the 2-fold symmetry $q_2$, see Methods for a precise definition.
-In Fig.~\ref{fig:breaking}a we observe the slow build up of tension over the first 30 min, until the tension is concentrated on a weak part, a one particle thin strand.
-This strand breaks and the particles involved merge in their respective part of the network that then stay apart from each other.
-This is the only elementary process allowed for a percolated network to lower the free energy and it is a mechanically driven coarsening process \cite{Tanaka2007}.
-The driving force is simply attractive interactions between particles favouring compact structures, which can be rephrased by
-interfacial energy in a coarse-grained picture.
-
-To detect strand rupture, we use the topology of the bond network.
-We can consider the gel as a graph with the particles as nodes and the bonds as edges.
-This graph evolves from frame to frame separated by $3\tau_B$.
-In the lower part of Fig.~\ref{fig:breaking}a, we draw in red the shortest on-graph path between two particles of interest.
-Before the strand rupture, this path is a single bond long.
-After the rupture, the shortest path is much longer.
-In general, when two particles were bonded on the previous frame and are no more bonded on the present frame, we define the post-breaking topological distance $\Lambda$ as the new shortest distance on the graph between them, minus 1.
-If the particles still have a common neighbour then $\Lambda=1$, because two bonds are needed to go from one to the other.
-$\Lambda=2$ when three bonds are needed, etc.
-
-This path length $\Lambda$ is a good measure of the significance of a bond breaking event.
-Small values indicate a local rearrangement whereas large values are the signature of important changes in the topology of the network, namely strand rupture.
-Figure~\ref{fig:breaking}b shows the distribution of $\Lambda$ for three colloidal volume fractions.
-Excluding the largest values that are dominated by the limited size of the field of view, $\Lambda$ seems to follow a power-law distribution of exponent between $-3$ and $-4$.
-However the values at $\Lambda=1$ seems in excess.
-Figure~\ref{fig:breaking}c compares the probability distribution of $q_2$ for all bond breaking events versus for evens with $\Lambda>1$.
-In both cases bonds about to break have a higher probability of being under tension, but this trend is much clearer when excluding local events.
-Both observations point to spurious detection of bond breaking events due to localisation errors comparable to the short attraction range and rattling of particles.
-For this reason, but also to focus on topologically relevant strand rupture, we discard all events with $L \leq 3$ in the following analysis.
-
-In Fig.~\ref{fig:breaking}d we show the time evolution of the probability for a topologically relevant strand rupture $P_\text{break}(\Lambda>3)$, i.e.
-the ratio of the number of bond breaking events with $\Lambda>3$ by the number of particles.
-$P_\text{break}$ has its maximum at percolation and then decreases and finally saturates.
-Strikingly all curves collapse after percolation, indicating common physical ingredients for the ageing of gels at all concentrations.
-
-Initially, clusters are in elongated, unstable configurations.
-When isolated, a cluster is able to relax to a more compact and stable shape.
-However in dense samples, elongated clusters meet, before any compaction, into large branched clusters able to transmit stresses.
-The compaction trend exerts internal stresses on the strands inside those clusters large enough to make them rupture.
-This effect is maximum when the sample is fully percolated and thus the network is most strongly stretched, and the internal stresses are maximum.
-
-The characteristic size of a spinodal network is \textcolor{blue}{$\xi(t)\sim t^{1/2}$} (see Fig.
-2c).
-Strands being linear objects, their volume is linear in $\xi$ and thus the number of strands in the field of view $N_s$ evolves as \textcolor{blue}{$t^{-1/2}$}.
-Since after the percolation no new strands are to be created, the variation in the number of strands is given only by the strand rupture rate:
-\begin{equation}
-\textcolor{blue}{P_\text{break} = -\frac{d N_s}{dt} \sim t^{-3/2}.}
-\end{equation}
-Indeed in Fig.~\ref{fig:breaking}d we observe that the initial regime of the master curve is well described by a power law of exponent \textcolor{blue}{$-3/2$}. 
-\textcolor{blue}{The saturation of $P_{\rm break}$ at late times may be an artefact due to a choice of $\Lambda$ too small for characterising breaking events taking place in the late stage. 
-The criterion $\Lambda>3$ is good for the initial stage, but may be too strict for the late stage and detect local rearrangements. 
-Thus, $P_{\rm break}$ should actually be negligible in the very late stage and the structure evolution is arrested (see Fig. 2c).} 
-At longer times, most of the internal stresses have been released and the system reaches arrested phase separation, where the yield stress emerging due to dynamical arrest 
-exceeds the internal mechanical stress. 
-For dilute samples, percolation happens later, after the end of the power law regime. Thus, the clusters have already compacted to stable configurations and internal stresses are low.
-
-% \section{Conclusion}
-To summarize, we successfully follow the entire process of colloidal gelation at a single particle level and 
-show that spinodal gelation is induced by spinodal decomposition, but the process is heavily frustrated  by 
-hydrodynamics and mechanics, both of which originates from the dynamical asymmetry due to the large size disparity between 
-colloidal particles and solvent molecules. The hydrodynamic effect is the consequence of the fact that solvent molecules 
-can be treated as a continuum fluid in the much larger length and time scales of colloids and thus obey the Navier-Stokes equation. 
-We can preclude a possibility that the formation of elongated clusters is due to non-ideal flow induced by the mixing, which may be the case for the conventional protocols. 
-In a dilute system, local condensation proceeds simultaneously as percolation.
-In contrast, dense systems accomplish percolation in the early stage, whereas local condensation proceeds in the late stage; and this rapid percolation leads to high internal stress at the time of percolation.
-In both cases of gelation, percolation is a consequence of condensation frustrated by hydrodynamic interactions, whereas the coarsening process is frustrated by mechanical tensions.
-We also find that the fate of a percolated network, more specifically, whether it is permanently stabilised as a gel or eventually breaks up into isolated clusters, 
-crucially depends on whether the weak parts of the gel network can support the self-generated mechanical stress or not. 
-%In the systems studied the rate of the network breakup events decreases with time, but tends to remain finite even after 10$^3$ $\tau_{B}$, 
-%suggesting that network may eventually loose its connectivity. 
-Since colloidal suspensions can be regarded as an ideal model system of binary mixtures that consist of small and big components, 
-our study will shed new light on not only colloidal gelation but also dynamically asymmetric mixtures, which include polymer solutions, emulsions, and protein solutions. 
-We hope that our findings will deepen our microscopic understanding of spinodal gelation concerning the lower bound of gelation and the long-term stability, both of 
-which are important in industrial applications.
-
-\section*{METHODS}
-
-\subsection*{Experimental.}
-
-We used \textsc{pmma} (poly(methyl methacrylate)) colloids sterically stabilized with methacryloxypropyl terminated \textsc{pdms}(poly(dimethyl siloxane)) and fluorescently labelled with rhodamine isothiocyanate chemically bonded to the \textsc{pmma}.
-Colloids are dispersed in a mixture of cis-decalin (Tokyo Kasei) and bromocyclohexane (Sigma-Aldrich) that matches both optical index and density of the colloids.
-
-To induce short-ranged depletion attraction, we use polystyrene (TOSOH) of molecular weight 8.4$\times 10^6$ as non-adsorbing polymer.
-The radius of gyration in theta solvent is estimated to 110 nm.
-Here the solvent may be regarded as ``good'' and a Flory scaling of the measurements of~\cite{lu2008gelation} yields $R_g=148$ nm.
-In the absence of salt, the Debye length is expected to reach several $\mu$m and the (weakly) charged colloids experience a long range electrostatic repulsion~\cite{Royall2003}.
-We confirm that colloids never come close enough to feel the short-ranged attraction and form a Wigner crystal.
-
-The colloids and polymers are contained in an observation cell ($10$ mm$^2$ $\times$ 200 $\mu$m) made of glass in contact with an half-open glass channel approximately 400 times larger in volume, via a millipore filter with pore size of 100 nm that allows the salt through but neither polymer nor colloid (see Fig.~\ref{fig:cell_vs_cap}a).
-The channel is filled with the same solvents at density matching composition.
-At the beginning of the experiment, solid tetrabutylammonium bromide (Fluka) is introduced to the channel.
-Data acquisition starts within 30 s after salt introduction.
-Our procedure induces practically no solvent flow in the observation cell.
-We confirmed the presence of undissolved salt several days after mixing, indicating that the observation cell was brought to saturation concentration.
-
-Given the diffusion constants of Bromide and alkyl cation ($6$ and $2 \times 10^{-10}$~m$^2$/s~\cite{Campbell2005}), we estimate the characteristic diffusion time of salt from top to bottom of the order of 10~s.
-Therefore, we reach uniform final salt concentration into the observation cell within only a few Brownian times of the colloids.
-Indeed we measured a delay of about 1 min between the aggregation at the bottom and at the top of the cell.
-We define the initial time of the aggregation process when the maximum of the $g(r)$ jumps from the lattice constant of the Wigner crystal to the hard-core diameter $\sigma$.
-
-We collect the data on a Leica SP5 confocal microscope, using 532 nm laser excitation.
-The temperature was controlled on both stage and objective lens, allowing a more precise density matching.
-The scanned volume is at least $82 \times 82 \times 85$~$\mu$m$^3$.
-The particle coordinates are tracked in three dimensions (3D) with an accuracy of around $0.03\sigma$~\cite{LeocmachColloids}.
-
-\subsection*{Analysis.}
-
-From direct confocal measurements~\cite{Royall2007, Poon2012}, we estimate the hard-core diameter of our colloids ($\sigma=2.75$~$\mu$m) and the range of the interaction potential (that confirmed our scaling of $R_g$ within $1\%$), leading to a polymer-colloid size ratio $q = 2R_g/\sigma = 0.10(6)$.
-Spinodal line on Fig.~\ref{fig:phasediag}b are calculated from this size ratio using the generalized free volume theory~\cite{Fleer2008}.
-
-In principle the attraction well of the depletion extends to $\sigma+2R_g$, however, resolution-dependent tracking imprecisions and systematic errors do not give a precise enough estimate of such short distance.
-Therefore we consider two particles bonded when their distance is shorter the first minimum of $g(r)$, i.e.
-3.55~$\mu$m.
-This defines the bond graph that we analyse using connected components and shortest path analysis algorithms~\cite{Hagberg2008}.
-
-To detect local 2-fold symmetry and thus elongation, we use \citet{steinhardt1983boo} bond orientational order for the particle $i$,
-\begin{align}
-	q_2(i) =& \sqrt{\frac{4\pi}{5} \sum_{m=-2}^{2} |q_{2,m}(i)|^2 }, \label{eq:ql}\\
-	q_{2,m}(i) =& \frac{1}{N_i}\sum_{j=1}^{N_i} Y_{2,m}(\theta(\mathbf{r}_{ij}),\phi(\mathbf{r}_{ij})),
-	\label{eq:qlm}
-\end{align}
-where the $Y_{\ell, m}$ are spherical harmonics and $\mathbf{r}_{ij}$ is one of the $N_i$ bonds involving particle $i$.
-
-\bibliographystyle{naturemag3}
-\bibliography{ico_dyn}
-
-\vspace{1cm}
-%\item[Supplementary Information] is linked to the online version of the paper at www.nature.com/nature.
-\noindent
-{\bf Acknowledgements.} This study was partly supported by Grants-in-Aid for Scientific Research (S) (Grand No. 21224011) and Specially Promoted Research (Grand No. 25000002) from 
-the Japan Society for the Promotion of Science (JSPS).
-
-%\vspace{0.3cm}
-\noindent
-{\bf Author Contributions.} H.Ts. and M.L. contributed equally to this work. 
-H.Ta. conceived and supervised the project, H. Ts. performed experiments, M.L. analysed the data, and all authors discussed and wrote the manuscript.
-
-%\vspace{0.3cm}
-\noindent
-{\bf Author Information} Reprints and permissions information is available at www.nature.com/reprints.
-Correspondence and requests for materials should be addressed to H.T. ~(tanaka@iis.u-tokyo.ac.jp).
-
-\clearpage
-\begin{figure*}
-	%\includegraphics[width=16cm]{figure1.pdf}
-	\includegraphics{figs/cell_vs_cap2.pdf}
-	\caption{\textbf{Reservoir cell.} \textbf{a,} Sketch of our experimental setup.
-The observation cell contains initially colloids, polymer and no salt.
-\textbf{b,} Confocal slice of a gel formed \textit{in situ} by our method ($\phi=25.5~\%$, $c_p=1.4$ g/$\ell$), 1 hour after gelation.
-\textbf{c,} Idem for a gel at the same state point formed \textit{ex situ} and immediately pumped into a capillary.
-\textbf{d,} Gelation observed by our method.
-Experimental coordinates are reconstructed and coloured by the number of particles in clusters in a typical sample close to the cluster-gel line ($\phi=7.5~\%$, $c_p=1$ g/$\ell$).
-Origin of time is the last frame before melting of Wigner crystal.
-	%Phase diagram obtained in reservoir cell.
-Spinodal line is obtained from free volume theory.
-State points analysed in the text are circled.
-The state point of \textbf{b-c} is highlighted by a square.
-	}
-	\label{fig:cell_vs_cap}
-\end{figure*}
-
-\clearpage 
 \begin{figure}
-%\includegraphics[width=10cm]{figure2.pdf}
-\includegraphics{figs/phasediag.pdf}
-\caption{\textbf{Different regimes of gelation.} \textbf{a,} Phase diagram.
-Experimental points are categorised based on the final state obtained in reservoir cell.
-The spinodal line is obtained from free volume theory.
-State points analysed in the text are circled.
-The state point of Fig.~\ref{fig:cell_vs_cap}b-c is highlighted by a square.
-\textbf{b,} Comparison of system evolution in terms of largest cluster extent and of mean coordination number.
-By increasing density: $\phi=4.2,\,8,\,16,\,27~\%$, $c_p=1,\,1.5,\,1.2,\, 1$ g/$\ell$ for
-%\textcolor{red!40!yellow}
-{$\blacklozenge$}, 
-%\textcolor{red!80!yellow}
-{$\circ$}, 
-%\textcolor{red!80!black}
-{\tiny$\blacksquare$} and 
-%\textcolor{red!40!black}
-{$\bullet$} respectively. \textbf{c,} Growth of the characteristic wave number for the same samples. 
-The line is a scaling law for the intermediate coarsening regime for network-forming phase separation.}
-\label{fig:phasediag}
+\includegraphics{figs/structure_factor.pdf}
+\caption{\textbf{Structure factor evolution} in the four samples shown on Fig.
+2 of the main text by decreasing volume fraction.
+The thick black curve corresponds to the intial wigner crystal before salt introduction (ill defined thus not shown in \textbf{d}).
+Thin curves from dark red to yellow are spaced by \SI{150}{\second} and display a peak corresponding to the hard sphere diameter as well as a growing peak at low $q$ inticating gelation.}
+\label{fig:structure_factor}
 \end{figure}
 
-\clearpage
-\begin{figure}
-	%\includegraphics[width=10cm]{figure3.pdf}
-	\includegraphics{figs/hydro.pdf}
-	\caption{\textbf{Hydrodynamics} \textbf{a,} Probability of staying elongated for a triplet in a non-percolating sample ($\phi=4~\%$, $c_p=1$ g/$\ell$).
-The continuous line is the best exponential fit of characteristic time $27\tau_B$.
-Inset: probability distribution of radii of gyration of triplets.
-\textbf{b,} Evolution of the aspect ratios of clusters of 4 particles and more in the same sample (dashed lines) and in a percolating sample ($\phi=8~\%$, $c_p=1.5$ g/$\ell$, continuous lines).
-\textbf{c,} Bond angle distribution relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue) obtained in the percolating sample.
-Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles.
-Insets sketch both cases, with present bonds drawn thick and future bonds drawn dotted.}
-	\label{fig:hydro}
-\end{figure}
-
-\clearpage
-\begin{figure*}
-%\includegraphics[width=16cm]{figure4.pdf}
-\includegraphics{figs/breaking.pdf}
-\caption{\textbf{Mechanical tension drives coarsening} 
-\textbf{a,} Reconstruction from experimental coordinates ($\phi=29~\%$, $c_p=0.7$ g/$\ell$) of coarsening process geometry (top) and topology (bottom).
-Particles are drawn to scale and coloured by $q_2$ from blue (low) to red (high).
-The meshed surface is a Gaussian coarse-graining of the network pattern.
-The red line indicates the shortest on-graph path between the two particles of interest.
-\textbf{b,} Number of bond breaking function of the future on-graph distance $\Lambda$ (after percolation) for the three percolating state points of Fig. 2a (same colours and markers).
-%three state points of increasing density: $\phi=8,\,16,\,27~\%$, $c_p=1.5,\,1.2,\,1$g/$\ell$ for \textcolor{red!80!yellow}{$\circ$}, \textcolor{red!80!black}{\tiny$\blacksquare$} and \textcolor{red!40!black}{$\bullet$} respectively.
-\textbf{c,} Probability for a bond to break during $3\tau_B$ function of bond-centred $q_2$ for all events (blue) and for events with $\Lambda>1$ (thick red) in the same sample as \textbf{a}.
-\textbf{d,} Evolution of the topologically relevant bond breaking probability ($\Lambda>3$) for the same state points as in b. Vertical lines indicate the respective percolation times.
-}
-\label{fig:breaking}
-\end{figure*}
-
 \end{document}

### 2016-10-01 manuscript4.tex
Comment out "effective volume fraction" according to mail exchanges between 17/11/2015 and 24/11/2015. Final word was "The percolation problem may be related to a large scale organization of structures helped by flow. This may lead to the failure of a simple argument based on effective volume, assuming the isotropic nature of structuring."

@@
 \author{Hideyo Tsurusawa}
+\affiliation{ {Institute of Industrial Science, University of Tokyo, 4-6-1 Komaba, Meguro-ku, Tokyo 153-8505, Japan} }
 %\thanks{These authors contributed equally to this work}
 \author{Mathieu Leocmach}
+\affiliation{Univ Lyon, Université Claude Bernard Lyon 1, CNRS, Institut Lumière Matière, F-69622, VILLEURBANNE, France}
 %\thanks{These authors contributed equally to this work}
@@
 Consequently, long-lived elongated clusters have a higher probability to meet via either rotational or translational diffusion than compact spherical clusters. 
-In Supplementary Figure~\ref{fig:effectiveVF} we show that indeed at all colloidal volume fraction percolation takes place when the effective volume fraction $\phi_\text{eff} = \sum\frac{4\pi}{3}R_g^3$ of the clusters reaches random close packing.
+%In Supplementary Figure~\ref{fig:effectiveVF} we show that indeed at all colloidal volume fraction percolation takes place when the effective volume fraction $\phi_\text{eff} = \sum\frac{4\pi}{3}R_g^3$ of the clusters reaches random close packing.
 Hydrodynamics explains why in a rather dilute regime we can observe immediate formation of elongated clusters and then their slow, hydrodynamically-assisted aggregation into a percolated structure.

### 2016-10-01 manuscript4.tex
rework intro to dense gel and stress-driven ageing

@@
 %\subsection*{Network ageing}
-In the above, we show that with a help of hydrodynamic interactions, particles first form
-a transient gel even at very low volume fractions, and thus only later they increase the number of
-nearest neighbours to minimize the energy of the structure. 
+In denser samples, hydrodynamics also helps create elongated structures, but in that case these structures immediately connect and percolate. The increase of the number of
+nearest neighbours to minimize the energy of the structure comes only later.
+%In the above, we show that with a help of hydrodynamic interactions, particles first form
+%a transient gel even at very low volume fractions, and thus only later they increase the number of
+%nearest neighbours to minimize the energy of the structure. 
 Thus, hydrodynamic interactions lead to the formation of gels that are very far from equilibrium and under a strong thermodynamic driving force 

### 2016-11-25 gel_cond/trunk/manuscript4.tex
two columns, figures in the text

@@
-\documentclass[preprint,footinbib,amsmath,amssymb,superscriptaddress]{revtex4}
+\documentclass[footinbib,amsmath,amssymb,superscriptaddress,twocolumn]{revtex4}
 \usepackage{graphicx,amsmath}
@@
 \begin{document}
-\draft
 
@@
 On noting that the strands of a gel network are often very thin, and thus it is hardly clear whether we can apply the concept of glass transition as it is to describe dynamic arrest in gelation.
+
+\begin{figure*}
+	%\includegraphics[width=16cm]{figure1.pdf}
+	\includegraphics{figs/cell_vs_cap2.pdf}
+	\caption{\textbf{Reservoir cell.} \textbf{a,} Sketch of our experimental setup.
+The observation cell contains initially colloids, polymer and no salt.
+\textbf{b,} Confocal slice of a gel formed \textit{in situ} by our method ($\phi=25.5~\%$, $c_p=1.4$ g/$\ell$), 1 hour after gelation.
+\textbf{c,} Idem for a gel at the same state point formed \textit{ex situ} and immediately pumped into a capillary.
+\textbf{d,} Gelation observed by our method.
+Experimental coordinates are reconstructed and coloured by the number of particles in clusters in a typical sample close to the cluster-gel line ($\phi=7.5~\%$, $c_p=1$ g/$\ell$).
+Origin of time is the last frame before melting of Wigner crystal.
+	%Phase diagram obtained in reservoir cell.
+Spinodal line is obtained from free volume theory.
+State points analysed in the text are circled.
+The state point of \textbf{b-c} is highlighted by a square.
+	}
+	\label{fig:cell_vs_cap}
+\end{figure*}
 
@@
 %\subsection*{Observation of the initial stage}
+\begin{figure}
+%\includegraphics[width=10cm]{figure2.pdf}
+\includegraphics{figs/phasediag.pdf}
+\caption{\textbf{Different regimes of gelation.} \textbf{a,} Phase diagram.
+Experimental points are categorised based on the final state obtained in reservoir cell.
+The spinodal line is obtained from free volume theory.
+State points analysed in the text are circled.
+The state point of Fig.~\ref{fig:cell_vs_cap}b-c is highlighted by a square.
+\textbf{b,} Comparison of system evolution in terms of largest cluster extent and of mean coordination number.
+By increasing density: $\phi=4.2,\,8,\,16,\,27~\%$, $c_p=1,\,1.5,\,1.2,\, 1$ g/$\ell$ for
+%\textcolor{red!40!yellow}
+{$\blacklozenge$}, 
+%\textcolor{red!80!yellow}
+{$\circ$}, 
+%\textcolor{red!80!black}
+{\tiny$\blacksquare$} and 
+%\textcolor{red!40!black}
+{$\bullet$} respectively. \textbf{c,} Growth of the characteristic wave number for the same samples. 
+The line is a scaling law for the intermediate coarsening regime for network-forming phase separation.}
+\label{fig:phasediag}
+\end{figure}
 
@@
 %\subsection*{Role of hydrodynamics}
+\begin{figure}
+	%\includegraphics[width=10cm]{figure3.pdf}
+	\includegraphics{figs/hydro.pdf}
+	\caption{\textbf{Hydrodynamics} \textbf{a,} Probability of staying elongated for a triplet in a non-percolating sample ($\phi=4~\%$, $c_p=1$ g/$\ell$).
+The continuous line is the best exponential fit of characteristic time $27\tau_B$.
+Inset: probability distribution of radii of gyration of triplets.
+\textbf{b,} Evolution of the aspect ratios of clusters of 4 particles and more in the same sample (dashed lines) and in a percolating sample ($\phi=8~\%$, $c_p=1.5$ g/$\ell$, continuous lines).
+\textbf{c,} Bond angle distribution relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue) obtained in the percolating sample.
+Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles.
+Insets sketch both cases, with present bonds drawn thick and future bonds drawn dotted.}
+	\label{fig:hydro}
+\end{figure}
 
@@
 
+\begin{figure*}
+%\includegraphics[width=16cm]{figure4.pdf}
+\includegraphics{figs/breaking.pdf}
+\caption{\textbf{Mechanical tension drives coarsening} 
+\textbf{a,} Reconstruction from experimental coordinates ($\phi=29~\%$, $c_p=0.7$ g/$\ell$) of coarsening process geometry (top) and topology (bottom).
+Particles are drawn to scale and coloured by $q_2$ from blue (low) to red (high).
+The meshed surface is a Gaussian coarse-graining of the network pattern.
+The red line indicates the shortest on-graph path between the two particles of interest.
+\textbf{b,} Number of bond breaking function of the future on-graph distance $\Lambda$ (after percolation) for the three percolating state points of Fig. 2a (same colours and markers).
+%three state points of increasing density: $\phi=8,\,16,\,27~\%$, $c_p=1.5,\,1.2,\,1$g/$\ell$ for \textcolor{red!80!yellow}{$\circ$}, \textcolor{red!80!black}{\tiny$\blacksquare$} and \textcolor{red!40!black}{$\bullet$} respectively.
+\textbf{c,} Probability for a bond to break during $3\tau_B$ function of bond-centred $q_2$ for all events (blue) and for events with $\Lambda>1$ (thick red) in the same sample as \textbf{a}.
+\textbf{d,} Evolution of the topologically relevant bond breaking probability ($\Lambda>3$) for the same state points as in b. Vertical lines indicate the respective percolation times.
+}
+\label{fig:breaking}
+\end{figure*}
+
 %\subsection*{Network ageing}
-In the above, we show that with a help of hydrodynamic interactions, particles first form
-a transient gel even at very low volume fractions, and thus only later they increase the number of
-nearest neighbours to minimize the energy of the structure. 
+In denser samples, hydrodynamics also helps create elongated structures, but in that case these structures immediately connect and percolate. The increase of the number of
+nearest neighbours to minimize the energy of the structure comes only later.
+%In the above, we show that with a help of hydrodynamic interactions, particles first form
+%a transient gel even at very low volume fractions, and thus only later they increase the number of
+%nearest neighbours to minimize the energy of the structure. 
 Thus, hydrodynamic interactions lead to the formation of gels that are very far from equilibrium and under a strong thermodynamic driving force 
@@
 \clearpage
-\begin{figure*}
-	%\includegraphics[width=16cm]{figure1.pdf}
-	\includegraphics{figs/cell_vs_cap2.pdf}
-	\caption{\textbf{Reservoir cell.} \textbf{a,} Sketch of our experimental setup.
-The observation cell contains initially colloids, polymer and no salt.
-\textbf{b,} Confocal slice of a gel formed \textit{in situ} by our method ($\phi=25.5~\%$, $c_p=1.4$ g/$\ell$), 1 hour after gelation.
-\textbf{c,} Idem for a gel at the same state point formed \textit{ex situ} and immediately pumped into a capillary.
-\textbf{d,} Gelation observed by our method.
-Experimental coordinates are reconstructed and coloured by the number of particles in clusters in a typical sample close to the cluster-gel line ($\phi=7.5~\%$, $c_p=1$ g/$\ell$).
-Origin of time is the last frame before melting of Wigner crystal.
-	%Phase diagram obtained in reservoir cell.
-Spinodal line is obtained from free volume theory.
-State points analysed in the text are circled.
-The state point of \textbf{b-c} is highlighted by a square.
-	}
-	\label{fig:cell_vs_cap}
-\end{figure*}
 
 \clearpage
-\begin{figure}
-%\includegraphics[width=10cm]{figure2.pdf}
-\includegraphics{figs/phasediag.pdf}
-\caption{\textbf{Different regimes of gelation.} \textbf{a,} Phase diagram.
-Experimental points are categorised based on the final state obtained in reservoir cell.
-The spinodal line is obtained from free volume theory.
-State points analysed in the text are circled.
-The state point of Fig.~\ref{fig:cell_vs_cap}b-c is highlighted by a square.
-\textbf{b,} Comparison of system evolution in terms of largest cluster extent and of mean coordination number.
-By increasing density: $\phi=4.2,\,8,\,16,\,27~\%$, $c_p=1,\,1.5,\,1.2,\, 1$ g/$\ell$ for
-%\textcolor{red!40!yellow}
-{$\blacklozenge$}, 
-%\textcolor{red!80!yellow}
-{$\circ$}, 
-%\textcolor{red!80!black}
-{\tiny$\blacksquare$} and 
-%\textcolor{red!40!black}
-{$\bullet$} respectively. \textbf{c,} Growth of the characteristic wave number for the same samples. 
-The line is a scaling law for the intermediate coarsening regime for network-forming phase separation.}
-\label{fig:phasediag}
-\end{figure}
-
-\clearpage
-\begin{figure}
-	%\includegraphics[width=10cm]{figure3.pdf}
-	\includegraphics{figs/hydro.pdf}
-	\caption{\textbf{Hydrodynamics} \textbf{a,} Probability of staying elongated for a triplet in a non-percolating sample ($\phi=4~\%$, $c_p=1$ g/$\ell$).
-The continuous line is the best exponential fit of characteristic time $27\tau_B$.
-Inset: probability distribution of radii of gyration of triplets.
-\textbf{b,} Evolution of the aspect ratios of clusters of 4 particles and more in the same sample (dashed lines) and in a percolating sample ($\phi=8~\%$, $c_p=1.5$ g/$\ell$, continuous lines).
-\textbf{c,} Bond angle distribution relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue) obtained in the percolating sample.
-Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles.
-Insets sketch both cases, with present bonds drawn thick and future bonds drawn dotted.}
-	\label{fig:hydro}
-\end{figure}
-
-\clearpage
-\begin{figure*}
-%\includegraphics[width=16cm]{figure4.pdf}
-\includegraphics{figs/breaking.pdf}
-\caption{\textbf{Mechanical tension drives coarsening} 
-\textbf{a,} Reconstruction from experimental coordinates ($\phi=29~\%$, $c_p=0.7$ g/$\ell$) of coarsening process geometry (top) and topology (bottom).
-Particles are drawn to scale and coloured by $q_2$ from blue (low) to red (high).
-The meshed surface is a Gaussian coarse-graining of the network pattern.
-The red line indicates the shortest on-graph path between the two particles of interest.
-\textbf{b,} Number of bond breaking function of the future on-graph distance $\Lambda$ (after percolation) for the three percolating state points of Fig. 2a (same colours and markers).
-%three state points of increasing density: $\phi=8,\,16,\,27~\%$, $c_p=1.5,\,1.2,\,1$g/$\ell$ for \textcolor{red!80!yellow}{$\circ$}, \textcolor{red!80!black}{\tiny$\blacksquare$} and \textcolor{red!40!black}{$\bullet$} respectively.
-\textbf{c,} Probability for a bond to break during $3\tau_B$ function of bond-centred $q_2$ for all events (blue) and for events with $\Lambda>1$ (thick red) in the same sample as \textbf{a}.
-\textbf{d,} Evolution of the topologically relevant bond breaking probability ($\Lambda>3$) for the same state points as in b. Vertical lines indicate the respective percolation times.
-}
-\label{fig:breaking}
-\end{figure*}
 

### 2017-01-12 manuscript4.tex
microrheology 2P + internal stress

@@
 We stress that this is a direct consequence of large-size disparity, which leads to the physical situation where discrete solid objects are floating in a continuum liquid.
+
+\begin{figure}
+\includegraphics{figs/microrheology2P.pdf}
+\caption{\textbf{Time-dependent microrheology} of three percolating samples.
+By increasing density from top to bottom $\phi=8,\,16,\,27~\%$, $c_p=1.5,\,1.2,\, 1$ g/$\mathrm{\ell}$. 
+The thick gray curve is the internal stress $\Sigma$ obtained from the measure of bond-breaking rate. 
+Elastic ($G^\prime$) and viscous ($G^{\prime\prime}$) shear moduli, obtained by two-particle microrheology, are drawn respectively as red filled and black open circles. 
+The dotted vertical line shows the percolation time.
+}
+\end{figure}
+
+\begin{figure*}
+%\includegraphics[width=16cm]{figure4.pdf}
+\includegraphics{figs/breaking.pdf}
+\caption{\textbf{Mechanical tension drives coarsening} 
+\textbf{a,} Reconstruction from experimental coordinates ($\phi=29~\%$, $c_p=0.7$ g/$\ell$) of coarsening process geometry (top) and topology (bottom).
+Particles are drawn to scale and coloured by $q_2$ from blue (low) to red (high).
+The meshed surface is a Gaussian coarse-graining of the network pattern.
+The red line indicates the shortest on-graph path between the two particles of interest.
+\textbf{b,} Number of bond breaking function of the future on-graph distance $\Lambda$ (after percolation) for the three percolating state points of Fig. 2a (same colours and markers).
+%three state points of increasing density: $\phi=8,\,16,\,27~\%$, $c_p=1.5,\,1.2,\,1$g/$\ell$ for \textcolor{red!80!yellow}{$\circ$}, \textcolor{red!80!black}{\tiny$\blacksquare$} and \textcolor{red!40!black}{$\bullet$} respectively.
+\textbf{c,} Probability for a bond to break during $3\tau_B$ function of bond-centred $q_2$ for all events (blue) and for events with $\Lambda>1$ (thick red) in the same sample as \textbf{a}.
+\textbf{d,} Evolution of the topologically relevant bond breaking probability ($\Lambda>3$) for the same state points as in b. Vertical lines indicate the respective percolation times.
+}
+\label{fig:breaking}
+\end{figure*}
 
@@
 Both observations point to spurious detection of bond breaking events due to localisation errors comparable to the short attraction range and rattling of particles.
-For this reason, but also to focus on topologically relevant strand rupture, we discard all events with $L \leq 3$ in the following analysis.
+For this reason, but also to focus on topologically relevant strand rupture, we discard all events with $\Lambda \leq 3$ in the following analysis.
 

### 2017-01-13 manuscript4.tex
Describe fig:microrheology2P

@@
 \usepackage{color}
+
+\newcommand{\FigLossTangent}{XXX}
+
 \begin{document}
@@
 \title{Gelation as condensation frustrated by hydrodynamics and mechanical tension}
+\author{Mathieu Leocmach}
+\thanks{These authors contributed equally to this work}
+\affiliation{Univ Lyon, Universit\'e Claude Bernard Lyon 1, CNRS, Institut Lumi\`ere Mati\`ere, F-69622, VILLEURBANNE, France}
 \author{Hideyo Tsurusawa}
+\thanks{These authors contributed equally to this work}
 \affiliation{ {Institute of Industrial Science, University of Tokyo, 4-6-1 Komaba, Meguro-ku, Tokyo 153-8505, Japan} }
-%\thanks{These authors contributed equally to this work}
-\author{Mathieu Leocmach}
-\affiliation{Univ Lyon, Université Claude Bernard Lyon 1, CNRS, Institut Lumière Matière, F-69622, VILLEURBANNE, France}
-%\thanks{These authors contributed equally to this work}
+\author{John Russo}
+\affiliation{ {School of Mathematics, University of Bristol, Bristol BS8 1TW, United Kingdom} }
 \author{Hajime Tanaka}
-%\email{tanaka@iis.u-tokyo.ac.jp}
+\email{tanaka@iis.u-tokyo.ac.jp}
 \affiliation{ {Institute of Industrial Science, University of Tokyo, 4-6-1 Komaba, Meguro-ku, Tokyo 153-8505, Japan} }
@@
 \maketitle
+
+\begin{figure*}
+	%\includegraphics[width=16cm]{figure1.pdf}
+	\includegraphics{figs/cell_vs_cap2.pdf}
+	\caption{\textbf{Reservoir cell.} \textbf{a,} Sketch of our experimental setup.
+The observation cell contains initially colloids, polymer and no salt.
+\textbf{b,} Confocal slice of a gel formed \textit{in situ} by our method ($\phi=25.5~\%$, $c_p=1.4$ g/$\ell$), 1 hour after gelation.
+\textbf{c,} Idem for a gel at the same state point formed \textit{ex situ} and immediately pumped into a capillary.
+\textbf{d,} Gelation observed by our method.
+Experimental coordinates are reconstructed and coloured by the number of particles in clusters in a typical sample close to the cluster-gel line ($\phi=7.5~\%$, $c_p=1$ g/$\ell$).
+Origin of time is the last frame before melting of Wigner crystal.
+	%Phase diagram obtained in reservoir cell.
+Spinodal line is obtained from free volume theory.
+State points analysed in the text are circled.
+The state point of \textbf{b-c} is highlighted by a square.
+	}
+	\label{fig:cell_vs_cap}
+\end{figure*}
 
@@
 On noting that the strands of a gel network are often very thin, and thus it is hardly clear whether we can apply the concept of glass transition as it is to describe dynamic arrest in gelation.
-
-\begin{figure*}
-	%\includegraphics[width=16cm]{figure1.pdf}
-	\includegraphics{figs/cell_vs_cap2.pdf}
-	\caption{\textbf{Reservoir cell.} \textbf{a,} Sketch of our experimental setup.
-The observation cell contains initially colloids, polymer and no salt.
-\textbf{b,} Confocal slice of a gel formed \textit{in situ} by our method ($\phi=25.5~\%$, $c_p=1.4$ g/$\ell$), 1 hour after gelation.
-\textbf{c,} Idem for a gel at the same state point formed \textit{ex situ} and immediately pumped into a capillary.
-\textbf{d,} Gelation observed by our method.
-Experimental coordinates are reconstructed and coloured by the number of particles in clusters in a typical sample close to the cluster-gel line ($\phi=7.5~\%$, $c_p=1$ g/$\ell$).
-Origin of time is the last frame before melting of Wigner crystal.
-	%Phase diagram obtained in reservoir cell.
-Spinodal line is obtained from free volume theory.
-State points analysed in the text are circled.
-The state point of \textbf{b-c} is highlighted by a square.
-	}
-	\label{fig:cell_vs_cap}
-\end{figure*}
 
@@
 
+%\subsection*{Network ageing}
+In denser samples, hydrodynamics also helps create elongated structures, but in that case these structures immediately connect and percolate. The increase of the number of
+nearest neighbours to minimize the energy of the structure comes only later.
+%In the above, we show that with a help of hydrodynamic interactions, particles first form
+%a transient gel even at very low volume fractions, and thus only later they increase the number of
+%nearest neighbours to minimize the energy of the structure. 
+Thus, hydrodynamic interactions lead to the formation of gels that are very far from equilibrium and under a strong thermodynamic driving force 
+towards more stable compact structures. 
+Due to the connectivity of the network, the resulting transition from open to more compact networks can take place only through
+the breaking of the bonds that have accumulated more stress. The process was called stress-driven ageing~\cite{Tanaka2007}, 
+which is characteristic of viscoelastic phase separation \cite{tanaka2000viscoelastic}. 
+As we saw in Fig.~\ref{fig:phasediag}c, the coarsening in these samples is indeed much slower than what is expected from ordinary spinodal decomposition dynamics \cite{onuki2002phase}, 
+suggestive of mechanical frustration effects.
+The phase separation is arrested, but the system is still ageing slowly, a process sometimes leading to delayed sudden collapse of gels~\cite{poon1999delayed,Bartlett2012}, a catastrophic phenomenon from the industrial point of view.
+Previous numerical studies~\cite{Tanaka2007,colombo2014self,testard2014intermittent} have shown that the main coarsening mechanism is the rupture of strands in the network, a process that to our knowledge has not been followed experimentally at the particle level.
+Below we provide the first experimental proof of this process.
+
 \begin{figure}
@@
 By increasing density from top to bottom $\phi=8,\,16,\,27~\%$, $c_p=1.5,\,1.2,\, 1$ g/$\mathrm{\ell}$. 
-The thick gray curve is the internal stress $\Sigma$ obtained from the measure of bond-breaking rate. 
-Elastic ($G^\prime$) and viscous ($G^{\prime\prime}$) shear moduli, obtained by two-particle microrheology, are drawn respectively as red filled and black open circles. 
+The thick gray curve is the internal stress $\Sigma$ obtained from the measure of bond-breaking probability. 
+Elastic ($G^\prime$) and viscous ($G^{\prime\prime}$) shear moduli at high frequency ($f=0.1\tau_\mathrm{B}^{-1}$), obtained by two-particle microrheology, are drawn respectively as red filled and black open circles.
 The dotted vertical line shows the percolation time.
 }
+\label{fig:microrheology2P}
 \end{figure}
+
+Following \citet{Lindstrom2012} we express the bond dissociation rate $k_D$ under a force $\mathcal{F}$ as 
+\begin{equation}
+k_D(\mathcal{F}) = k_D(\mathcal{F}=0) \exp\left(\frac{\mathcal{F} \delta}{k_\mathrm{B}T}\right)
+\end{equation}
+with $\delta$ the width of the potential, here the depletion range obtained from generalized free volume theory~\cite{Fleer2008}.
+$k_D(\mathcal{F}=0)$ depends only on the depth and shape of the interaction potential.
+From our particle-level experimental data, we can measure at each time step the probability for a bond to break.
+This probability decays from high values at short times to an asymptotic, finite value at long times.
+We checked that $k_D(t\rightarrow\infty)$ decreases with increasing polymer concentration and thus the attractive potential depth.
+Although, due to the small but finite value of the Debye length, $k_D(t\rightarrow\infty)$ cannot be related to the theoretical depth of the depletion potential~\cite{VanDoorn2016}.
+
+The decay of $k_D$ takes tens of Brownian times, a time scale much longer than ion diffusion throughout the cell.
+Therefore the interaction potential can be considered stable and the evolution of $k_D$ translates directly in an evolution of $\mathcal{F}$.
+\begin{equation}
+\mathcal{F}(t) = \frac{k_\mathrm{B}T}{\delta} \log\frac{k_D(t)}{k_D(t\rightarrow\infty)}
+\end{equation}
+where we assume that the final state is force-free $k_D(t\rightarrow\infty) = k_D(\mathcal{F}=0)$.
+Using the contact area of the depletion potential we can convert $f$ into a statistical measure of the internal stress $\Sigma (t) = 2 \mathcal{F}(t) /(\pi \sigma \delta^2)$.
+
+To put internal stress relaxation in perspective, we need to know when the system becomes solid.
+The rheological definition of the gelation point is the time when the elastic and viscous parts of the shear modulus (respectively $G^\prime$ and $G^{\prime\prime}$) both scale as identical power laws of frequency $f$, in other words $G^{\prime\prime}/G^\prime$ is independent of the frequency~\cite{Chambon1987}.
+To measure
+the shear modulus, we use the particles themselves as passive rheological probes.
+Following~\citet{Crocker2000} we convert two-particle mean square displacements $\Delta r^2(t, \Delta t)$ in $G^\prime(t, f)$ and $G^{\prime\prime}(t, f)$.
+Supplementary figure~\FigLossTangent{} shows the evolution of $G^{\prime\prime}/G^\prime$ for three percolating samples, for three frequencies each.
+The convergence of the different frequencies is obvious for all samples, however only the two samples with highest volume fractions actually reach the gelation point during the experimental time.
+Nonetheless all three samples reach $G^\prime > G^{\prime\prime}$ at high frequencies.
+
+In Figure~\ref{fig:microrheology2P}, to relate the timing of stress relaxation, mechanical gelation and percolation, we superimpose the time evolutions of internal stress and both parts of the shear moduli at the highest accessible frequency ($f=0.1\tau_\mathrm{B}^{-1}$).
+The time needed for $\Sigma(t)$ to relax completely seems to be approximatively independent of colloid volume fraction.
+Moreover, stress relaxation occurs independently of percolation.
+In dilute gels, Figure~\ref{fig:microrheology2P}a, internal stresses are relaxed when percolation takes place, whereas in dense gels, Figure~\ref{fig:microrheology2P}c, stress relaxation occurs mostly after percolation.
+Percolation is obviously a necessary condition for mechanical gelation, since the crossing of $G^\prime$ and $G^{\prime\prime}$ occurs always later than percolation.
+However there is a long delay between percolation and the rise of $G^\prime$, therefore percolation is not enough to ensure mechanical stability.
+In dense gel, Figure~\ref{fig:microrheology2P}c, the just percolated network rearranges under internal stresses until a mechanically stable configuration is found.
+For dilute gels, Figure~\ref{fig:microrheology2P}a, we observe larger fluctuations on $\Sigma(t)$ after percolation, probably due to the release of local internal stresses progressively leading to a mechanically stable configuration.
+
+%- dense gels have much higher moduli than dilute ones
 
@@
 \end{figure*}
-
-%\subsection*{Network ageing}
-In denser samples, hydrodynamics also helps create elongated structures, but in that case these structures immediately connect and percolate. The increase of the number of
-nearest neighbours to minimize the energy of the structure comes only later.
-%In the above, we show that with a help of hydrodynamic interactions, particles first form
-%a transient gel even at very low volume fractions, and thus only later they increase the number of
-%nearest neighbours to minimize the energy of the structure. 
-Thus, hydrodynamic interactions lead to the formation of gels that are very far from equilibrium and under a strong thermodynamic driving force 
-towards more stable compact structures. 
-Due to the connectivity of the network, the resulting transition from open to more compact networks can take place only through
-the breaking of the bonds that have accumulated more stress. The process was called stress-driven ageing~\cite{Tanaka2007}, 
-which is characteristic of viscoelastic phase separation \cite{tanaka2000viscoelastic}. 
-As we saw in Fig.~\ref{fig:phasediag}c, the coarsening in these samples is indeed much slower than what is expected from ordinary spinodal decomposition dynamics \cite{onuki2002phase}, 
-suggestive of mechanical frustration effects.
-The phase separation is arrested, but the system is still ageing slowly, a process sometimes leading to delayed sudden collapse of gels~\cite{poon1999delayed,Bartlett2012}, a catastrophic phenomenon from the industrial point of view.
-Previous numerical studies~\cite{Tanaka2007,colombo2014self,testard2014intermittent} have shown that the main coarsening mechanism is the rupture of strands in the network, a process that to our knowledge has not been followed experimentally at the particle level.
-Below we provide the first experimental proof of this process.
 

### 2017-01-31 manuscript4.tex
Try to integrate Lambda max

@@
 \includegraphics{figs/microrheology2P.pdf}
-\caption{\textbf{Time-dependent microrheology} of three percolating samples.
+\caption{\textbf{Time-dependent mechanical response} of three percolating samples.
 By increasing density from top to bottom $\phi=8,\,16,\,27~\%$, $c_p=1.5,\,1.2,\, 1$ g/$\mathrm{\ell}$. 
 The thick gray curve is the internal stress $\Sigma$ obtained from the measure of bond-breaking probability. 
-Elastic ($G^\prime$) and viscous ($G^{\prime\prime}$) shear moduli at high frequency ($f=0.1\tau_\mathrm{B}^{-1}$), obtained by two-particle microrheology, are drawn respectively as red filled and black open circles.
+Elastic ($G^\prime$) and viscous ($G^{\prime\prime}$) shear moduli at high frequency ($f=0.1\tau_\mathrm{B}^{-1}$), obtained by two-particle microrheology, are drawn respectively as filled and open circles.
+The dark red bars show $\Lambda_\mathrm{max}$, the size of the largest strand breaking event.
 The dotted vertical line shows the percolation time.
@@
 In dense gel, Figure~\ref{fig:microrheology2P}c, the just percolated network rearranges under internal stresses until a mechanically stable configuration is found.
-For dilute gels, Figure~\ref{fig:microrheology2P}a, we observe larger fluctuations on $\Sigma(t)$ after percolation, probably due to the release of local internal stresses progressively leading to a mechanically stable configuration.
+%For dilute gels, Figure~\ref{fig:microrheology2P}a, we observe larger fluctuations on $\Sigma(t)$ after percolation, probably due to the release of local internal stresses progressively leading to a mechanically stable configuration.
 
@@
 
-Figure~\ref{fig:breaking}a shows a strand rupture reconstructed from confocal 3D images, the colours mapping the intensity of internal stresses acting on each particle.
-In practice, the attraction potential well is too narrow relative to the particle localisation errors for us to extract directly the force acting on a particle.
-Therefore, we use the elongation of the particle neighbourhood as a proxy.
-The more the bonds around a particle are oriented along a single axis, the more tension is exerted on the particle.
+To understand how a percolated suspension evolves to a mechanically stable gel, we complement the mean field measurements above with local observables.
+Figure~\ref{fig:breaking}a shows a strand rupture reconstructed from confocal 3D images, the colours mapping the internal strain acting on each particle. 
+In practice, the attraction potential well is too narrow relative to the particle localisation errors for us to measure reliably the strain of a single bond.
+Therefore, we measure the elongation of the particle neighbourhood. 
+%The more the bonds around a particle are oriented along a single axis, the more tension is exerted on the particle. 
 This local elongation is quantified using bond orientational order~\cite{steinhardt1983boo} for the 2-fold symmetry $q_2$, see Methods for a precise definition.
@@
 This strand breaks and the particles involved merge in their respective part of the network that then stay apart from each other.
-This is the only elementary process allowed for a percolated network to lower the free energy and it is a mechanically driven coarsening process \cite{Tanaka2007}.
+This is the only elementary process allowed for a percolated network to lower the free energy and it is a mechanically driven coarsening process~\cite{Tanaka2007}.
 The driving force is simply attractive interactions between particles favouring compact structures, which can be rephrased by
